---
title: "Stephens Passage area survey results"
author: "Katie Palof"
date: "Nov 14th, 2020"
output: html_document
---

```{r setup, include = FALSE}
library(knitr)
library(tidyverse)
#dat <- read.csv("../data/rkc/Juneau/jnu_16_17_oceanAK_out_RAW.csv")
cur_yr = 2020
survey.location = 'Juneau'
area = "SP"
cur_yr
```

## Stephens Passage
## CPUE from survey / data for CSA
```{r CPUE, echo = FALSE }
cpue <- read.csv(paste0(here::here(),'/results/tanner/nj_stp/', cur_yr, '/', area, '_CPUE_all.csv'))
cpue %>% 
  filter(Year >= cur_yr-4) -> cpue_cur_yr
kable(cpue_cur_yr, digits = 6)

```

### Male weights from survey 
```{r weights, echo = FALSE }
male_weights <- read.csv(paste0(here::here(),'/results/tanner/nj_stp/', cur_yr,'/', area, '_weights.csv'))
kable(male_weights, digits = 3)
```

## Short term trends in CPUE
```{r short term, echo = FALSE }
short_term_results <- read.csv(paste0(here::here(),'/results/tanner/nj_stp/', cur_yr,'/', area, '_shortterm.csv'))
kable(short_term_results, digits = 3)
```


## Long term trends in CPUE
```{r long term,echo = FALSE  }
#long_term_results <- read.csv(paste0(here::here(),'/results/tanner/nj_stp/', cur_yr,'/', area, '_longterm.csv'))
#kable(long_term_results, digits = 3)
```

## Female health
#### percentage and SD of poor clutches (<25%)
```{r female health,echo = FALSE  }
poorclutch_curyr <- read.csv(paste0(here::here(),'/results/tanner/nj_stp/', cur_yr,'/', area, '_percent_low_clutch.csv'))
poorclutch_curyr %>% 
  filter(Year >= cur_yr-1) -> poorclutch_curyr

kable(poorclutch_curyr, digits = 3)
```


####long term mean comparison
```{r long term female, echo = FALSE}
#lt_female <- read.csv(paste0(here::here(),'/results/tanner/nj_stp/', cur_yr,'/', area, 'lt_female.csv'))

#kable(lt_female, digits = 3)
```

####short term females
```{r short term female, echo = FALSE}
short_female <- read.csv(paste0(here::here(),'/results/tanner/nj_stp/', cur_yr,'/', area, '_Fem_shortterm.csv'))

kable(short_female, digits = 3)
```


####Mean egg percentage for mature females
```{r egg per female, echo = FALSE}
egg_per_mean <- read.csv(paste0(here::here(),'/results/tanner/nj_stp/', cur_yr,'/', area, '_percent_clutch.csv'))
egg_per_mean %>% 
  filter(Year >= cur_yr-1) -> egg_per_mean

kable(egg_per_mean, digits = 3)
```



## Stock health
```{r stock health, echo = FALSE}
#stock_health <- read.csv(paste0(here::here(),'/results/rkc/', survey.location, '/', cur_yr,'/stock_health.csv'))

#kable(stock_health, digits = 3)
```


