---
title: "Southeast Tanner crab assessment 2021 CONFIDENTIAL draft "
author: "Katie Palof, katie.palof@alaska.gov"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  bookdown::word_document2:
    fig_caption: yes
    includes: null
    toc: no
    reference_docx: style_settings.docx
  word_document:
    reference_docx: style_settings.docx
    toc: no
---
\pagenumbering{arabic}

```{r global_options, include=FALSE, echo = FALSE, message = FALSE, warning=FALSE}
library(knitr)
source(paste0(here::here(),'/code/tanner_rkc_functions.R'))
cur_yr = 2021
pr_yr = cur_yr-1
fut_yr = cur_yr+1
opts_chunk$set(fig.width = 12, fig.height = 7, echo = FALSE, warning = FALSE, message = FALSE,  dpi=300)

set_flextable_defaults(
  font.family = "Arial", 
  font.size = 9,
  font.color = "black",
  table.layout = "autofit",
  text.align = "center"
  #digits = 1,
  #theme_fun = "theme_box"
  )
#\pagenumbering{gobble}
```

```{r exesum, echo = FALSE}
biomass <- read.csv(paste0(here::here(),'/data/tanner/tanner_', cur_yr, '_biomassmodel.csv'))  
# file for all locations.  Has legal and mature biomass from current year CSA & harvest
hist_bio <- read.csv(paste0(here::here(),'/data/tanner/tanner_annual_pt_estimate_historic_', pr_yr,'.csv'))

#table2 <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/Table2_regional_2021.csv'))
# these are created in 'figure2_tables.R'
#table3 <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/Table3_regional_2021.csv'))
#tableA3 <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/TableA3_regional_2021.csv'))
#table4 <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/Table4_regional_2021.csv'))
###
# regional biomass ----
biomass %>% 
  group_by(Year) %>% 
  summarise(legal = round(sum(Legal),0), mature = round(sum(Mature),0)) %>% 
  as.data.frame() -> regional.b

## expansion factor for non-surveyed areas ----
regional.b %>% 
  mutate(non_sur_legal = round((legal/0.66) - legal, 0),
         non_sur_mature = round((mature/0.66) - mature, 0),
         TOTAL_leg = (legal + non_sur_legal), 
         TOTAL_mat = (mature + non_sur_mature)) -> regional.b_table

regional.b_table %>% filter(Year == cur_yr) -> b_cur_yr
b_cur_yr %>% 
  select(Year, legal, mature) -> add_hist
# historic comparisons ---
hist_bio %>% 
  dplyr::rename(legal = Legal, mature = Mature) %>% 
  bind_rows(add_hist) -> hist_bio2
# save a new version of this file here !!fix!!
hist_bio2 %>% 
  filter(Year >= pr_yr) %>% 
  mutate(non_sur_legal = round((legal/0.66) - legal, 0),
         non_sur_mature = round((mature/0.66) - mature, 0),
         TOTAL_leg = (legal + non_sur_legal), 
         TOTAL_mat = (mature + non_sur_mature)) %>% 
  gather(type, pounds, legal:TOTAL_mat, factor_key = TRUE) %>% 
  spread(key = Year, value = pounds) %>% 
  mutate(change = 100*(`2021`-`2020`)/`2020`, diff = `2021`-`2020`) -> change

round((change %>% filter(type == 'TOTAL_mat'))$diff/1000000, 2) -> pr_yr_diff
round((change %>% filter(type == 'TOTAL_mat'))$`2020`/1000000, 2) -> pr_yr_mat
round((change %>% filter(type == 'TOTAL_leg'))$diff/1000000, 2) -> pr_yr_diff_L
round((change %>% filter(type == 'TOTAL_leg'))$change, 1) -> pr_yr_per_L

prop_harvest <- read.csv(paste0(here::here(), '/results/tanner/harvest/', cur_yr, '/proportion_total_harvest_', cur_yr, '.csv'))

prop_harvest %>% 
  filter(Year == cur_yr-1)


```

FYI: CONFIDENTIAL biometrics draft 


# `r cur_yr` QUICK SUMMARY {-}
  - Generally regional biomass has been steady or increasing under the current effort-based management framework, allowing for a stable population and a consistent annual harvest (Figure \@ref(fig:regionalbio), \@ref(fig:stdcpue), and \@ref(fig:regionalbio2)).  
  - The trends in legal and mature male biomass have been generally increasing since 2010, with this year's projection has both legal and mature biomass increasing from the previous year. However, historic point estimate show a divergent trajectory for this stock, but both have the stock at healthy levels (Figure \@ref(fig:regionalbio) and \@ref(fig:regionalbio2)). 
  - Overall stock health is mixed with some areas improving and others declining from last year. Stock health is “Poor” in one areas, “Below Average” in one areas, “Moderate” in four areas, “Above Average” in two areas, and “Healthy” in four areas (Tables 2 and 3).

# SUMMARY {-}
The estimated `r cur_yr`/`r fut_yr` Southeast Region mature male Tanner crab biomass is **`r round(b_cur_yr$TOTAL_mat/1000000, 2)` million lb**, up approximately **`r pr_yr_diff` million lb** from the `r pr_yr`/`r cur_yr` estimate of **`r pr_yr_mat` million lb**. 
This estimate exceeds the 2.3 million-pound threshold of mature male biomass in regulation [5 AAC 35.113(a)] required to open the commercial fishery. Once the threshold is met, season length is determined using a regulatory harvest strategy based on effort and mature male biomass. No guideline harvest level (GHL) is set or targeted through inseason management. Despite the lack of a GHL-based harvest strategy, harvestable surplus (GHL) of legal male Tanner crab is estimated to provide a basis for evaluating fishery performance and removals from the stock. 
Applying the stock health status recommended (14.9%) and maximum (20%) exploitation rates to mature male biomass results in a range of GHLs between 0.88 and 1.16 million pounds, respectively (Tables 1 and 2). Harvesting at higher levels, when stock health is poor or moderate, may increase the probability of population declines. Since 2010, the stock status of Southeast Alaska Tanner crab has generally improved (Figure \@ref(fig:regionalbio)). 

# SOUTHEAST TANNER CRAB SURVEY AND ANALYSIS {-}
Methods to estimate mature male biomass and assess stock health are similar to those used since 2013; changes to the sampling areas, sampling methods, and catch per unit effort (CPUE) calculations are described below. Background and details of historic methods can be found in Bishop et al. 2013.  In general, a three-stage Catch Survey Analysis (CSA) model is used to estimate biomass and the Alaska Department of Fish and Game (ADF&G) survey data are used to assess stock health (Seber 2002, Zheng and Kruse 1999). 

## No Updates or Change (2016-2021) {-}

## 2015 Updates and Change {-}
Due to budget constraints, Port Camden and Port Frederick were removed as surveyed areas in 2015 and are now considered part of the non-surveyed area for biomass calculations. To estimate regional Tanner crab biomass, the survey area biomass is extrapolated to the non-surveyed areas using an expansion factor. The expansion factor was adjusted in 2015 by removing the average contribution of commercial catch from the two areas removed from the survey during the years used for expansion factor estimation (1980-2000). From 1980 to 2000, an average of 1% of the commercial harvest was from Port Frederick and 4% of the commercial harvest was from Port Camden. Therefore, the previous expansion factor of 71% was reduced to 66%. The current analysis calculates biomass assuming 66% of the biomass is found in the survey areas and 34% in the non-surveyed areas. All graphs and figures reflect these changes.  

Additionally, in 2015 the Stephens Passage area was removed from the October Tanner crab survey. In the past, data from the summer red king/Tanner crab survey and the October Tanner crab survey were combined to assess stock health and estimate biomass in this area. Retrospective analysis of these data showed that the summer red king crab survey adequately allowed for an estimation of biomass in Stephens Passage and that the October survey data could be removed. Long- and short-term trends of stock health were recalculated using ONLY summer red king/Tanner crab survey data during the baseline years (1997–2006) and the biomass estimates were also adjusted by a correction factor. This correction factor was calculated by comparing a retrospective analysis from 1997 (when the survey began for Tanner crab) to 2014 (the last year Stephens Passage was surveyed in October). Biomass estimates using only the red king crab survey data were compared to those using both data sets. The difference between these estimates was used to adjust ONLY the red king crab survey data biomass estimates to be comparable to previous years. On average the biomass estimates using ONLY the red king crab survey data were 7% higher than those with both data sets. For 2015 and beyond, the biomass estimate was adjusted down 7% to compare to previous years reported biomass estimates using data from both surveys. 

## 2014 – No Updates or changes {-}

## 2013 Updates and Changes {-}
In preparation for the 2013 Tanner crab survey the survey areas were stratified based on crab density and depth, modeled on the density stratification currently in place for red king crab survey areas (Clark 2008). Prior to this stratification, simple random sampling had occurred to determine pot placement in the survey areas. The goal of density stratified sampling is to provide more statistically robust estimates of CPUE for use in the CSA model, which in turn will provide additional confidence in our biomass forecasts. Survey sampling from 2013 forward will be performed using these density strata to guide our randomized pot placement. All of the previous year’s CPUE calculations and biomass estimates were also re-estimated to accommodate the changes in sampling methods.  

A CSA model is performed for each of the survey areas, accurate harvest data in each area is vital to biomass estimation. Harvest, in numbers of crab, is used in the model to scale the survey CPUE to estimate biomass in each area.  Inaccurate accounting of harvest can lead to over or under estimation of the biomass. To better match spatial harvest with survey areas, the statistical areas included in harvest calculations for each survey area were reevaluated. The CSA model requires that the harvest input accounts for all harvest on the stock being modeled, prior to this reevaluation some statistical areas adjacent to our survey areas were not included when they should have been. Historic harvests from fish tickets were recalculated using these improved statistical area divisions and used in the 2013 CSA models. The recalculated harvest in these areas changed the magnitude of the biomass estimates in some of the surveyed areas.  

The final change in 2013 and future analyses was the graphical representation of legal biomass from the CSA in the area figures. In the past the forecasted biomass for each year was represented here, however this led to inaccuracies in the actual trend in legal biomass (forecasted biomass estimates in each year only include data up to that year). In this document the estimated biomass for each year is based on the current year’s model, which includes all data available for each area. Displaying the biomass estimates from the current year’s model allows for a more accurate representation of the trends in biomass over time, which more closely follows the historic harvest in most areas. 

# Harvestable Surplus {-}
Since the 2009/2010 fishing season the Southeast Alaska Tanner crab fishery has been managed using a minimum mature male biomass threshold with a variable season length, in days, determined by a regulatory harvest strategy reliant on fishing effort and mature male biomass. Even though the fishery is not managed using a GHL, the department continues to determine stock health, establish a biologically appropriate mature male harvest rate, and calculate GHLs to provide a biologically sound benchmark by which actual fishery performance can be evaluated. Based on the analysis of Tanner crab biology and harvest strategies adopted in other regions, region-wide exploitation rate (ER) should not exceed 20% of mature male or 38% of legal male estimated biomass.  

Catch-survey modeling of the `r cur_yr` fishery and survey data yields a biomass estimate of **`r round(b_cur_yr$TOTAL_mat/1000000, 2)` million lb** of mature (greater than 108 mm carapace width) and **`r round(b_cur_yr$TOTAL_leg/1000000, 2)` million lb** of legal (greater than 140 mm carapace width) male Tanner crab (Table 1). This is a increase of **`r pr_yr_diff_L` million lb** of legal male Tanner crab (`r pr_yr_per_L `%) from the `r pr_yr` estimate (Figure \@ref(fig:regionalbio2)), predominantly due to legal biomass increases from the `r pr_yr` projections in Stephens Passage, Thomas Bay, Seymour Canal, North Juneau, Excursion Inlet, and Gambier Bay, but balanced by legal biomass decreases in Icy Strait, Glacier Bay, Holkham Bay, Pybus Bay, Peril Strait and Lynn Sisters. Harvesting at the maximum rate (20% of mature biomass) would equate to a GHL of approximately 1.16 million pounds (Table 1). Harvest above this level will increase the probability of population declines. Incorporating stock health information suggests a regional exploitation rate of 14.9% of the mature male biomass would reduce the likelihood of population decline and may provide higher probability of an increase in biomass (Table 1).


# STOCK STATUS BY SURVEY AREA (TABLE 4, FIGS. \@ref(fig:pybus2) – \@ref(fig:excursion3)) {-}
Stock health status is determined by a combination of long- and short-term trends in CPUE. Significance in long-term or short-term trends is defined as a p-value < 0.05. Long-term trends compare the current years mean to the long-term baseline value (generally 1997-2010, or the first ten years for which survey data are available); short-term trends regress the last four years of survey data to determine if a significant increasing or decreasing trend is present. Total score is the sum of scores (+1, 0, -1 for long-term; +.25, 0, -.25 for short-term) for each response variable. Stock health is defined by the total score: < -3.25 = Poor, -3.25 to -1.26 = Below Average, -1.25 to 1.25 = Moderate, 1.26 to 3.25 = Above Average, and > 3.25 = Healthy. Recommended exploitation rates based on stock health are zero percent for “Poor”, 5% for “Below Average”, 10% for “Moderate”, 15% for “Above Average”, and 20% for “Healthy”.

# Fall survey areas (previously Tanner crab) {-}

## Icy Strait, Above Avergage 15% {-}
The Icy Strait stock score increased since the `r pr_yr` survey from poor to above average stock status (Table 2). This change in the population status was due to a increase in all mature male CPUEs from the previous year (Figures \@ref(fig:icy2) and \@ref(fig:icy3)). All of the mature male CPUEs are not significantly different from their long-term averages. Post-recruit male CPUE has a significant increasing short-term trend. The percent of females with poor clutch fullness is significantly lower than 10%. Harvest in Icy Strait has always been close to the estimated legal biomass (see relationship between circles and solid legal biomass line in Figure \@ref(fig:icy2)), suggesting that the population is not isolated to the survey area and that there is likely movement of crab in and out of this area. This hypothesis would suggest that the CSA model is underestimating biomass in Icy Strait, which is apparent in the high harvest rates in this area that are likely not sustainable without population fluctations. Harvest from this area provided an average of 12.0% of the commercial harvest over the baseline years and 13.1% of the harvest during the `r pr_yr`/`r cur_yr` fishery (\@ref(fig:icy2)).

## Glacier Bay, Moderate 10% {-}
The Glacier Bay stock score increased from the `r pr_yr` survey from below average to moderate (Table 2). Increased stock health score is primarily due to an increase in pre-recruit male CPUE and a decrease of females with poor clutches. Recruit male and post-recruit male CPUEs are not significantly different from their long-term averages, while mature female CPUE significantly lower than the long term average (Figures \@ref(fig:glacier2) and \@ref(fig:glacier3)). Both pre-recruit and recruit male CPUE have significant decreasing short-term trends. The percent of females with poor clutch fullness is significantly lower than 10%. The legal population is slightly below baseline levels, and both legal and mature biomass is decreasing rapidly from the high levels of the last few years.  Harvest from this area provided an average of 9.2% of the commercial harvest over the baseline years and 11.1% of the harvest during the `r pr_yr`/`r cur_yr` fishery (Figure \@ref(fig:glacier2)).


## Thomas Bay, Healthy 20% {-}
The Thomas Bay stock score remained healthy similar to the stock status for `r pr_yr` survey (Table 2). Pre-recruit and recruit male CPUEs are significantly above their long-term baseline, while post-recruit male CPUE and mature female CPUE are not significantly different frmo their long-term averages (Figure \@ref(fig:thomas2) and \@ref(fig:thomas3)). Pre-recruit, recruit and mature female CPUEs have significant short-term increasing trends. The percent of females with poor clutch fullness is significantly lower than 10%. Both pre-recruit (second highest observation) and recruit (highest observation) CPUE are at high points historically, and legal biomass projections for `r cur_yr` are the highest predicted for Thomas Bay since the survey began. Thomas Bay commercial harvest provided an average of 4.8% of the regional commercial harvest over the baseline years and 3.5% of the harvest during the `r pr_yr`/`r cur_yr` fishery (Figure \@ref(fig:thomas2)).


## Holkham Bay, Above Average 15% {-}
The Holkham Bay stock score remained above average similar to the health of the stock from the `r pr_yr` survey (Table 2). All recruit class CPUEs are at or above their long-term averages, with none being significantly different from the baseline values (Figures \@ref(fig:holkham2) and \@ref(fig:holkham3)). There is a significant short-term decreasing trend in recruit male CPUE, primarily due to a reduction from historically high levels. The percentage of females with poor clutch fullness is significantly lower than the baseline 10% level. Biomass estimates are generally increasing and are well above their long-term averages. Harvest from this area provided an average of 7.1% of the commercial harvest over the baseline years and 5.1% of the harvest during the `r pr_yr`/`r cur_yr` fishery (Figure \@ref(fig:holkham2)).

## Port Camden, Not surveyed since 2015 {-}
The Port Camden area was removed from the survey in 2015 due to budgetary constraints as well as the low contribution of this area to the overall Tanner crab commercial harvest.  Port Camden is now included in the non-surveyed areas; the average contribution of the catch from Port Camden from 1980 to 2000 (catch years used for survey expansion value calculation) was removed from the survey expansion percentage. See comments at the beginning of this document for specific methods.  The harvest from this area provided an average of 3.8% of the commercial harvest over the baseline years and 0.5% of the harvest during the `r pr_yr`/`r cur_yr` fishery. 

# Summer survey areas (previously red king crab) {-}

## Stephens Passage, Healthy 20% {-}
The Stephens Passage stock score remained in healthy stock status similar to `r pr_yr` (Table 2). All recruit class CPUEs are significantly above their long-term averages (Figures \@ref(fig:sp2) and \@ref(fig:sp3)). All mature male CPUEs have significant short-term increasing short-term trends. The percentage of females with poor clutch fullness was significantly less than the 10% threshold. The legal biomass estimate is above the baseline value, with both legal and mature biomass exceeding the high levels of the late 1990s. The harvest from this area provided an average of 9.5% of the commercial harvest over the baseline years and 14.1% of the harvest during the `r pr_yr`/`r cur_yr` fishery (Figure \@ref(fig:sp2)).  Starting in 2015, only survey data from the summer crab survey is used to assess the Stephens Passage area.  Refer to the assessment updates and changes at the beginning of this document.  

## Seymour Canal, Moderate 10% {-}
The Seymour Canal stock score increased to moderate, up from below average in `r pr_yr` (Table 3). This score increase was driven by a rebounding of recruit male CPUE, and the elimination of the short term decreasing trends in pre-recruit and recruit CPUE. All size/sex categories are at or above their long-term averages, with pre-recruit male CPUE increasing to be significantly above its long term baseline (Figures \@ref(fig:seymour2) and \@ref(fig:seymour3)). The percentage of females with poor clutch fullness is at the threshold of 10%, indicating an average number of females with poor or low clutches. The legal biomass estimate bounced back from the decrease last year to be similar to the estimate two years ago, and remains above the baseline value. The harvest from this area provided an average of 6.3% of the commercial harvest over the baseline years and 5.0% of the harvest during the `r pr_yr`/`r cur_yr` fishery (Figure \@ref(fig:seymour2).

## North Juneau, Healthy 20% {-}
The North Juneau stock score increased since the `r pr_yr` survey to a stock health status of healthy (Table 3). This score increase is driven by all size/sex CPUEs being significantly above their baseline values, with both pre-recruit and recruit male CPUE having significant short-term increasing trends (Figures \@ref(fig:nj2) and \@ref(fig:nj3)). The percentage of females with poor clutch fullness less than 10%, but not significantly so. The legal biomass estimate is increasing but still below the baseline value despite record high pre-recruit CPUE, primarily due to high biomass levels at during the baseline years. The harvest from this area provided an average of 7.1% of the commercial harvest over the baseline years and 4.6% of the harvest during the `r pr_yr`/`r cur_yr` fishery (Figure \@ref(fig:nj2)).

## Excursion Inlet, Moderate 10% {-}
The Excursion Inlet stock score remained at a moderate stock health, similar to the `r pr_yr` survey (Table 3). All recruit class CPUEs are not significantly different from their baseline values, and there are no significant short term trends in CPUEs. The recruit CPUE did increase substantially from the `r pr_yr` survey value, which is reflected in the increasing biomass trend (Figures \@ref(fig:ei2) and \@ref(fig:ei3)). The percentage of females with poor clutches is at the 10% threshold. The legal biomass estimate is above the baseline value and has an increasing trend. The harvest from this area provided an average of 6.3% of the commercial harvest over the baseline years and 1.6% of the harvest during the `r pr_yr`/`r cur_yr` fishery (Figure \@ref(fig:ei2).

# Pybus Bay, Below Average 15% {-}
The Pybus Bay stock decreased since the `r pr_yr`survey to a stock health status of below average (Table 3). This change is a result of decreases in all recruit class CPUEs, with all mature male CPUEs being significantly below their baseline values, which was a substantial decrease from `r pr_yr` values. There are no significant short-term trends (Figures \@ref(fig:pybus2) and \@ref(fig:pybus3)). The percentage of females with poor clutches was not significantly different from the 10% threshold. The legal biomass estimate is just below the baseline value and contradicts the decreasing trend of the past few years. The `r pr_yr` mature male CPUE data points appear out of place in this time series, and while future surveys will validate the trajectory of this stock, the resulting biomass estimates for current year should be assumed to have high uncertainty. The harvest from this area provided an average of 1.2% of the commercial harvest over the baseline years and 0.8% of the harvest during the `r pr_yr`/`r cur_yr` fishery (Figure \@ref(fig:pybus2)).

# Gambier Bay, Poor 0% {-}
The Gambier Bay stock score remained at a poor stock health status, similar to the `r pr_yr` survey results (Table 3). All recruit classes are significantly below their baseline values. There is a significant short-term decreasing trend in mature female CPUE but a significantly short-term increasing trend in recruit male CPUE (Figures \@ref(fig:gambier2) and \@ref(fig:gambier3)). The percentage females with poor clutches is not significantly different from the threshold of 10%. The legal biomass estimate is below the baseline value and has a increasing trend over the last two years suggesting some potential future improvement for this stock. The harvest from this area provided an average of 1.9% of the commercial harvest over the baseline years and 1.1% of the harvest during the `r pr_yr`/`r cur_yr` fishery (Figure \@ref(fig:gambier2)).

# Peril Strait, Healthy 20% {-}
The Peril Strait stock score increased substantially from a health status of moderate in `r pr_yr` to healthy for this year (Table 3).  This increased score is driven by an increase in female health, with mature female CPUE increasing to be significantly above the baseline value and the percentage of females with poor clutches falling significantly below the 10% threshold. Pre-recruit and recruit CPUEs are significantly above their long-term baseline value, while post-recruit CPUE is at its long-term average (Figures \@ref(fig:peril2) and \@ref(fig:peril3)). There is a significant short-term increasing trend in recruit male CPUE. The percentage of females with poor clutches is significantly below the 10% threshold. The legal biomass estimate is above its baseline value, with an increasing trend in the past few years. The harvest from this area contributed an average of 0.7% of the commercial harvest over the baseline years and 1.2% of the harvest during the `r pr_yr`/`r cur_yr` fishery (Figure \@ref(fig:peril2)).

# Lynn Sisters, Above Average 15% {-}
The Lynn Sisters stock remained at above average stock health similar to the `r pr_yr` survey (Table 3). Both pre-recruit and recruit CPUEs are significantly above their long-term baseline values, while post-recruit male and mature female CPUEs are at their long-term baselines (Figures \@ref(fig:lynn2) and \@ref(fig:lynn3)). There is a significant short-term decreasing trend in mature female CPUE. The percentage of females with poor clutch fullness is significantly lower than 10%. The legal biomass estimate is above the baseline value at historically high levels for the area and has remained high for the last few years. The harvest from this area provided an average of 0.7% of the commercial harvest over the baseline years and 1.6% of the harvest during the `r pr_yr`/`r cur_yr` fishery (Figure \@ref(fig:lynn2)).

# Port Frederick, Not surveyed since 2015 {-}
The Port Frederick survey area was removed from the survey in 2015 due to its low contribution to the overall Tanner crab catch and department budget constraints.  Port Frederick is now included in the non-surveyed areas. The average contribution of catch in Port Frederick from 1980 to 2000 was removed from the survey expansion percentage. See comments at the beginning of this document for more detail. The harvest from this area provided an average of 0.5% of the commercial harvest over the baseline years and 0.65% of the harvest during the `r pr_yr`/`r cur_yr` fishery.


# `r cur_yr`/`r fut_yr` TANNER FISHERY MANAGEMENT ACTIONS {-}
TBD

# FISHERY MANAGEMENT CONCERNS {-}
TBD

\newpage
# TABLES AND FIGURES {-}
```{r explain, include=FALSE, echo = FALSE, message = FALSE, warning=FALSE}
# Tables 1, 2, 3 

# Bring in Table 2 and 3 from word for now. Complicated due to how the values in these tables are stored from analysis. 
# 'tanner_crab_tables.docx'

# Table 1 ----
expansion = 0.66
biomass %>% 
  filter(Year == cur_yr) %>% 
  dplyr::select(Year, Area, Legal, Mature) %>%  
  group_by(Year) %>% 
  summarise(Legal = sum(Legal), Mature = sum(Mature)) %>% 
  gather(type, surveyed, Legal:Mature, factor_key = TRUE) %>% 
  mutate(other.areas = ((surveyed/expansion) - surveyed), 
         total = surveyed + other.areas) %>% 
  gather(Area, pounds, surveyed:total) %>% 
  cast(Year+Area~type) -> regional_totals
  
biomass %>% 
  filter(Year == cur_yr) %>% 
  dplyr::select(Year, Area, Legal, Mature) %>% 
  bind_rows(regional_totals) %>% 
  mutate(Healthy_HR = round(0.20, 2), 
         Healthy_GHL = round(Healthy_HR*Mature, 0), 
         Healthy_legalHR = round(Healthy_GHL/Legal, 2), 
         Healthy_GHL = round(ifelse(Healthy_legalHR < 0.38, Healthy_GHL, 
                              Legal*0.38), 0)) -> biomass_rate
```


### Table 1. Results of `r cur_yr` catch-survey modeling estimation of legal and mature Tanner crab biomass and guideline harvest level (GHL) calculations using proposed maximum 20% region-wide mature exploitation rates and exploitation rates based upon the current stock health status for each of the 12 survey areas. See matrices below for a more detailed look at the basis of stock status determinations. The expansion factor of 66% (34% for non-surveyed areas) for the total legal and mature male crab biomass was based on the percent of commercial harvest taken from 1980–2000 in surveyed areas. The average harvest and biomass from the first ten years of survey data in each area represents a mean historical baseline (long-term average) of harvest. Both Tanner crab survey (TCS) and red king crab survey (RKCS) areas are presented.{-}

```{r table1, results = "asis"}
df <- biomass_rate
df %>% 
  select(-Year) %>% 
  filter(Area != "surveyed") -> df
names(df) <- c("Survey area", "Legal biomass", "Mature biomass", "Healthy HR", 
               "Healthy GHL", "Legal HR")
#knitr::kable((df), booktabs = T, caption = "Table 2")
ft <- flextable(df)
#ft <- autofit(ft)
#ft
set_table_properties(ft, layout = "autofit")
```

\newpage
```{r regionalbio, fig.cap = "Trends in Tanner crab mature and legal biomass for the surveyed areas estimated from the current years catch-survey modeling using the pot survey data for Southeast Alaska.  Biomass estimates do NOT include non-surveyed areas (starting in 2015 Port Camden and Port Frederick were removed from the survey areas, they are not included in any biomass estimates here). Prior to 2001 the biomass of areas initially not surveyed (Thomas Bay, Glacier Bay), but added in subsequent years, is as estimated as their average percent contribution to the total surveyed biomass in all subsequent years (first year surveyed to current year’s survey)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/', cur_yr,'_figure1_curyr_data.png'), dpi = 125)
```

\newpage
```{r stdcpue, fig.cap = "Southeast Alaska commercial Tanner crab harvest and standardized commercial catch-per-unit-effort (CPUE) for 1991/1992 through 2020/2021 seasons. The x axis is represented by fishery year, e.g. 2018/2019 season is 2019 fishery year. CPUE was calculated using logbook data, which began during the 1993/1994 season.  Standardized CPUE was calculated by using a similar number of pot lifts for each year, based on the year (2008/2009) with the fewest number of pot lifts (12,521)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/', cur_yr,'_figure2.png'), dpi = 125)
```

```{r icy2, fig.cap = "Icy Strait Tanner crab survey area. Biomass estimates of legal and mature Tanner crab are based on catch-survey analysis methodologies. Commercial harvest is the total pounds harvested in associated and adjacent statistical areas. Reference lines represent long-term benchmark (1997-2006) for pre-recruit male (orange), recruit (blue), and post-recruit (grey) crabs. Reference line for biomass (dashed line) represents the long-term average (1997-2006) for legal biomass (lb). There is a significant short-term increasing trend for post-recruit CPUE (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/Icy Strait_', cur_yr, '_2confidential.png'), dpi = 125)
```

```{r icy3, fig.cap = "Female information for Icy Strait Tanner crab survey area. Reference lines represent long-term benchmark (1997-2006) values. There are no significant short-term trends for female measures."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/Icy Strait_', cur_yr, '_3confidential.png'), dpi = 125)
```

```{r glacier2, fig.cap = "Glacier Bay Tanner crab survey area. Biomass estimates of legal and mature Tanner crab are based on catch-survey analysis methodologies. Commercial harvest is the total pounds harvested in associated and adjacent statistical areas. Reference lines represent long-term benchmark (1997-2006) pre-recruit male (orange), recruit (blue), and post-recruit (grey) crabs. Reference line for biomass (dashed line) represents the long-term average (1997-2006) for legal biomass (lb). There are significant short-term decreasing trends for pre-recruit and recruit male CPUE (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/Glacier Bay_', cur_yr, '_2confidential.png'), dpi = 125)
```

```{r glacier3, fig.cap = "Female information for Glacier Bay Tanner crab survey area. Reference lines represent long-term benchmark (1997-2006) values. There are no significant short-term trends for females measures."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/Glacier Bay_', cur_yr, '_3confidential.png'), dpi = 125)
```

```{r thomas2, fig.cap = "Thomas Bay Tanner crab survey area. Biomass estimates of legal and mature Tanner crab are based on catch-survey analysis methodologies. Commercial harvest is the total pounds harvested in associated and adjacent statistical areas. Reference lines represent long-term benchmark (1997-2006) for pre-recruit male (orange), recruit (blue), and post-recruit (grey) crabs. Reference line for biomass (dashed line) represents the long-term average (1997-2006) for legal biomass (lb). There are significant short-term increasing trends for pre-recruit and recruit male CPUEs (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/Thomas Bay_', cur_yr, '_2confidential.png'), dpi = 125)
```

```{r thomas3, fig.cap = "Female information for Thomas Bay Tanner crab survey area. Reference lines represent long-term benchmark (1997-2006) values. There are significant short-term increasing trends mature female CPUE and the proportion of poor clutches (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/Thomas Bay_', cur_yr, '_3confidential.png'), dpi = 125)
```

```{r holkham2, fig.cap = "Holkham Bay Tanner crab survey area. Biomass estimates of legal and mature Tanner crab are based on catch-survey analysis methodologies. Commercial harvest is the total pounds harvested in associated and adjacent statistical areas. Reference lines represent long-term benchmark (1997-2006) for pre-recruit male (orange), recruit (blue), and post-recruit (grey) crabs. Reference line for biomass (dashed line) represents the long-term average (1997-2006) for legal biomass (lb). There is a significant short-term decreasing trend for recruit CPUE (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/Holkham Bay_', cur_yr, '_2confidential.png'), dpi = 125)
```

```{r holkham3, fig.cap = "Female information for Holkham Bay Tanner crab survey area. Reference lines represent long-term benchmark (1997-2006) values. There are no significant short-term trends in female measures."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/Holkham Bay_', cur_yr, '_3confidential.png'), dpi = 125)
```

```{r sp2, fig.cap = "Stephens Passage red king crab survey area. Biomass estimates of legal and mature Tanner crab are based on catch-survey analysis methodologies. Commercial harvest is the total pounds harvested in associated and adjacent statistical areas. Reference lines represent long-term benchmark (1997-2006) for pre-recruit male (orange), recruit (blue), and post-recruit (grey) crabs. Reference line for biomass (dashed line) represents the long-term average (1997-2006) for legal biomass (lb). There are significant short-term increasing trends for pre-recruit, recruit and post-recruit male CPUE (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/Juneau_', cur_yr, '_2.png'), dpi = 125)
```

```{r sp3, fig.cap = "Female information for Tanner crab in the Stephens Passage red king crab survey area. Reference lines represent long-term benchmark (1997-2006) values. There are NO significant short-term trends in either CPUE or the proportion of poor clutches (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/Juneau_', cur_yr, '_3.png'), dpi = 125)
```

```{r seymour2, fig.cap = "Seymour Canal red king crab survey area. Biomass estimates of legal and mature Tanner crab are based on catch-survey analysis methodologies. Commercial harvest is the total pounds harvested in associated and adjacent statistical areas. Reference lines represent long-term benchmark (1997-2006) for pre-recruit male (orange), recruit (blue), and post-recruit (grey) crabs. Reference line for biomass (dashed line) represents the long-term average for legal biomass (lb). There are no significant short-term trends in male CPUEs (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/tanner_rkc/', cur_yr, '/SC_2021_2confidential.png'), dpi = 125)
```

```{r seymour3, fig.cap = "Female information for Tanner crab in the Seymour Canal red king crab survey area. Reference lines represent long-term benchmark (1997-2006) values. There are no significant short-term trends in mature female CPUE or in the proportion of poor clutches (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/tanner_rkc/', cur_yr, '/SC_2021_3confidential.png'), dpi = 125)
```

```{r nj2, fig.cap = "North Juneau red king crab survey area. Biomass estimates of legal and mature Tanner crab based on catch-survey analysis methodologies. Commercial harvest is the total pounds harvested in associated and adjacent statistical areas. Reference lines represent long-term benchmark (1997-2006) for pre-recruit male (orange), recruit (blue), and post-recruit (grey) crabs. Reference line for biomass (dashed line) represents the long-term average (1997-2006) for legal biomass (lb). There are significant short-term increasing trends for pre-recruit and recruit male CPUEs (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/North Juneau_2021_2.png'), dpi = 125)
```

```{r nj3, fig.cap = "Female information for Tanner crab in the North Juneau red king crab survey area. Reference lines represent long-term benchmark (1997-2006) values. There is a significant short-term decreasing trend in the proportion of poor clutches (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/North Juneau_2021_3.png'), dpi = 125)
```

```{r ei2, fig.cap = "Excursion Inlet red king crab survey area. Biomass estimates of legal and mature Tanner crab based on catch-survey analysis methodologies. Commercial harvest is the total pounds harvested in associated and adjacent statistical areas. Reference lines represent long-term benchmark (1997-2006) for pre-recruit male (orange), recruit (blue), and post-recruit (grey) crabs. Reference line for biomass (dashed line) represents the long-term average for legal biomass (lb). There are no significant short-term trends for male CPUEs (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/tanner_rkc/', cur_yr, '/EI_2021_2confidential.png'), dpi = 125)
```

```{r ei3, fig.cap = "Female information for Tanner crab in the Excursion Inlet red king crab survey area. Reference lines represent long-term benchmark (1997-2006) values. There are no significant short-term trends in mature female CPUE or in the proportion of poor clutches (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/tanner_rkc/', cur_yr, '/EI_2021_3confidential.png'), dpi = 125)
```

```{r pybus2, fig.cap = "Pybus Bay red king crab survey area. Biomass estimates of legal and mature Tanner crab are based on catch-survey analysis methodologies. Commercial harvest is the total pounds harvested in associated and adjacent statistical areas. Reference lines represent long-term benchmark (1997-2006) for pre-recruit male (orange), recruit (blue), and post-recruit (grey) crabs. Reference line for biomass (dashed line) represents the long-term average for legal biomass (lb). There are no significant short-term trends (p < 0.05) for male CPUEs."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/tanner_rkc/', cur_yr, '/PB_2021_2confidential.png'), dpi = 125)
```

```{r pybus3, fig.cap = "Female information for Tanner crab in the Pybus Bay red king crab survey area. Reference lines represent long-term benchmark (1997-2006) values. There are NO significant short-term trend (p < 0.05) for either mature female CPUE or the proportion of poor clutches."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/tanner_rkc/', cur_yr, '/PB_2021_3confidential.png'), dpi = 125)
```

```{r gambier2, fig.cap = "Gambier Bay red king crab survey area. Biomass estimates of legal and mature Tanner crab are based on catch-survey analysis methodologies. Commercial harvest is the total pounds harvested in associated and adjacent statistical areas. Reference lines represent long-term benchmark (1997-2006) for pre-recruit male (orange), recruit (blue), and post-recruit (grey) crabs. Reference line for biomass (dashed line) represents the long-term average for legal biomass (lb). There is a significant short-term increasing trends (p < 0.05) for recruit male CPUE."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/tanner_rkc/', cur_yr, '/GB_2021_2confidential.png'), dpi = 125)
```

```{r gambier3, fig.cap = "Female information for Tanner crab in the Gambier Bay red king crab survey area. Reference lines represent long-term benchmark (1997-2006) values. There is a significant short-term decreasing trend in mature female CPUE (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/tanner_rkc/', cur_yr, '/GB_2021_3confidential.png'), dpi = 125)
```

```{r peril2, fig.cap = "Peril Strait red king crab survey area. Biomass estimates of legal and mature Tanner crab based on catch-survey analysis methodologies. Commercial harvest is the total pounds harvested in associated and adjacent statistical areas. Reference lines represent long-term benchmark (1997-2006) for pre-recruit male (orange), recruit (blue), and post-recruit (grey) crabs. Reference line for biomass (dashed line) represents the long-term average for legal biomass (lb). There is a significant short-term increasing trend (p < 0.05) for recruit male CPUE."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/tanner_rkc/', cur_yr, '/PS_2021_2confidential.png'), dpi = 125)
```

```{r peril3, fig.cap = "Female information for Tanner crab in the Peril Strait red king crab survey area. Reference lines represent long-term benchmark (1997-2006) values. There are no significant short-term trends in mature female CPUE or in the proportion of poor clutches (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/tanner_rkc/', cur_yr, '/PS_2021_3confidential.png'), dpi = 125)
```

```{r lynn2, fig.cap = "Lynn Sisters red king crab survey area. Biomass estimates of legal and mature Tanner crab based on catch-survey analysis methodologies. Commercial harvest is the total pounds harvested in associated and adjacent statistical areas. Reference lines represent long-term benchmark (1997-2006) for pre-recruit male (orange), recruit (blue), and post-recruit (grey) crabs. Reference line for biomass (dashed line) represents the long-term average for legal biomass (lb). There is a significant short-term trend for pre-recruit male CPUE (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/tanner_rkc/', cur_yr, '/LS_2021_2confidential.png'), dpi = 125)
```

```{r lynn3, fig.cap = "Female information for Tanner crab in the Lynn Sisters red king crab survey area. Reference lines represent long-term benchmark (1997-2006) values. There is a significant short-term decreaseing trend in mature female CPUE (p < 0.05)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/tanner_rkc/', cur_yr, '/LS_2021_3confidential.png'), dpi = 125)
```

\newpage
# Appendix A {-}


## Figures and Tables {-}
### Table A1: Regional biomass estimates from surveyed areas ONLY. The “`r cur_yr` model” reflects biomass estimates from the `r cur_yr` CSA models (displayed in Figure \@ref(fig:regionalbio)) and the “Annual Point Estimates” reflects the survey area biomass as a point estimate from each modeling year. {-}

```{r tableA1, results = "asis"}
#place this in from word doc "tanner_crab_tables.docx"
# current years model is from file C:\Users\kjpalof\Documents\SE_crab_assessments\results\tanner\2021\surveyed_areas_total_2021_model.csv
```


```{r regionalbio2, fig.cap = "Trends in Tanner crab mature and legal biomass for the surveyed areas estimated from each year’s projection or point estimate using the pot survey data for Southeast Alaska.  The points above reflect the survey area biomass as a point estimate from each modeling year, i.e. 2007 values are taken from the 2007 CSA model. Biomass estimates do NOT include non-surveyed areas (starting in 2015 Port Camden and Port Frederick were removed from the survey areas, they are not included in any biomass estimates here). Prior to 2001 the biomass of areas initially not surveyed (Thomas Bay, Glacier Bay), but added in subsequent years, is as estimated as their average percent contribution to the total surveyed biomass in all subsequent years (first year surveyed until current year’s survey)."}
knitr::include_graphics(paste0(here::here(),'/figures/tanner/', cur_yr, '/', cur_yr,'_figureA1_historic_data.png'), dpi = 125)
```

 
# References {-}
Bishop, G., C. Siddon, and A. Olson. 2013. Southeast Alaska Tanner crab survey and stock health prior to the 2011/2012 season. Regional information report No. 1J13-03. Alaska Department of Fish and Game, Division of Commercial Fisheries.

Clark, J.E. 2008. Restratification of the red king crab stock assessment survey in Southeast Alaska (pp.96). Juneau: Alaska Department of Fish and Game, Division of Commercial Fisheries.

Seber, G. A. F. 2002. The estimation of animal abundance, 2 edition. Blackburn Press, Caldwell, New Jersey.  654 pp.

Zheng, J., and G. H. Kruse. 1999. Evaluation of harvest strategies for Tanner crab stocks that exhibit periodic 
recruitment. Journal of Shellfish Research 18:667-679.
