---
title: "Tanner results from RKC survey"
author: "Caitlin Stern"
date: "October 2023"
output: html_document
---

```{r setup, include = FALSE}
library(knitr)
library(tidyverse)
cur_yr <- 2023
pr_yr <- cur_yr - 1

```

## CPUE from survey / data for CSA
```{r CPUE, echo = FALSE }
cpue_cur_yr <- read.csv(paste0(here::here(),'/results/tanner/tanner_rkc/', cur_yr, '/RKCS_CPUE_all.csv')) %>%
  filter(Year %in% c(pr_yr, cur_yr)) %>%
  select(-X)
kable(cpue_cur_yr, digits = 6)


# need to seperate time hauled to just have data hauled look for mid-date 
#dat[1,7] # 6-22
#dat[5097,7] # 6-29
# so mid-date would be 26th.
```

### Male weights from survey 
```{r weights, echo = FALSE }
male_weights <- read.csv(paste0(here::here(),'/results/tanner/tanner_rkc/', cur_yr, '/RKCS_weights.csv')) %>%
  filter(Year %in% c(pr_yr, cur_yr)) %>%
  select(-X)
kable(male_weights, digits = 3)
```

## Short term trends in CPUE
```{r short term, echo = FALSE }
short_term_results <- read.csv(paste0(here::here(),'/results/tanner/tanner_rkc/', cur_yr, '/shortterm.csv'))
kable(short_term_results, digits = 3)
```


## Long term trends in CPUE
```{r long term,echo = FALSE  }
long_term_results <- read.csv(paste0(here::here(),'/results/tanner/tanner_rkc/', cur_yr, '/long_term.csv')) %>%
  select(-X)
kable(long_term_results, digits = 3)
```

## Female health
#### percentage and SD of poor clutches (<25%)
```{r female health,echo = FALSE  }
poorclutch_curyr <- read.csv(paste0(here::here(),'/results/tanner/tanner_rkc/', cur_yr,'/RKCS_percent_low_clutch.csv')) %>%
  select(-X)
poorclutch_curyr %>% 
  filter(Year >= cur_yr-1) -> poorclutch_curyr

kable(poorclutch_curyr, digits = 3)
```


####long term mean comparison
```{r long term female, echo = FALSE}
lt_female <- read.csv(paste0(here::here(),'/results/tanner/tanner_rkc/', cur_yr,'/female_long_term.csv')) %>%
  select(-X)

kable(lt_female, digits = 3)
```

####short term females
```{r short term female, echo = FALSE}
short_female <- read.csv(paste0(here::here(),'/results/tanner/tanner_rkc/', cur_yr,'/female_shortterm.csv'))

kable(short_female, digits = 3)
```


####Mean egg percentage for mature females
```{r egg per female, echo = FALSE}
egg_per_mean <- read.csv(paste0(here::here(),'/results/tanner/tanner_rkc/', cur_yr,'/RKCS_percent_clutch.csv')) %>%
  select(-X)
egg_per_mean %>% 
  filter(Year >= cur_yr-1) -> egg_per_mean

kable(egg_per_mean, digits = 3)
```



## Stock health
```{r stock health, echo = FALSE}
stock_health <- read.csv(paste0(here::here(),'/results/tanner/tanner_rkc/', cur_yr,'/stock_health.csv'))

kable(stock_health, digits = 3)
```




