---
title: "Juneau area (11-A) red king crab assessment CONFIDENTIAL memo "
author: "Katie Palof, katie.palof@alaska.gov"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  bookdown::word_document2:
    fig_caption: yes
    includes: null
    toc: no
    reference_docx: style_settings.docx
  word_document:
    reference_docx: style_settings.docx
    toc: no
---
\pagenumbering{arabic}

```{r global_options, include=FALSE, echo = FALSE, message = FALSE, warning=FALSE}
library(knitr)
source(paste0(here::here(),'/code/functions.R'))
cur_yr = 2022
pr_yr = cur_yr-1
fut_yr = cur_yr+1
opts_chunk$set(fig.width = 12, fig.height = 7, echo = FALSE, warning = FALSE, message = FALSE,  dpi=300)

set_flextable_defaults(
  font.family = "Arial", 
  font.size = 9,
  font.color = "black",
  table.layout = "autofit",
  text.align = "center"
  #digits = 1,
  #theme_fun = "theme_box"
  )
#\pagenumbering{gobble}
```

```{r exesum, echo = FALSE}

biomass <- read.csv(paste0(here::here(),'/data/rkc/biomass.csv'))

````


# `r cur_yr` SUMMARY POINTS {-}
- A harvest rate of 7% was implemented for the 2020/2021 personal use and commercial fisheries; estimated actual harvest rate was 3.6% due to lack of a commercial fishery opening. In the prior two seasons similar harvest rates were implemented and the commercial fishery was closed resulting in an estimated actual harvest rate of 3.7% in the 2019/2020 season and 5.0% in the 2018/2019 season (this season had an 8% intended harvest rate). 
- Estimated legal (up 2.5%) and mature (up 4.5%) biomass both increased compared to 2020 predicted values. Legal biomass remains slightly above the long-term average (using baseline years), while mature biomass increased (small increase) for the first time since 2017. 
- Pre-recruit and recruit CPUEs increased from 2020 (16% and 45% respectively). Pre-recruit CPUE is still significantly below its long-term average, while recruit CPUE is at the long-term average. Post-recruit CPUE decreased (14% decrease from 2020) but is still significantly above its long-term average. 
- Juvenile CPUE was 7.65, the highest value on record since the early 90s, suggesting promise for future population growth given these crab continue to flourish. 
- A harvest rate of 7% for the 2021/2022 season will likely allow for a small increase (similar to the 2020/2021 season) in the abundance, while a harvest rate of 8% would likely allow for a steady state of abundance. Harvest rates above these would likely produce a decrease in abundance. These potential likelihoods are based on the recent population trajectory and the outcome of the last four years fisheries.
- It is recommended that harvest pressure not be increased until all male CPUEs increase to at least their long-term averages (using baseline years).   


# OVERVIEW {-}
