---
title: "Juneau area (11-A) red king crab assessment CONFIDENTIAL memo "
author: "Katie Palof, katie.palof@alaska.gov"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  bookdown::word_document2:
    fig_caption: yes
    includes: null
    toc: no
    reference_docx: style_settings.docx
  word_document:
    reference_docx: style_settings.docx
    toc: no
---
\pagenumbering{arabic}

```{r global_options, include=FALSE, echo = FALSE, message = FALSE, warning=FALSE}
library(knitr)
source(paste0(here::here(),'/code/functions.R'))
cur_yr = 2022
pr_yr = cur_yr-1
fut_yr = cur_yr+1
opts_chunk$set(fig.width = 12, fig.height = 7, echo = FALSE, warning = FALSE, message = FALSE,  dpi=300)

set_flextable_defaults(
  font.family = "Arial", 
  font.size = 9,
  font.color = "black",
  table.layout = "autofit",
  text.align = "center"
  #digits = 1,
  #theme_fun = "theme_box"
  )
#\pagenumbering{gobble}
```

```{r exesum, echo = FALSE}
# run code/CSA_model/JNU_RKC_masterfile_crabCSA....... for figures of cpue fit
biomass <- read.csv(paste0(here::here(),'/data/rkc/biomass.csv'))
biomass %>% 
  filter(Location == "Juneau") -> jnu_biomass
hindcast <- read.csv(paste0(here::here(), "./data/rkc/Juneau/hind_fore_cast_JNU_current.csv")) 

cpue <- read.csv(paste0(here::here(), '/results/rkc/Juneau/', cur_yr, '/JNU_CPUE_', cur_yr,'.csv'))

# change from previous year's forecasted values 
hindcast %>% 
  filter(year >= pr_yr) %>% 
  mutate(leg_change = round((legal_forecast - lag(legal_forecast))/ lag(legal_forecast)*100, 1), 
         mat_change = round((mature_forecast - lag(mature_forecast))/ lag(mature_forecast)*100, 1), 
         leg_cur_change = round((legal_curyr - lag(legal_curyr))/ lag(legal_curyr)*100, 1), 
         mat_cur_change = round((mature_curyr - lag(mature_curyr))/ lag(mature_curyr)*100, 1)) -> change_forecast

# cpue and change in cpue from last year
#cpue %>% 
#  gather(Rclass, cpue, Pre_Recruit_wt:SmallF_SE)
cpue_short <- as.data.frame(t(cpue))
cpue_short[2:13, ] -> cpue_short
colnames(cpue_short) <- c("2021", "2022")
cpue_short %>% 
  mutate(change = ((`2022` - `2021`)/`2021`)*100) -> cpue_short

cpue %>% 
  filter(Year == cur_yr) -> cpue2
```


# `r cur_yr` SUMMARY POINTS {-}
- A harvest rate of xx% was implemented for the `r pr_yr`/`r cur_yr` personal use and commercial fisheries; estimated actual harvest rate was xx% due to lack of a commercial fishery opening. In the prior three seasons similar harvest rates were implemented and the commercial fishery was closed resulting in an estimated actual harvest rate of 3.6% in 2020/2021, 3.7% in 2019/2020 and 5.0% in 2018/2019 (this season had an 8% intended harvest rate). 

- Estimated legal (up `r change_forecast$leg_change[2]`%) and mature (up `r change_forecast$mat_change[2]`%) biomass both increased compared to `r pr_yr` predicted values. Legal biomass remains slightly above the long-term average (using baseline years) and mature biomass is now above the long-term average after two consecutive years of increasing biomass.

- Pre-recruit CPUE increased substantially from `r pr_yr` (`r round(cpue_short$change[1], 1)` %), and is significantly above its long-term average. Both recruit and post-recruit CPUE decreased from `r pr_yr` (`r round(cpue_short$change[3], 1)` % and `r round(cpue_short$change[5], 1)` % respectively), with recruit CPUE falling significantly below the long-term average, and post-recruit CPUE at the long-term average. 

- Juvenile CPUE is `r cpue2$Juvenile_wt`, the highest value on record since the early 2000s, following a high CPUE in `r pr_yr`, which both suggest promise for future population growth given these crab continue to flourish. 

- A harvest rate of 7% for the `r cur_yr`/`r fut_yr` season will likely allow for a small increase (similar to the `r pr_yr`/`r cur_yr` season) in the abundance, while a harvest rate of 8% would likely allow for a steady state of abundance. Harvest rates above these would likely produce a decrease in abundance. These potential likelihoods are based on the recent population trajectory and the outcome of the last four years fisheries.

- It is recommended that harvest pressure not be increased until all male CPUEs increase to at least their long-term averages (using baseline years).   


# STOCK ASSESSMENT {-}
The following is a summary of the biomass estimates and stock status of red king crab (RKC) for the Juneau Area (Section 11-A) for the `r cur_yr`/`r fut_yr` season. Stock assessment methods for `r cur_yr` are identical to those used since 2012; however, in 2017 adjustments to historic (1993–2004) catch-per-unit-effort (CPUE) calculations were performed so that all CPUEs are now calculated using a stratified, weighted mean.  This corrected the long-term baseline (1993–2007) values used to determine stock health (Figs. 2a and 2b, Table 1), which in turn more accurately depicted the stock health status over time; this was specifically relevant for juvenile males and females. 

The biomass estimates for legal and mature RKC from a 3-stage catch-survey analysis (CSA) for the Juneau area are `r change_forecast$legal_curyr[2]` lb and `r change_forecast$mature_curyr[2]` lb respectively for the `r cur_yr` season (Fig. 1). This is a `r change_forecast$leg_change[2]`% increase in legal biomass and `r change_forecast$mat_change[2]`% increase in mature biomass from the `r pr_yr` predicted biomass levels (Fig. A1). Similarly using the `r cur_yr` model, where estimates of the historic biomass are calculated with data that includes up to the current year, there was an `r change_forecast$leg_cur_change[2]`% increase in legal biomass and a `r change_forecast$mat_cur_change[2]`% increase in mature biomass (Fig. 1). Pre-recruit CPUE increased substantially from `r pr_yr`, which suggests increase in juvenile CPUE last year are moving into the mature population. However, both recruit and post-recruit CPUE decreased from `r pr_yr`. While post-recruit CPUE decreased it still remains high, still significantly  above the long-term average. Recruit CPUE feel significantly below its long-term average, but large increases in pre-recruit CPUE suggest that we can likely expect recruit CPUE to increase in the coming years assuming current population productivity levels (Fig. 3a.). Model fit to the post-recruit survey CPUE has been poor in the last few years (Fig. 2), while fit to pre-recruit and recruit CPUEs was substantially better. This suggest more research is needed into Southeast red king crab life history, specifically growth increments and molting probabilities, to parameterize the underlying population dynamics more completely. 

The realized harvest rate in `r pr_yr` (3.1% of the mature biomass) allowed for growth in both legal and mature biomass, with legal biomass increasing slightly and mature biomass increasing more substantially from `r pr_yr`. Legal biomass estimates remain close to the long-term average and trends in recruitment – in the form of pre-recruit and recruit CPUE – are trending up from low levels in 2019. The increase in mature biomass pulls the value above the long-term average for the first time since 2017. All indicators suggest the population is likely to be stable or showing small increases at the current harvest pressure, additionally the large CPUE of juvenile and pre-recruit males indicate the potential for good recruitment in the next few years (Fig. 3a). 

The stock status for the Juneau area has increased to “healthy” from “above average” in `r pr_yr` (Table 1). The CPUEs of pre-recruit and post-recruit males, as well as juveniles males and females, are significantly above their long-term averages; CPUE of recruit males fell significantly below the baseline levels; and the CPUE of mature females is at the long-term average (using standardized baselines recalculated in 2017, Fig. 3a). There is evidence of a significant short-term (4-year) increase in juvenile male, juvenile female, pre-recruit and post-recruit CPUEs, and all other CPUEs are showing no significant trends in the last four years (Fig. 3a, Table 1). The clutch fullness of mature females remains high and few poor clutches were evident (Fig. 3b).  

Concern remains over the low CPUE for recruit males, which fell significantly below the long-term average (Table A3). However, increases in both juvenile and pre-recruit male and juvenile female CPUE suggest evidence of potential future recruitment in the population, assuming more of these individuals survive to “recruit” to the mature population. The point estimate CPUE of mature females is low compared to 2005 levels (one of the last years with a commercial fishery opening) but has been slowly increasing for the last few years. However, the variability about this CPUE declined from the late 90s early 2000s, suggesting that we are currently more precisely surveying this aspect of the population.  

Harvest of RKC in the Juneau area has been reduced below the equilibrium harvest rate of 17% (Fig. 4 – panel 1) every year since 2006 (Table 2). Although harvests have been small since then, previous increases in mature biomass were only observed in the years directly following full closures, where the harvest rate was zero of both the commercial and personal use fisheries (Fig.1, Table 2). However, increases in mature biomass were observed in the last two years with harvest pressure of approximately 3 to 3.6% applied.

Determining an appropriate harvest level for red king crab in Southeast Alaska, specifically the Juneau area, is a complex task. Prior to 2012 the matrix for stock health (Table 1) was used to suggest an appropriate harvest rate. In 2012 this was replaced with an equilibrium harvest rate that was calculated from the relationship between observed harvest rate and observed change in mature biomass. In theory (given a stable population with consistent growth and recruitment), this calculated equilibrium harvest rate would have an equal chance of producing an increase or decrease in the mature population size, therefore being a risk-neutral choice.  

Prior to the 2018 survey, the equilibrium harvest rate was re-analyzed using data up to the 2017/18 season. The results of this analysis, for the Juneau area, suggest an equilibrium harvest rate of 17%, which is the same as previous analyses (Fig. 4, panel 1).  Despite a statistically strong relationship (p <0.01) this estimate continues to have substantial variability. To understand this variability, the analysis was repeated on subsets of the data: years with declining/low abundance, years with increasing/high abundance, and the currently used baseline years (Fig. 4, panels 2-4). These subsets suggest a range of harvest rates from 6 to 25%, and these are presented as harvest options, except for 25% since throughout Alaska 20% is thought to be the maximum harvest that should be applied to mature king crab populations (Table 3). 

Recent explorations of the relationship between harvest rates and observed changes in mature biomass in the Juneau area suggest a strong AR1 process. Suggesting that the change in mature biomass under a specific harvest rate is strongly related to the mature biomass in the previous year and that we cannot set HRs independent of each other. Further exploration is underway to utilize this relationship in predicting an appropriate harvest rate. 
The model suggests healthier trends in biomass in recent years which may warrant higher harvest rates (17 – 20%), and the stock health matrix calculations suggest a harvest rate of 20% (Fig. 3, Table 1). The last two years' survey data suggests the potential of a strong recruitment pulse upcoming in the population. However, juvenile crab can be one to several molts away from entering into the mature biomass (molting to pre-recruit size), so it is hard to predict when this recruitment pulse will fully manifest in the mature population, some evidence of this was seen in this year's survey. Molting probability and growth are both linked to the health of the crab and their environment (food availability, temperature, etc.) and can be variable throughout Southeast Alaska. 

Low levels of recruit CPUE compared to long term trends, and under reporting of harvest in the personal use harvest reporting (25%,13%, 7%, 6%, 11%, 24%, and 21% of permits were not reported in previous personal use seasons, 2010, 2011, 2017, 2018, 2019, 2020, and 2021 respectively) and the subsequent decrease in mature biomass resulting from the 10% harvest rate in 2017 and 8% harvest rate in 2018 suggests a reduced harvest rate from the equilibrium rate of 17% or maximum 20%. 

The harvest rate of 10% that was applied in 2017 was enacted with the goal of allowing for population growth, since it was substantially lower than the 17% equilibrium harvest rate. The result was a decrease in the estimated mature biomass, therefore the harvest rate in 2018 was set at 8% once again allowing for overall population growth. However, the mature biomass has decreased following both openings, therefore a further reduction in harvest pressure to 7% was enacted in 2019. 

The 2019 and 2020 harvest rate (7%) produced a relatively stable biomass estimate for legal and mature crab, with small (less than 8% decrease or increase) fluctuation in both legal and mature biomass estimates depending on which model they were compared to, but the CPUEs of most mature male recruit classes showed an increase. Setting a harvest rate of 7%, the same level the last few seasona, would likely provide allow for some growth or stability in mature male biomass for the following season, which would be effective if the goal is to maintain the population at the current level. A harvest rate of less than 7% may allow for growth in the coming year. Harvest rates exceeding this would likely result in further population declines, with the probability of decrease and magnitude of the decline increasing proportional to the harvest rate. This population has only shown substantial improvements from 2013 to 2017, even though harvest has been severely reduced since 2008 (0, 0, 3%, 10%, 0, 0, 0, 0, 0, and 10% respectively). To encourage sustainability and population growth, a **7% or less harvest rate is recommended for the `r cur_yr/fut_yr` personal use season**. A GHL allocation table for multiple harvest rate strategies was constructed (Table 3). Although harvest rates of 20%, 17%, 10%, 8%, 7%, 6%, and 5% are shown, the data do not currently support the higher end of this range with the goal of sustaining average baseline population levels.

\newpage

# TABLES AND FIGURES {-}
```{r explain, include=FALSE, echo = FALSE, message = FALSE, warning=FALSE}
# Table 1 is updated from excel sheet (stock health matrix) in 'Tables RIR.docx' and brought into this document after it's knit

# Tables 2 to 3, are updated from CSA excel file and pulled in after knit to word

# when bring in tables not created here add page numbers and header

# Figure 4 is also carried over each year in JNU_t_and_f.docx

# appendix A - figures created here but tables in docx.
```


\newpage

```{r jnumodel, fig.cap = "Juneau Area biomass estimates for legal (black circles) and mature (gray points) red king crab from the current year’s 3-stage catch-survey analysis model. Black and grey (dashed) reference lines represent mean estimates during baseline years (1995¬¬–2007). Fishery status is reported in symbol type; closed status is when both commercial and personal use fishery are closed and PU only status indicates that only a PU fishery occurred (commercial fishery was closed in that year)."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr,'/juneau_fig1_', cur_yr, '.png'), dpi = 125)
```


```{r jnuCSA, fig.cap = "The current year’s CSA model fit. Both top and bottom left panels show model estimated survey CPUE (red lines) compared to calculated survey CPUE (black circles). Bottom right panel shows estimated stock abundance, which is also shown in Fig.1."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr,'/jnu_csa_', cur_yr,'.png'), dpi = 125)
```

```{r panel2, fig.cap = "Survey CPUE for male size/sex classes of red king crab along with biomass and harvest estimates for the Juneau Area from 1993–2020 – using the 2020 model output.  Reference lines indicate long-term averages, defined as the average CPUEs from 1995–2007.  There are no significant short-term (last 4-years) trends in mature male CPUEs. There is no mark-recapture adjustment for the Juneau area. "}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr,'/Juneau_', cur_yr, '_2.png'), dpi = 125)
```

```{r panel3, fig.cap = "Survey CPUE for female and juvenile size/sex classes of red king crab along with female percentage of poor clutches (% poor clutch) and overall clutch fullness (total % clutch).  Reference lines indicate long-term averages, defined as the average CPUEs from 1995–2007.  There are significant short-term trends increasing trends for juvenile male and female CPUEs."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr,'/Juneau_', cur_yr, '_3.png'), dpi = 125)
```


\newpage

# Appendix A. Historic record of annual model forecast {-}

```{r afig1, fig.cap = "Annual forecasts1 of Juneau Area biomass estimates for legal (black points) and mature (gray points) red king crab as annual point estimates (forecasts) from the 3-stage catch-survey analysis model. Black and grey (dashed) reference lines represent mean estimates during baseline years (1995–2007). Fishery status is reported in symbol type; closed status is when both commercial and personal use fishery are closed and PU only status indicates that only a PU fishery occurred (commercial fishery was closed in that year)."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr,'/juneau_figA1_', cur_yr, '.png'), dpi = 125)
```


