---
title: "2026 Southeast Alaska red king crab stock assessment CONFIDENTIAL RIR draft "
author: "Alex Reich (alex.reich@alaska.gov), Caitlin Stern, and Katie Palof"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  bookdown::word_document2:
    fig_caption: yes
    includes: null
    toc: no
    reference_docx: style_settings.docx
  #word_document:
    #reference_docx: style_settings.docx
    #toc: no
---
\pagenumbering{arabic}

```{r global_options, include=FALSE, echo = FALSE, message = FALSE, warning=FALSE}
library(knitr)
library(readxl)
library(officer)
library(officedown)
source(paste0(here::here(),'/code/functions.R'))
cur_yr = 2026 # updated annually
pr_yr = cur_yr-1
fut_yr = cur_yr+1
opts_chunk$set(fig.width = 12, fig.height = 7, echo = FALSE, warning = FALSE, message = FALSE,  dpi=300)

set_flextable_defaults(
  font.family = "Arial", 
  font.size = 9,
  font.color = "black",
  table.layout = "autofit",
  text.align = "center"
  #digits = 1,
  #theme_fun = "theme_box"
  )
#\pagenumbering{gobble}
```

```{r exesum, echo = FALSE}
mr_adjust <- read.csv(paste0(here::here(),'/data/rkc/adj_final_stock_assessment.csv'))
fishery.status <- read.csv(paste0(here::here(),'/data/rkc/Juneau/hind_fore_cast_JNU_current.csv')) # has fishery status
#                     may want to save this information somewhere else in the future
biomass <- read.csv(paste0(here::here(),'/data/rkc/biomass.csv'))
# file for all locations.  Has legal and mature biomass from current year CSA & harvest
# mr adjustments can be made in the function using mr_adjust file.
exploit_rate <- read.csv(paste0(here::here(),"/data/rkc/table3.csv"))

baseline_rel <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/relative_to_baseline_', cur_yr,'.csv'))
LEGAL_baseline_rel <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/LEGAL_relative_to_baseline_', cur_yr,'.csv')) #AGR add, surprised it wasn't here before
# which R file is this from ?

table2 <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/Table2_regional_', cur_yr,'.csv'))
table2.7 <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/Table2.7_regional_', cur_yr,'.csv'))#AGR added for legal #'s
# these are created in 'figure2_tables.R'
table3 <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/Table3_regional_', cur_yr,'.csv'))
table3.6 <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/Table3.6_regional_', cur_yr,'.csv'))

tableA3 <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/TableA3_regional_', cur_yr,'.csv'))
#table4 <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/Table4_regional_2021.csv'))
regpu <- read.csv(paste0(here::here(),'/data/harvest/', cur_yr, '_regional_PU_harvest.csv'))

###
## clean up figure 2-------
# add in mr adjustments
mr_adjust %>% 
  select(-X) %>% 
  mutate(Location = ifelse(area == "St_James", "LynnSisters", as.character(area))) %>% 
  select(-area) -> mr_adjust2
biomass %>% 
  left_join(mr_adjust2) %>% 
  mutate(adj.legal = ifelse(Location == "Juneau", legal.biomass, 
                            legal.biomass*weighted_ADJ), 
         adj.mature = ifelse(Location == "Juneau", mature.biomass, 
                            mature.biomass*weighted_ADJ))-> biomass
#write.csv(biomass, paste0('./results/rkc/Region1/', cur_yr, '/biomass_', cur_yr, '.csv'))
# use these values for Table A2 in stock health document

# regional biomass ----
biomass %>% 
  group_by(Year) %>% 
  summarise(legal = sum(legal.biomass), mature = sum(mature.biomass), 
            adj_legal = sum(adj.legal), adj_mature = sum(adj.mature)) %>% 
  as.data.frame() -> regional.b
fishery.status %>% 
  select(Year = year, status) %>% 
  mutate(status = ifelse(status == "PU only", "closed", as.character(status))) -> fishery.status.update
  # add next line to deal with current year which is TBD in file but will most 
  # likely be closed in current year (2018)
  # %>% mutate(status = ifelse(status == "TBD", "closed", as.character(status))) -> fishery.status.update
   
regional.b %>% 
  left_join(fishery.status.update) -> regional.b

## expansion factor for non-surveyed areas ----
regional.b %>% 
  mutate(non_sur_legal = (legal/.528) - legal, 
         non_sur_mature = (mature/0.528) - mature, 
         non_sur_adj_legal = (adj_legal/.528) - adj_legal, 
         non_sur_adj_mature = (adj_mature/0.528) - adj_mature, 
         bkc_leg = legal*0.0106, 
         bkc_mat = mature*0.0106, 
         bkc_adj_leg = adj_legal*0.0106, 
         bkc_adj_mat = adj_mature*0.0106, 
         TOTAL_leg = (adj_legal + non_sur_adj_legal + bkc_adj_leg), 
         TOTAL_mat = (adj_mature + non_sur_adj_mature + bkc_adj_mat)) -> regional.b_table


regional.b_table %>% filter(Year == cur_yr) -> b_cur_yr

## harvest rate summary ----
exploit_rate %>% 
  select(area, equ.er.adj, avg.inc.hr, alt.equ.hr) %>% 
  mutate(equ.er.adj = round(equ.er.adj, 2), avg.inc.hr = round(avg.inc.hr, 2), 
         alt.equ.hr = round(alt.equ.hr, 2), 
         hr_cur_yr = ifelse(area == 'Juneau', 0.07, 0)) -> exploit_rate2
## look into doing these calcs in figure2_tables instead and bringing in csv here

```
```{r harvestrec.prep, echo = FALSE}

# prepare harvest recommendations table so can pull numbers from it for text

survey.locations <- c("Pybus", "Excursion", "Gambier", "Juneau", 
                      "LynnSisters", "Peril", "Seymour")

# input mature harvest rates. These are determined from stock health & the previous year's results.
# the Juneau harvest rate should be the one decided upon in the Juneau assessment meeting in July.
#AGR I did not update in 2024 because not relevant, we use legal hr
##AGR likely obsolete below -2026
pybus_hr <- 0
gambier_hr <- 0
seymour_hr <- 0
peril_hr <- 0
juneau_hr <- 0.09 #updated 2026 UPDATE EACH YEAR!!
lynnsisters_hr <- 0
excursion_hr <- 0
bkc_hr_display <- 0
other_hr <- 0.10
total_hr <- NA

#UPDATE THE BELOW CHUNK EACH YEAR
# input legal harvest rates. These are determined from stock health & the previous year's results.
# the Juneau harvest rate should be the one decided upon in the Juneau assessment meeting in July.
#AGR 2025- FLAG - take a look and update manually...#AGR 2026- update manually - TK FLAG!!
pybus_hr_leg <- 0 #agr updated to legal stock harvest rates 2024
gambier_hr_leg <- 0.04
seymour_hr_leg <- 0.1 #debated 0.05 but went with 0.10
peril_hr_leg <- 0
juneau_hr_leg <- 0.09 #2025 number UPDATE EACH YEAR
lynnsisters_hr_leg <- 0.09
excursion_hr_leg <- 0
bkc_hr_display_leg <- 0
other_hr_leg <- 0.10
total_hr_leg <- NA

bkc_hr <- 0.0106 # note that this represents expected BKC bycatch in the RKC fishery, not a directed harvest rate on BKC.

tbl7_a <- table2 #TK what is going on here AGR #I didn't like table 2 for some reason. Check it has the legal values and calcs that we need please
tbl7_b <- tbl7_a %>% 
  mutate(adj.legal = round(adj.legal, 0), adj.mature = round(adj.mature, 0)) %>% 
  select(-Year, -Legal.HR) %>% 
  filter(Location != "surveyed")

tbl7_c <- tbl7_b %>% 
  mutate(Mature.HR = c(pybus_hr, gambier_hr, seymour_hr, peril_hr, juneau_hr, lynnsisters_hr, excursion_hr, bkc_hr_display, other_hr, total_hr), Legal.HR = c(pybus_hr_leg, gambier_hr_leg, seymour_hr_leg, peril_hr_leg, juneau_hr_leg, lynnsisters_hr_leg, excursion_hr_leg, bkc_hr_display_leg, other_hr_leg, total_hr_leg)) %>% 
  mutate(Total.GHL = round(adj.mature*Mature.HR,0), 
         Total.GHL.legal = round(adj.legal*Legal.HR,0), 
         PU.catch = ifelse(Location == "Juneau", 
                           round(0.6*Total.GHL,0), ifelse(Location == "other.areas", 1000, 0)),
         PU.catch.legal = ifelse(Location == "Juneau", 
                           round(0.6*Total.GHL.legal,0), ifelse(Location == "other.areas", 1000, 0)),
         Comm.GHL.adj = round(Total.GHL - PU.catch, 0), 
         Comm.GHL.adj.legal = round(Total.GHL.legal - PU.catch.legal, 0), 
         bkc_temp = round(sum(Comm.GHL.adj[Location%in%survey.locations], na.rm = TRUE)*bkc_hr, 0), 
         bkc_temp.legal = round(sum(Comm.GHL.adj.legal[Location%in%survey.locations], na.rm = TRUE)*bkc_hr, 0), 
         Comm.GHL.adj = ifelse(Location == "bkc", bkc_temp, Comm.GHL.adj),
         Comm.GHL.adj.legal = ifelse(Location == "bkc", bkc_temp.legal, Comm.GHL.adj.legal)) %>%
  select(-bkc_temp)

tbl7_d <- tbl7_c %>% 
  mutate(Comm.GHL.adj = ifelse(Location == "total", sum(tbl7_c$Comm.GHL.adj, na.rm = TRUE), Comm.GHL.adj),
         Comm.GHL.adj.legal = ifelse(Location == "total", sum(tbl7_c$Comm.GHL.adj.legal, na.rm = TRUE), Comm.GHL.adj.legal),
         Total.GHL = ifelse(Location == "total", sum(tbl7_c$Total.GHL, na.rm = TRUE), Total.GHL),
         Total.GHL.legal = ifelse(Location == "total", sum(tbl7_c$Total.GHL.legal, na.rm = TRUE), Total.GHL.legal),
         PU.catch = ifelse(Location == "total", sum(tbl7_c$PU.catch, na.rm = TRUE), PU.catch),
         PU.catch.legal = ifelse(Location == "total", sum(tbl7_c$PU.catch.legal, na.rm = TRUE), PU.catch.legal)) %>% 
  select(Location, adj.legal, adj.mature, Mature.HR, Total.GHL, PU.catch, Comm.GHL.adj, Legal.HR, Total.GHL.legal, PU.catch.legal, Comm.GHL.adj.legal) %>%
  mutate(Location = case_when(Location == "Pybus" ~ "Pybus Bay", 
                              Location == "Gambier" ~ "Gambier Bay",
                              Location == "Seymour" ~ "Seymour Canal",
                              Location == "Peril" ~ "Peril Strait",
                              Location == "LynnSisters" ~ "Lynn Sisters",
                              Location == "Excursion" ~ "Excursion Inlet",
                              Location == "bkc" ~ "BKC",
                              Location == "other.areas" ~ "Other areas",
                              Location == "total" ~ "Total",
                              .default = as.character(Location)))


names(tbl7_d) <- c("Survey area", "Legal biomass (adj)", "Mature biomass (adj)", "Mature HR", 
               "Total GHL (mature lb)", "PU harvest (mature lb)", paste0(cur_yr, " Commercial GHL (mature lb)"), "Legal HR",
               "Total GHL (legal lb)", "PU harvest (legal lb)", paste0(cur_yr, " Commercial GHL (legal lb)"))

# alternative table with only one harvest rate, applied to legal biomass. Keep 0.10 as the rate applied to legal biomass for the Juneau- #AGR ummm, this might be out of date for 2024, 0.08 is the 2024 harvest rate#
# area. Change the harvest rate applied to legal biomass from other areas such that the GHL is the same as it would be if a 0.10 harvest #AGR - WHAT IS THIS RIDDLE?
# rate was applied to the mature biomass from other areas. 
#AGR - ok the alt table was made at a manager's request and was not a biometric rec. I got rid of the table in 2024.

other_hr_leg_alt <- tbl7_d %>%
  filter(`Survey area` == "Other areas") %>%
  mutate(newHR = `Total GHL (mature lb)`/`Legal biomass (adj)`) %>%
  pull(newHR)

tbl7_c_alt <- tbl7_b %>% 
  mutate(Legal.HR = c(pybus_hr_leg, gambier_hr_leg, seymour_hr_leg, peril_hr_leg, juneau_hr_leg, lynnsisters_hr_leg, excursion_hr_leg, bkc_hr_display_leg, other_hr_leg_alt, total_hr_leg)) %>% 
  mutate(Total.GHL.legal = round(adj.legal*Legal.HR,0), 
         PU.catch.legal = ifelse(Location == "Juneau", 
                           round(0.6*Total.GHL.legal,0), ifelse(Location == "other.areas", 1000, 0)),
         Comm.GHL.adj.legal = round(Total.GHL.legal - PU.catch.legal, 0), 
         bkc_temp.legal = round(sum(Comm.GHL.adj.legal[Location%in%survey.locations], na.rm = TRUE)*bkc_hr, 0), 
         Comm.GHL.adj.legal = ifelse(Location == "bkc", bkc_temp.legal, Comm.GHL.adj.legal))

tbl7_d_alt <- tbl7_c_alt %>% 
  mutate(Comm.GHL.adj.legal = ifelse(Location == "total", sum(tbl7_c_alt$Comm.GHL.adj.legal, na.rm = TRUE), Comm.GHL.adj.legal),
         Total.GHL.legal = ifelse(Location == "total", sum(tbl7_c_alt$Total.GHL.legal, na.rm = TRUE), Total.GHL.legal),
         PU.catch.legal = ifelse(Location == "total", sum(tbl7_c_alt$PU.catch.legal, na.rm = TRUE), PU.catch.legal),
         Legal.HR = round(Legal.HR, 2)) %>% 
  mutate(Location = case_when(Location == "Pybus" ~ "Pybus Bay", 
                              Location == "Gambier" ~ "Gambier Bay",
                              Location == "Seymour" ~ "Seymour Canal",
                              Location == "Peril" ~ "Peril Strait",
                              Location == "LynnSisters" ~ "Lynn Sisters",
                              Location == "Excursion" ~ "Excursion Inlet",
                              Location == "bkc" ~ "BKC",
                              Location == "other.areas" ~ "Other areas",
                              Location == "total" ~ "Total",
                              .default = as.character(Location))) %>%
  select(Location, adj.legal, adj.mature, Legal.HR, Total.GHL.legal, PU.catch.legal, Comm.GHL.adj.legal)


names(tbl7_d_alt) <- c("Survey area", "Legal biomass (adj)", "Mature biomass (adj)", "Legal HR",
               "Total GHL (legal lb)", "PU harvest (legal lb)", paste0(cur_yr, " Commercial GHL (legal lb)"))


```



```{r numbers.for.text, echo = FALSE}

# *************************************************************************************
# Quick summary ----

files_sh <- c(paste0(here::here(), "/results/rkc/Pybus/", cur_yr, "/stock_health.csv"), 
                    paste0(here::here(), "/results/rkc/Gambier/", cur_yr, "/stock_health.csv"), 
                    paste0(here::here(), "/results/rkc/Seymour/", cur_yr, "/stock_health.csv"), 
                    paste0(here::here(), "/results/rkc/Peril/", cur_yr, "/stock_health.csv"), #TURN ON IF WE SURVEY PERIL THIS YEAR. TURN OFF IF WE DON'T
                    paste0(here::here(), "/results/rkc/Juneau/", cur_yr, "/stock_health.csv"), 
                    paste0(here::here(), "/results/rkc/LynnSisters/", cur_yr, "/stock_health.csv"),
                    paste0(here::here(), "/results/rkc/Excursion/", cur_yr, "/stock_health.csv"))

sh_list <- files_sh %>%
  map(read.csv) 
names(sh_list) <- c("Pybus", "Gambier", "Seymour", "Juneau", "LynnSisters", "Excursion", "Peril") #add "Peril" in peril-surveyed years please.

sh_all <- do.call(rbind, Map(cbind.data.frame, Location = names(sh_list), sh_list))
row.names(sh_all) <- NULL

pybus_stockhealth <- sh_all %>% filter(location == "Pybus") %>% pull(health_status)
gambier_stockhealth <- sh_all %>% filter(location == "Gambier") %>% pull(health_status)
seymour_stockhealth <- sh_all %>% filter(location == "Seymour") %>% pull(health_status)
peril_stockhealth <- sh_all %>% filter(location == "Peril") %>% pull(health_status) # use this in years with a Peril survey
#peril_stockhealth <-  "unsurveyed" # use this in years without a Peril survey
juneau_stockhealth <- sh_all %>% filter(location == "Juneau") %>% pull(health_status)
lynnsisters_stockhealth <- sh_all %>% filter(location == "LynnSisters") %>% pull(health_status)
excursion_stockhealth <- sh_all %>% filter(location == "Excursion") %>% pull(health_status)

# *************************************************************************************
# Overview ----

# pounds and numbers of crab targeted in the Juneau summer personal use fishery

# input the Juneau mature harvest rate (decided upon in the Juneau assessment meeting in July)
#probs obsolete below- AGR 2026
juneau_hr <- 0.09 #updated AGR #CRAP, is this # wrong? since the legal rate is 0.10, the mature rate will be lower
##this # might not be used tho, so pay attention. FLAG!!

# input the Juneau legal harvest rate
juneau_hr_legal <- 0.09 #UPDATE EACH YEAR - updated 2026

# summer PU proportion of the GHL (= 0.5; winter PU is 0.1 and commercial is 0.4)
sum.pu.prop <- 0.5 #Same each year

# get legal weight for conversion to numbers
leg.wt <- read.csv(paste0(here::here(),'/results/rkc/Juneau/', cur_yr, '/maleweights.csv')) %>% #this gets auto-created by everything I did for the Juneau memo
  filter(Year == cur_yr) %>%
  pull(legal_lbs)

# legal male lbs for Juneau total PU #TK This is wrong #WHAT? FLAG 2025
lbs.leg.pu.total <- tbl7_d_alt %>%
  filter(`Survey area` == "Juneau") %>%
  mutate(pu.harvest = `PU harvest (legal lb)`) %>%
  pull(pu.harvest)

# legal male lbs for Juneau summer PU #TK this is wrong #FLAG!! 2025
lbs.leg.pu <- tbl7_d_alt %>%
  filter(`Survey area` == "Juneau") %>%
  mutate(pu.harvest = sum.pu.prop*`PU harvest (legal lb)`) %>%
  pull(pu.harvest)

num.leg.pu <- lbs.leg.pu / leg.wt

# Commercial GHL in legal pounds- AGR this isnt right TK

ghl.bkc <- tbl7_d %>% filter(`Survey area` == "BKC") %>% pull(paste0(cur_yr, " Commercial GHL (legal lb)"))
ghl.total <- tbl7_d %>% filter(`Survey area` == "Total") %>% pull(paste0(cur_yr, " Commercial GHL (legal lb)"))
comm.ghl.leg <- ghl.total - ghl.bkc

# *************************************************************************************
# Summary of stock status ----

# change in regional legal and mature biomass

reg_bio_change_leg <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/change_in_modeled_regional_biomass_', cur_yr,'.csv')) %>%
  filter(type == "adj_legal") %>% select("change") %>% pull()

reg_bio_change_mat <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/change_in_modeled_regional_biomass_', cur_yr,'.csv')) %>%
  filter(type == "adj_mature") %>% select("change") %>% pull()

reg_bio_change_leg_sign <- ifelse(reg_bio_change_leg > 0, "increased", "decreased")
reg_bio_change_mat_sign <- ifelse(reg_bio_change_mat > 0, "increased", "decreased")


# average regional decline in legal biomass since 2017

files_regch <- c(paste0(here::here(), "/results/rkc/Region1/2019/change_in_modeled_regional_biomass_2019.csv"), 
                    paste0(here::here(), "/results/rkc/Region1/2020/change_in_modeled_regional_biomass_2020.csv"), 
                    paste0(here::here(), "/results/rkc/Region1/2021/change_in_modeled_regional_biomass_2021.csv"), 
                    paste0(here::here(), "/results/rkc/Region1/2022/change_in_modeled_regional_biomass_2022.csv"), 
                    paste0(here::here(), "/results/rkc/Region1/2023/change_in_modeled_regional_biomass_2023.csv"),
                    paste0(here::here(), "/results/rkc/Region1/2024/change_in_modeled_regional_biomass_2024.csv"),
                    paste0(here::here(), "/results/rkc/Region1/2025/change_in_modeled_regional_biomass_2025.csv"),
                 paste0(here::here(), "/results/rkc/Region1/2026/change_in_modeled_regional_biomass_2026.csv")
                 ) #AGR added TK- in the spirit of copy paste and pattern matching

regch_list <- files_regch %>%
  map(read.csv) 
names(regch_list) <- c("2019", "2020", "2021", "2022", "2023", "2024", "2025", "2026") #AGR added 2024, and a year later 2025 - I probs will drop the earlier years off the table. Added 2026 in 2026
type_change <- c("type", "change")
regch_list2 <- lapply(regch_list, "[", , type_change)
regch_all <- do.call(rbind, Map(cbind.data.frame, name = names(regch_list2), regch_list2))
row.names(regch_all) <- NULL

avg_change_legal <- regch_all %>%
  filter(type == "adj_legal") %>%
  summarise(mean_change = mean(change)) %>% pull()

avg_change_mature <- regch_all %>%
  filter(type == "adj_mature") %>%
  summarise(mean_change = mean(change)) %>% pull()

avg_change_legal_sign <- ifelse(avg_change_legal > 0, "increased", "declined")
avg_change_mature_sign <- ifelse(avg_change_mature > 0, "increased", "declined")



```


FYI: *information is not completed yet; this is a draft of the RIR for both research (biometrics) and management. Management sections are also labeled TBD in this draft.*


# `r cur_yr` QUICK SUMMARY {-}
  - Regional legal and mature RKC biomass increased by `r round(reg_bio_change_leg, 0)`% and `r round(reg_bio_change_mat, 0)`% respectively in `r cur_yr`.
  - Stock health was above average in the Juneau Area (section 11-A); moderate in Lynn Sisters and Seymour Canal, below average in Gambier Bay and Peril Strait; poor in Excursion Inlet and Pybus Bay. Stock health considers all age/sex classes of the population (mature males, juveniles, and females).
  - Gambier Bay, the Juneau Area, and Seymour Canal showed increases in legal biomass from `r pr_yr`, while by-area mature biomass estimates were either near or below `r pr_yr` levels. 
  - This pattern is consistent with the trends noted in the Juneau Area `r cur_yr` memo, with recruit and postrecruit males aging through the population without sufficient biomass of prerecruits or juveniles to replace them. Biomass estimates, while currently high, may fall once the abundant recruit and postrecruit cohorts are removed. 
  - The expanded regional legal biomass estimate was above the long-term median (Figure \@ref(fig:med1)). Managers can consult Tables 1, A1, and A2 when setting the commercial GHL; we recommend harvest rates at or below last year's levels, and the data would support a GHL above 200,000 lb should managers choose to open the full commercial fishery.

# OVERVIEW {-}
The Alaska Department of Fish and Game (ADF&G) annually evaluates stock status and establishes the guideline harvest levels (GHLs) for the Southeast red king crab (RKC) and blue king crab (BKC) fishery using data from fishery-independent surveys (pot gear), commercial fishery catch per unit of effort (CPUE), and biological data (length, weight, and shell condition) from the surveys and the fishery. The Southeast Alaska management area (Registration Area A) consists of all waters defined in 5 AAC 34.100 (Figure \@ref(fig:distribution)). 

For the `r cur_yr`-`r fut_yr` season, the estimate of regional legal male biomass was **`r round(b_cur_yr$TOTAL_leg/1000000, 2)` million lb** and regional mature male biomass was **`r round(b_cur_yr$TOTAL_mat/1000000, 2)` million lb** (Table \@ref(tab:harvestrec), Figure \@ref(fig:regionalbio)). These values were determined using mark–recapture adjustments and the historical expansion factor applied to the non-surveyed areas (Table \@ref(tab:bioadj)). The legal and mature male biomass estimates were below their baseline levels, defined as the average biomass from 1995-2007, but there were short-term increasing trends in recent years for both biomass estimates. The legal male biomass estimate is above the long-term median (3.0 million lb; Figure \@ref(fig:med1)).

The `r cur_yr`-`r fut_yr` Southeast commercial RKC fishery GHL was *TBD* lb of legal male RKC, *TBD (above/below) the 200,000 lb minimum threshold [5 AAC 34.113] required to open a commercial fishery- text needs to be updated as relevant to 2026/27*; 3 of the 7 surveyed areas had notable increases in legal biomass. Therefore, the commercial fishery *TBD (opened/closed)* for the `r cur_yr`-`r fut_yr` season (Table \@ref(tab:harvestrec) and Figure \@ref(fig:med1)).

The personal use RKC and BKC fishery opened July 1, `r cur_yr`, in non-surveyed areas with daily bag and possession limits of one RKC or BKC per person. Results from the annual stock assessment survey in the Juneau Area indicated that stock health was above average, with both legal and mature biomass estimated to be above the long-term average. The personal use summer fishery in Section 11-A opened on August 14, 2026, for ten days with a seasonal household limit of three red or blue male king crab and daily bag and possession limit of three crab to target 27,606 lb (3,572 crab) of legal male RKC in the summer fishery.

# `r cur_yr` SOUTHEAST RED KING CRAB STOCK ASSESSMENT {-}

## SUMMARY OF STOCK STATUS {-}
The Southeast RKC stock assessment regional biomass estimates for the `r cur_yr`/`r fut_yr` season were **`r round(b_cur_yr$TOTAL_leg/1000000, 2)` million lb of legal male RKC and `r round(b_cur_yr$TOTAL_mat/1000000, 2)` million lb of mature male RKC**, using the historical expansion factor (Table \@ref(tab:bioadj)). The legal biomass estimate `r reg_bio_change_leg_sign` `r round(reg_bio_change_leg, 0)`% from the previous year using the `r cur_yr` model estimates (Figure \@ref(fig:regionalbio)). The mature biomass estimate `r reg_bio_change_mat_sign` `r round(reg_bio_change_mat, 0)`% from `r pr_yr` using the `r cur_yr` model estimates. 

Survey area biomass is estimated using a three-stage catch survey analysis (CSA) model and adjusted using the mark-recapture expansions where available (Stratman et al. 2019; Palof et al. 2025). Sample sizes and numbers of pots set and sampled varied among the survey areas and determined using a Neyman allocation based on the variance of total crab CPUE survey estimates by stratum between 2021 and 2023, which is updated using new data every 3 years (Table \@ref(tab:samplesizes)). The legal crab component is composed of recruit and postrecruit crab and defined as those crab greater than or equal to 145 mm in carapace length. The mature crab component is composed of prerecruit, recruit, and postrecruit crab, and defined as crab greater than or equal to 129 mm in carapace length. Biomass estimates from the survey areas were expanded based on assumptions of how representative these areas are of the entire population in Southeast (Table \@ref(tab:harvestrec) and Figure \@ref(fig:distcur)). Holkham Bay has not been surveyed since 2015 due to survey funding reductions and therefore is no longer included in determining survey biomass estimates. Port Frederick was not surveyed from 2015 to 2024, but was added as a biennial survey site in 2025. Port Frederick was not used in the survey biomass estimate this year but may be included in the estimate after additional years of survey data collection.

Both mature and legal survey biomasses declined from 2001–2013 (Figure \@ref(fig:regionalbio)). Legal and mature biomasses showed regionwide increases in 2015 and continued to increase until 2017. In 2017, the commercial fishery opened and the regionwide stock decreased until 2022. From 2023 to present, the legal and mature regional biomasses both increased annually, although the 2026 mature biomass estimate is close to the 2025 estimate. This year, three of the seven surveyed areas (Juneau Area, Gambier Bay, and Seymour Canal) had increases in legal biomass. The legal biomass slightly increased for Pybus Bay, was close to the 2025 estimate for Excursion Inlet, and decreased for Lynn Sisters and Peril Strait. While Seymour Canal saw a small increase in mature biomass, mature biomass was either stable or decreasing for all other surveyed areas (Figures \@ref(fig:pybus2) – \@ref(fig:excursion3)).

The juvenile male CPUEs were significantly below average for all survey areas excluding the Juneau Area, where the CPUE was non-significantly different from the long-term average (Table \@ref(tab:longterm)). The juvenile female CPUEs were non-significantly different from the long-term average for Gambier Bay, Seymour Canal, and Juneau, and were below the long-term average for all other survey areas (Table \@ref(tab:longterm)). Mature female CPUEs were non-significantly different from the long-term average for Gambier Bay, Seymour Canal, Juneau, and Lynn Sisters, and below the long-term average for all other areas (Table \@ref(tab:longterm)). This survey was not designed to target juveniles, but the low observed abundance of juvenile males is notable and may indicate low recruitment in the coming years.

Mature male recruit and postrecruit male CPUEs were above average for the Juneau Area and Seymour Canal (Table \@ref(tab:longterm)). Postrecruit male CPUE was non-significantly different from the long-term average for Lynn Sisters and Peril Strait, and below average for Pybus Bay, Gambier Bay, and Excursion Inlet (Table \@ref(tab:longterm)). Recruit male CPUEs were non-significantly different from the long-term average for Gambier Bay and Seymour Canal, and below the long-term average for Pybus Bay, Excursion Inlet, and Peril Strait (Table \@ref(tab:longterm)). Prerecruit male CPUEs were non-significantly different from the long-term average for the Juneau Area and Lynn Sisters and below the long-term average for all other areas (Table \@ref(tab:longterm)). Observed reductions in the prerecruit males indicate the potential for declining recruit and postrecruit abundances in future years.

A matrix of stock health indicators provides an objective and repeatable evaluation of the survey data. A five-year summary of matrix results is therefore presented in Table \@ref(tab:health5year). The methods used to calculate stock health indicators are described in Siddon et al. (2009); note that stock health score categories changed after 2008 (Table \@ref(tab:healthscores)).


## MARK–RECAPTURE EXPERIMENT ADJUSTMENTS {-}
All survey areas (Excursion Inlet, Lynn Sisters, Peril Strait, Pybus Bay, Gambier Bay, and Seymour Canal; Figure \@ref(fig:distcur)), except Juneau, due to its expansive area, have a biomass adjustment that is calculated from mark-recapture studies (Table \@ref(tab:bioadj)). Two of the six survey areas have a single mark-recapture event, while the other four have two events; therefore, the estimate of biomass using this method does not consider the extensive interannual variability or variability in population size for all areas and should be applied with caution. 
ADF&G does not currently plan to continue with additional mark-recapture studies. 
Mark-recapture attempts in 2013 and 2014 (Lynn Sisters and Excursion Inlet) did not have sufficient sample sizes to produce usable biomass estimates by the sample size metrics recommended by Robson and Regier (1964).
Where two mark-recapture adjustments are available in a given survey area, a weighted average was used to determine the final mark-recapture adjustment (Table \@ref(tab:bioadj)). 
The biomass estimates presented in this analysis are the `r cur_yr` CSA model estimates adjusted by these values. 


## EXPANSION OPTION FOR NON-SURVEYED AREAS {-}
Regional biomass is estimated from the seven survey areas and extrapolated to the entire region using an expansion factor defined as the proportion of the population that lies within the non-surveyed areas. In 2015, the surveyed areas were adjusted since surveys in Port Frederick and Holkham Bay were discontinued due to reduced funding. The removal of Port Frederick from the survey is accounted for by placing it in the non-surveyed area designation. Port Frederick was surveyed in 2025 but will still be treated as a non-surveyed area this year until more years of recent data are available. A biomass estimate has never been produced for Holkham Bay due to the inconsistency of the data. Holkham Bay has always been included as a non-surveyed area and thus no changes to the biomass estimation were needed in removing Holkham Bay from the survey.   

The expansion factor, or an estimate of the percentage of the population found in the non-surveyed areas using historical harvest data, has not been consistent over time (Palof and Stratman 2020). 
In the past, two expansion factors have been used that represented historical harvests from 1974–1984 (with 47.2% of the harvest coming from the non-surveyed areas), and harvests during the formerly used baseline years 1993–2007 (with 36.1% of the harvest coming from the non-surveyed areas). 
The historical harvest time frame (1974–1984) was chosen to be the most appropriate for the `r cur_yr` assessment since it includes harvest years before management actions dictated spatial closure or influenced fleet behavior. Note that this time frame assumes that the spatial distribution of RKC in Southeast Alaska has remained consistent over time (since 1974) and with varying population sizes. 

Expanding to the non-surveyed areas using the historical harvest time frame results in a regional biomass estimate of `r round(b_cur_yr$TOTAL_leg/1000000, 2)` million lb for legal crab and `r round(b_cur_yr$TOTAL_mat/1000000, 2)` million lb for mature crab (Table \@ref(tab:harvestrec) and Figure \@ref(fig:regionalbio)).


## HARVEST RATES {-}
The final decision about harvest rates is made by management staff. A study of appropriate harvest rates for RKC in Southeast Alaska provides two approaches that serve as guidelines for recommended harvest rates, one with higher risk of leading to population decline and one with a lower risk (Palof and Stratman 2020). This guideline range recognizes the difficulty of determining appropriate harvest rates for the different survey areas given inconsistent recruitment and varying population health. In `r cur_yr`, we present these results in terms of legal male biomass.

Option 1, using the equilibrium harvest rates, is considered the most risk neutral option with an equal probability of the male biomass decreasing or increasing in the following year after applying this level of harvest pressure when the population is at average or above average stock health. For a sustainable population, these should be considered maximum appropriate harvest rates for each of the surveyed areas. This option uses a regression model and therefore incorporates both the variability in the harvest rates and their associated change in legal male biomass. In theory, these harvest levels will maintain the equilibrium population size when the population is at equilibrium, or more realistically at average stock health levels (> moderate, Tables \@ref(tab:health5year) and \@ref(tab:healthscores)). However, a disadvantage to this method as currently applied is that it does not account for time-varying trends in survival or other factors such as environmental change, temperature, etc., that affect biomass. For our purposes, equilibrium could be defined as the average baseline population size (Figure \@ref(fig:regionalbio)) or a biomass that is sustainable over time. When the population is below equilibrium, harvesting at these rates will either maintain low population levels or, more likely, cause a decrease in population size. 
The resulting legal biomass GHL for option 1 is **`r format((table2.7 %>% filter(Location == 'total'))$Comm.GHL, big.mark = ",")` lb** (Table A1). 

Option 2, using the average harvest rate for years in which the mature male biomass increased, is considered a lower risk option with a high probability of the mature male biomass increasing in the following year after applying this level of harvest pressure. This option only uses the average of the harvest rates that preceded population increases and therefore does not incorporate variability as well as option 1. In theory, these harvest levels will lead to increases in the population size regardless of health of the stocks. However, during depressed stock health conditions, where biomass levels are below baseline values, even small harvest levels may still result in a decrease in population size. 
The resulting GHL for option 2 is **`r format((table3.6 %>% filter(Location == 'total'))$Comm.GHL, big.mark = ",")` lb** (Table A2). 


## 2026 SPECIFIC STOCK ASSESSMENT COMMENTS {-}
The Southeast RKC commercial fishery opened in 2025, necessitating the inclusion of commercial catch in the 2026 CSA model. While Lynn Sisters was closed to commercial fishing in 2025, RKC from the Lynn Sisters population are thought to exit the bay and be caught in statistical area 115-14 (Figure A1). Thus, commercial harvest statistical area 115-14 was included in the Lynn Sisters CSA. The Juneau Area presents an analogous situation. Statistical area 115-13 had a substantial commercial catch in 2026 and RKC from the Juneau Area are thought to move in and out of 115-13. However, 115-13 was not included in the Juneau Area CSA due to the added complexity of the Juneau Area management. 115-13 falls outside the survey area used to set the Juneau Area GHL and is not otherwise factored into that GHL calculation. Including the commercial catch from this area would also skew the 60%/40% personal-use-to-commercial-catch ratio underlying the GHL.

Also of note is the Seymour Canal CSA. The survey likely does not capture a representative sample of RKC in Seymour Canal every year, and the Seymour CSA model historically underestimates the biomass, an issue that is corrected via a mark-recapture adjustment factor (Table \@ref(tab:bioadj) and Figure \@ref(fig:seymour2)). In order to achieve realistic results for the 2026 Seymour Canal CSA, the 2026 commercial catch was divided by the adjustment factor for the model input. As a result, there is more uncertainty in the Seymour Canal 2026 biomass estimates than in other years. The RTMB model that is under development may reduce the mark-recapture adjustment dependency going forward, but an additional mark-recapture survey in Seymour Canal should be prioritized to have more up-to-date mark-recapture numbers and reduce the reliance on historical data.


## STOCK ASSESSMENT CONCERNS AND RECOMMENDATIONS {-}
Over the past decade, most of the survey areas, except for the Juneau Area and Lynn Sisters, have recovered slowly from low biomass levels. Most areas, apart from Peril Strait, had increasing biomass estimates from 2015–2017. Both legal and mature biomass decreased in 2018 in all survey areas that experienced personal use and commercial harvest in the previous season (2017–2018). 
The impact of the commercial fishery opening in the 2017/2018 season is confounded by potential increased personal use harvest in the survey areas, but this is hard to quantify because we do not have personal use harvest estimates before 2018 in any area except Section 11-A. 

In 2026, both regional legal and mature biomass estimates were at a 30-year high (Figure \@ref(fig:regionalbio)). However, the juvenile and postrecruit CPUEs, along with carapace length density graphs (Figures \@ref(fig:ridgesJNU) - \@ref(fig:ridgesLS)) indicate that a large cohort of recruit and postrecruit RKC are aging through the fishery without sufficient recruitment to replace their numbers. Commercial fishermen have expressed that they appreciate consistency in fishing opportunity (CITATION NEEDED); in order to achieve consistency in fishing opportunity, the GHL can be set with the goal of fishing the large recruitment pulse of legal crab over multiple years.

The recent regulation revision [5 AAC 34.113] added commercial fishery opportunities based on the long-term median of the legal biomass estimate. The years 1995–2007 were chosen to represent the long-term median; this time period captures a high and low period of population biomass and these years are already used as the baseline when calculating the long-term mean. The `r cur_yr` legal biomass estimate of `r round(b_cur_yr$TOTAL_leg/1000000, 2)` million lb is above the long-term median (3,001,030 lb).

We recommend no harvest in Pybus Bay and Excursion Inlet due to poor stock status, and no harvest in Peril Strait due to low abundance estimates and historically poor stock status. The Juneau Area harvest rate has already been set at 9%. The harvest rates of Lynn Sisters, Seymour Canal, and Gambier Bay should be discussed, with consideration of Table A1 as the equilibrium guideline (the level of harvest an area can withstand under healthy stock conditions) and Table A2 as the conservative guideline.

The RKC and BKC commercial fishery and personal use fishery outside of Section 11-A are managed separately and there are no regulatory thresholds or allocations that combine estimated harvest for both user groups. Personal use harvest outside of Section 11-A is not considered when calculating the commercial GHLs for each area to determine whether the total commercial GHL meets the 200,000 lb threshold in regulation for a commercial fishery. A personal use permit requirement was implemented in 2018 for the regional (outside Section 11-A) personal use fishery and reported harvests are shown in Appendix A. In the past three harvest years, the only survey area that has seen substantial harvests under the regional personal use permit is Lynn Sisters.

# SURVEY AREA STOCK STATUS AND HARVEST RATE RECOMMENDATION {-}

Most of the areas with consistent RKC survey catch (Juneau, Seymour, Gambier, and possibly Lynn Sisters) experienced a recruitment pulse, as reflected in the high CPUEs of male recruit and postrecruit RKC. However, the low CPUES of juvenile males, juvenile females, and prerecruit males indicate that once this cohort has been fished, it will not be replaced in similar numbers. This pattern is also suggested by the length composition figures (\@ref(fig:ridgesJNU) - \@ref(fig:ridgesLS)). We recommend setting harvest rates at or below 2025 levels in order to provide the opportunity to fish the current pulse of large male RKC over multiple years.

## STOCK STATUS BY SURVEY AREA {-}

Significance in long-term or short-term trends is defined as a p-value <0.05. Long-term trends compare the current year’s mean to the long-term baseline value (1995–2007); short-term trends regress the last four years of survey data to determine if a significant increasing or decreasing trend is present. Estimates of legal and mature mark-recapture biomass (adjusted legal/adjusted mature) for the entire biomass time series for each area, along with their associated long-term baseline (1995–2007; solid black line for legal and grey dotted line for mature) estimates can be viewed in Figures \@ref(fig:pybus2) – \@ref(fig:excursion3). Graphs for each area reflect biomass estimates from the `r cur_yr` CSA model.

## Pybus Bay (`r pybus_stockhealth`) {-}
Pybus Bay stock health remained at `r pybus_stockhealth` status (Table \@ref(tab:health5year); Figures \@ref(fig:pybus2) and \@ref(fig:pybus3)). All size/sex class CPUEs were significantly below their long-term averages (Table \@ref(tab:longterm)). 
Legal biomass increased 23% from the `r pr_yr` model estimate and mature biomass increased 17%. 
The mature biomass estimate was `r abs(round((baseline_rel %>% filter(Location == 'Pybus'))$pct.adj.cur, 0))`% below the baseline value and the legal biomass estimate was `r abs(round((LEGAL_baseline_rel %>% filter(Location == 'Pybus'))$pct.adj.cur, 0))`% below the baseline value. 

Due to the aforementioned concerns and the low level of the stock biomass in Pybus Bay, no harvest is recommended for the `r cur_yr`/`r fut_yr` season (Table \@ref(tab:harvestrec)).

## Gambier Bay (`r gambier_stockhealth`) {-}
Gambier Bay stock health dropped to `r gambier_stockhealth` status (Table \@ref(tab:health5year); Figures \@ref(fig:gambier2) and \@ref(fig:gambier3)). Prerecruit, postrecruit, and juvenile male CPUEs were significantly below their long-term averages (Table \@ref(tab:longterm)). Juvenile and mature females and recruit male CPUEs were not significantly different from their long-term averages. There were significant short-term increasing trends in recruit male and mature female CPUEs and decreasing trends in juvenile male and female CPUEs (Table \@ref(tab:shortterm)).

Prerecruit and recruit male biomass and CPUEs trended up for this population in recent years, even after the 2025 fishery (Figure \@ref(fig:gambier4)). However, the CPUEs of prerecruits and juveniles declined in 2026.
Indicators of female stock health were good, as seen by the low proportion of poor clutches and high clutch fullness.
Legal biomass increased 50% and mature biomass decreased 1% from the `r pr_yr` model estimate, reflecting the low prerecruit CPUE. The legal adjusted biomass estimate was near the baseline, and the mature adjusted biomass estimate was below the baseline. 
The mature biomass estimate was `r abs(round((baseline_rel %>% filter(Location == 'Gambier'))$pct.adj.cur, 0))`% below and the legal biomass was `r abs(round((LEGAL_baseline_rel %>% filter(Location == 'Gambier'))$pct.adj.cur, 0))`%  below the baseline values. 

The 2025 legal harvest rate in Gambier Bay was 0.08, a realized rate of 0.05.

## Seymour Canal (`r seymour_stockhealth`) {-}
The overall stock health for Seymour Canal remained `r seymour_stockhealth` in 2026 (Table \@ref(tab:health5year); Figures \@ref(fig:seymour2), \@ref(fig:seymour3), and \@ref(fig:seymour4)). Recruit and postrecruit male CPUEs were above their long-term averages, while juvenile male and prerecruit CPUEs were below their long-term averages (Table \@ref(tab:longterm)). 
Recruit and postrecruit male CPUEs had significant short-term increasing trends (Table \@ref(tab:shortterm)). 
Indicators of female stock health were good, with a high mean clutch size and low percentage of poor clutches.

Estimated legal biomass increased 31% and mature biomass increased 6% from the `r pr_yr` model estimates.
The mature biomass estimate was `r abs(round((baseline_rel %>% filter(Location == 'Seymour'))$pct.adj.cur, 0))`% above and the legal biomass estimate was `r abs(round((LEGAL_baseline_rel %>% filter(Location == 'Seymour'))$pct.adj.cur, 0))`% above the baseline value.   

Undersampling during the survey has historically been a concern in Seymour Canal. The Seymour Canal model has extra uncertainty in 2026; see the above 2026 model run discussion. The biomass estimates were near the baseline values, an increase from prior years.

The 2025 legal harvest rate in Seymour Canal was 0.07, a realized rate of 0.12.

## Peril Strait (`r peril_stockhealth`) {-}
The stock status for Peril Strait was `r peril_stockhealth` in 2026 (Table \@ref(tab:health5year); Figures \@ref(fig:peril2) and \@ref(fig:peril3)). Peril Strait is on a biennial survey schedule. 

In 2026, the mature biomass estimate was `r abs(round((baseline_rel %>% filter(Location == 'Peril'))$pct.adj.cur, 0))`% below and the legal biomass estimate was `r abs(round((LEGAL_baseline_rel %>% filter(Location == 'Peril'))$pct.adj.cur, 0))`% below their respective baseline values. Due to recent concerns about the Peril Strait stock status, no harvestable surplus is recommended for the `r cur_yr`/`r fut_yr` season (Table \@ref(tab:harvestrec)). 

## Juneau (`r juneau_stockhealth`) {-}
The stock status for the Juneau Area was `r juneau_stockhealth` in 2026 (Table \@ref(tab:health5year); Figures \@ref(fig:juneau2) and \@ref(fig:juneau3)). 
Recruit and postrecruit males CPUEs were significantly above their long-term averages; all other size and sex classes were not significantly different from the long-term averages (Table \@ref(tab:longterm)). There was a significant short-term increasing trend in postrecruit male CPUE and a significant short-term decreasing trend in juvenile male and juvenile female CPUEs (Table \@ref(tab:shortterm)). 
When compared to the `r pr_yr` model estimate, legal biomass increased 16%, while mature biomass increased 0.1%. 
Indicators of female stock health remained stable as indicated by the low proportion of poor clutches and high clutch fullness. Both legal and mature biomass were above their long-term baseline values, with mature biomass `r round((baseline_rel %>% filter(Location == 'Juneau'))$pct.adj.cur, 0)`% above the baseline and legal biomass `r round((LEGAL_baseline_rel %>% filter(Location == 'Juneau'))$pct.adj.cur, 0)`% above the baseline. 

The high recruit and postrecruit CPUEs and fall in juvenile and prerecruit CPUEs indicate the end of an age cohort. In order to provide fishing opportunity this year while retaining large crab for future years of fishing, the decision was made in July to set the harvest rate at 9% of the legal male biomass for the `r cur_yr`/`r fut_yr` season (Table \@ref(tab:harvestrec)).

The 2025 legal harvest rate in the Juneau Area was 0.10, with a realized rate of 0.09.

## Lynn Sisters (`r lynnsisters_stockhealth`) {-}
Stock health in the Lynn Sisters area remained `r lynnsisters_stockhealth` in `r cur_yr` (Table \@ref(tab:health5year); Figures \@ref(fig:lynn2), \@ref(fig:lynn3), and \@ref(fig:lynn4)). CPUEs for juvenile males and juvenile females were below their long-term averages, while none of the other size/sex classes were significantly different from the long-term averages (Table \@ref(tab:longterm)). 
Juvenile male and prerecruit CPUEs had decreasing short-term trends (Table \@ref(tab:shortterm)). 
Female clutch indicators were stable as indicated by the high percentage clutch fullness and low percentage of poor clutches.
Legal biomass decreased 8%, while mature biomass decreased 20% from the `r pr_yr` model estimates.
Both legal and mature biomass were above their long-term baseline values, with mature biomass `r round((baseline_rel %>% filter(Location == 'LynnSisters'))$pct.adj.cur, 0)`% above the baseline value and legal biomass `r round((LEGAL_baseline_rel %>% filter(Location == 'LynnSisters'))$pct.adj.cur, 0)`% above the baseline value. 

Lynn Sisters was closed to commercial fishing in 2025.


## Excursion Inlet (`r excursion_stockhealth`) {-}
The stock health of Excursion Inlet did not improve from `r excursion_stockhealth` status (Table \@ref(tab:health5year); Figures \@ref(fig:excursion2), \@ref(fig:excursion3), \@ref(fig:excursion4)). CPUEs of all sex/size classes were significantly below their long-term averages (Table \@ref(tab:longterm)). There were no significant short-term trends for all size/sex classes (Table \@ref(tab:shortterm)). Females had a low proportion of poor clutches but marginal clutch fullness. Estimated legal biomass decreased 14% and mature biomass decreased 13% from the `r pr_yr` model estimates. 
The mature biomass estimate was `r abs(round((baseline_rel %>% filter(Location == 'Excursion'))$pct.adj.cur, 0))`% and the legal biomass estimate was `r abs(round((LEGAL_baseline_rel %>% filter(Location == 'Excursion'))$pct.adj.cur, 0))`% below the baseline value. 

Stock health was poor in Excursion Inlet. CPUEs of all mature male size classes were below long-term baselines for the eighth consecutive season. Mature and legal biomass estimates decreased and both were below long-term baselines. There were no short-term increasing trends. Considering these trends, there is not a harvestable surplus of RKC for the `r cur_yr`/`r fut_yr` season in Excursion Inlet (Table \@ref(tab:harvestrec)). 

## Port Frederick (reintroduced to survey in 2025) {-}
Port Frederick was surveyed in 2025 for the first time in 10 years (Figure \@ref(fig:fredtemp)). Given the ten-year gap in survey data, Port Frederick was considered part of the non-surveyed areas for the current year's stock assessment (Table \@ref(tab:harvestrec)). The area may be re-incorporated into the surveyed areas biomass estimate in future years, once more years of recent survey data are available. From 1979 to 2004 (the years used to expand the survey biomass to the non-surveyed areas), Port Frederick contributed 2.4% of the harvest. The previous percent expansion of 65.2% survey areas and 34.8% non-surveyed areas was adjusted. Excluding Port Frederick, 62.8% of the harvest was from survey areas and 37.2% from non-surveyed areas. Adjusting the expansion factor allows for consistency between previous years' estimates and the current year; all comparisons regionally were performed with a time series of estimates that were adjusted to not include Port Frederick.

## Holkham Bay (unknown since 2014){-}
Holkham Bay was removed as a survey area in 2015 due to budget constraints. The decision to drop Holkham Bay from the survey was based on difficulties in interpreting survey results from this location. Holkham Bay had consistently been surveyed since 2002, however, the data were not always adequate to use in the CSA to produce a biomass estimate; the estimates were only useful as an index of biomass and were never included in the regionwide biomass estimate. Holkham Bay continues to be part of the non-surveyed areas (Table \@ref(tab:harvestrec)).   

## Non-Surveyed Areas {-}
Information used to assess non-surveyed areas for the `r cur_yr`/`r fut_yr` commercial fishery recommendation includes the current CSA and historical harvest data, by statistical area, from fish tickets. The percentage of historical harvest that occurred within the surveyed areas from the 1974/1975 to 1984/1985 seasons was used to expand the harvestable surplus from the surveyed area to non-surveyed areas. Since 2015, when Port Frederick was removed from the survey, a historical harvest of 52.8% from surveyed areas is used; the remaining 47.2% of harvest is from the non-surveyed areas. Summing up the mature biomass estimates for the surveyed areas, and using this 52.8%/47.2% ratio, yields an adjusted legal biomass estimate of `r format(round((table2.7 %>% filter(Location == 'other.areas'))$adj.legal, 0), big.mark = ",")` lb for non-surveyed areas.

The harvest rate for the non-surveyed areas in 2025 was set at 0.11, a realized rate of 0.10.

# `r cur_yr`/`r fut_yr` RKC FISHERY MANAGEMENT ACTIONS {-}
TBD

# FISHERY MANAGEMENT CONCERNS {-}
TBD

\newpage
# TABLES AND FIGURES {-}

```{r harvestrec, tab.cap = paste(cur_yr, "Southeast Alaska commercial RKC fishery guideline harvest level (GHL) calculations for the surveyed areas and non-surveyed areas."), results = "asis"}
#AGR FLAG 25- adding BKC to the total GHL - added manually , FIX later!!
#TABLE 7 
# export in order to send a csv version of Table 7 to biologists/managers, since they need it for their announcement
write_csv(tbl7_d, paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/SE_RKC_RIR_table_7_FOR_BIOLOGISTS', cur_yr, '.csv')) #AGR 2026- I'll do this after the RIR


tbl7_e <- tbl7_d %>%
 dplyr::select(-c("Mature HR", "Total GHL (mature lb)", "PU harvest (mature lb)", "2026 Commercial GHL (mature lb)")) #updated the year to 2025, to 2026 in 2026

tbl7_e <- tbl7_e %>% #wrangling so I can add the TBD's
  dplyr::mutate(
    `Total GHL (legal lb)` = scales::comma(`Total GHL (legal lb)`, accuracy = 1),
    `2026 Commercial GHL (legal lb)` = scales::comma(`2026 Commercial GHL (legal lb)`, accuracy = 1)
  )

##AGR add 2026- add in the "TBDs"
tbl7_e[2,4] <- "TBD" #gambier
tbl7_e[3,4] <- "TBD" #seymour
tbl7_e[6,4] <- "TBD" #lynn

tbl7_e[2,5] <- "TBD" #gambier
tbl7_e[3,5] <- "TBD" #seymour
tbl7_e[6,5] <- "TBD" #lynn

tbl7_e[8,5] <- "TBD" #BKC, depends on totals

tbl7_e[10,5] <- "TBD" #total GHL legal

tbl7_e[2,7] <- "TBD" #gambier
tbl7_e[3,7] <- "TBD" #seymour
tbl7_e[6,7] <- "TBD" #lynn
tbl7_e[8,7] <- "TBD" #BKC, depends on totals
tbl7_e[10,7] <- "TBD" #total GHL comm legal

#ft <- align(ft, j = c("Total GHL (legal lb)", "2026 Commercial GHL (legal lb)"), align = "right", part = "all") #algin fix from adding the TBD's

ft <- flextable(tbl7_e) %>% 
   colformat_double(j = c("Legal HR"), #"Mature HR",  also
       digits = 2,
      na_str = "")


#ft <- italic(ft, i = 4, part = "body") %>% #italicize on odd years (when peril not surveyed)
 # fontsize(size = 8)

##AGR aDD 2026 - add in the TBD's so we can leave this an open-ended table for the biologists


set_table_properties(ft, layout = "autofit")

```

\newpage

```{r bioadj, echo=FALSE, tab.cap = "Southeast Alaska red king crab legal crab biomass adjustments to catch–survey analysis (CSA) based on Chapman mark–recapture estimates."}
#THE SAME EVERY YEAR (TABLE 5)

sur.ar <- c("Lynn Sisters", "Pybus Bay", "", "Gambier Bay", "", "Excursion Inlet", "", "Seymour Canal", "", "Peril Strait", "Port Frederick")
mr.yr <- c("2009", "2010", "2014", "2010", "2017", "2010", "2016", "2011", "2015", "2011", "2011")
csa.lb <- c("39,886", "80,807", "17,635", "42,104", "25,294", "20,066", "17,184", "6,387", "29,062", "19,023", "12,523")
mr.lb <- c("69,674", "236,042", "67,220", "180,433", "84,394", "97,232", "12,501", "58,002", "267,233", "52,377", "53,436")
adj <- c("1.75", "2.92", "3.81", "4.29", "3.34", "4.85", "0.73", "9.08", "9.20", "2.75", "4.27")
wt.adj <- c("", "", "3.08", "", "3.93", "", "2.95", "", "9.17", "", "")

#tbl1 <- as.data.frame(cbind(sur.ar, mr.yr, csa.lb, mr.lb, adj, wt.adj))
tbl1 <- data.frame(sur.ar, mr.yr, adj, wt.adj, stringsAsFactors = FALSE)

#names(tbl1) <- c("Survey area", "M–R study year", "CSA lb", "M–R lb", "Adjustment", "Weighted avg. adjustment")
# Fill blank area names down so each row knows its group
tbl1$sur.ar[tbl1$sur.ar == ""] <- NA
tbl1 <- tidyr::fill(tbl1, sur.ar)
tbl1$sur.ar <- factor(tbl1$sur.ar, levels = unique(tbl1$sur.ar))


# Collapse to one row per area
tbl2 <- tbl1 %>%
  group_by(sur.ar) %>%
  summarise(
    `Study years` = paste(mr.yr, collapse = ", "),
    Adjustment = dplyr::last(dplyr::coalesce(na_if(wt.adj, ""), adj)),
    .groups = "drop"
  ) %>%
  rename(`Survey area` = sur.ar)

ft <- flextable(tbl2)
ft <- set_table_properties(ft, layout = "autofit")
ft

#ft <- flextable(tbl1)

# Merge the grouping columns vertically where areas span multiple study years
#ft <- merge_v(ft, j = c("Survey area", "Weighted avg. adjustment"))


#set_table_properties(ft, layout = "autofit")

```

\newpage

```{r samplesizes, tab.cap = paste("Sample sizes for the", cur_yr, "survey by area."), results = "asis"}
#table 6 yearly edit - change Between Fred and Peril depeding on the year

df <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/Table7_raw_samp_', cur_yr,'.csv'))
df2 <- df %>% 
  select(-Year) %>%
  mutate(recruit.class = case_when(
    recruit.class == "Juvenile" ~ "Juvenile males",
    recruit.class == "Small.Females" ~ "Small females",
    recruit.class == "Large.Females" ~ "Large females",
    recruit.class == "Pre_Recruit" ~ "Prerecruits",
    recruit.class == "Recruit" ~ "Recruits",
    recruit.class == "Post_Recruit" ~ "Postrecruits",
    recruit.class == "effective_no_pots" ~ "Effective no. of pots"
  ))

names(df2) <- c(" ", "Peril Strait", "Excursion Inlet", "Gambier Bay", "Juneau", "Lynn Sisters", #add "Peril Strait" before Excursion in Peril survey years
              "Pybus Bay", "Seymour Canal")
#knitr::kable((df), booktabs = T, caption = "Table 2")
ft <- flextable(df2)
#ft <- autofit(ft)
#ft
set_table_properties(ft, layout = "autofit")
```


\newpage

```{r longterm, tab.cap = paste("Comparisons of", cur_yr, "survey CPUE values to long-term averages by size/sex class and survey area. 1 = significantly above long-term average; 0 = not significantly different from long-term average; -1 = significantly below long-term average."), results = "asis"}

#Table A1 (put that in manually)
#turn off peril in non-peril years
cur_yr<-2026

files_lt <- c(paste0(here::here(), "/results/rkc/Pybus/", cur_yr, "/longterm.csv"), 
                    paste0(here::here(), "/results/rkc/Gambier/", cur_yr, "/longterm.csv"), 
                    paste0(here::here(), "/results/rkc/Seymour/", cur_yr, "/longterm.csv"), 
                    paste0(here::here(), "/results/rkc/Juneau/", cur_yr, "/longterm.csv"), 
                    paste0(here::here(), "/results/rkc/LynnSisters/", cur_yr, "/longterm.csv"),
                    paste0(here::here(), "/results/rkc/Excursion/", cur_yr, "/longterm.csv"),
                    paste0(here::here(), "/results/rkc/Peril/", cur_yr, "/longterm.csv")
              )

lt_list <- files_lt %>%
  map(read.csv) 
names(lt_list) <- c("Pybus", "Gambier", "Seymour", "Juneau", "LynnSisters", "Excursion","Peril") #add peril in peril-survey years
#type_change <- c("type", "change")

#lt_list2 <- lapply(lt_list, "[", , type_change)
lt_all <- do.call(rbind, Map(cbind.data.frame, Location = names(lt_list), lt_list))
row.names(lt_all) <- NULL

lt_2 <- lt_all %>%
  select(Location, recruit.status, significant) %>%
  mutate(recruit.status = case_when(
    recruit.status == "Small.Female" ~ "Juvenile female",
    recruit.status == "Large.Female" ~ "Mature female",
    recruit.status == "Pre_Recruit" ~ "Prerecruit",
    recruit.status == "Post_Recruit" ~ "Postrecruit",
    recruit.status == "Juvenile" ~ "Juvenile male",
    recruit.status == "Recruit" ~ "Recruit"
  )) %>%
  mutate(Location = case_when(
    Location == "Pybus" ~ "Pybus Bay",
    Location == "Gambier" ~ "Gambier Bay",
    Location == "Seymour" ~ "Seymour Canal",
    Location == "Peril" ~ "Peril Strait",
    Location == "LynnSisters" ~ "Lynn Sisters",
    Location == "Excursion" ~ "Excursion Inlet",
    .default = as.character(Location)
  )) %>%
  #mutate(significant = case_when(
    #significant == -1 ~ "Below long-term average",
    #significant == 0 ~ "Not different from long-term average",
    #significant == 1 ~ "Above long-term average"
  #)) %>%
  pivot_wider(names_from = recruit.status, values_from = significant)

flextable(lt_2) -> ft

set_table_properties(ft, layout = "autofit")

```

\newpage

```{r health5year, tab.cap = paste("Total stock health designations and associated scores for", cur_yr-4, "to", cur_yr, "by survey area."), results = "asis"}

#AGR- NOTE, THIS ONE NEEDS MANUAL UPDATING, EVERY YEAR! Damn it-2025 - AGR 2026- NEeds update TK
# pull the current year's health scores for the table. Can use previous years' health scores written out as strings below.
pybus_healthscore <- sh_all %>% filter(location == "Pybus") %>% pull(score)
gambier_healthscore <- sh_all %>% filter(location == "Gambier") %>% pull(score)
seymour_healthscore <- sh_all %>% filter(location == "Seymour") %>% pull(score)
peril_healthscore <- sh_all %>% filter(location == "Peril") %>% pull(score) #ARG un-hashtagged. Will need to turn off peril every other year
juneau_healthscore <- sh_all %>% filter(location == "Juneau") %>% pull(score)
lynnsisters_healthscore <- sh_all %>% filter(location == "LynnSisters") %>% pull(score)
excursion_healthscore <- sh_all %>% filter(location == "Excursion") %>% pull(score)


sur.area <- c("Pybus Bay", "Gambier Bay", "Seymour Canal", "Peril Strait", "Juneau Area", "Lynn Sisters", "Excursion Inlet")
#y2019 <- c("Below Average (-3.75)", "Poor (-6.00)", "Poor (-5.00)", "Poor (-6.25)", "Below Average (-3.50)", "Moderate (0.50)", "Below Average (-2.75)")
#y2020 <- c("Below Average (-2.50)", "Poor (-6.25)", "Below Average (-3.50)", "Below Average (-4.25)", "Moderate (-0.50)", "Moderate (1.50)", "Poor (-4.75)")
#y2021 <- c("Below Average (-4.00)", "Below Average (-2.75)", "Poor (-5.00)", "Below Average (-2.25)", "Above Average (3.50)", "Moderate (1.25)", "Poor (-5.00)") #agr 2026 off
y2022 <- c("Below Average (-2.50)", "Moderate (0.75)", "Below Average (-4.00)", "Below Average (-2.75)", "Healthy (5.00)", "Moderate (1.00)", "Poor (-6.00)")
y2023 <- c("Poor (-5.75)", "Moderate (1.25)", "Below Average (-3.00)", "Unsurveyed", "Healthy (7.75)", "Above Average (3.25)", "Poor (-5.75)")
y2024 <- c("Poor (-5.25)", "Below Average (-2.75)", "Moderate (-0.5)", "Poor (-7)", "Healthy (4.5)", "Below Average (-2.5)", "Poor (-5.5)")
y2025 <- c("Poor (-7)", "Moderate (-1.25)", "Moderate (0.5)", "Unsurveyed", "Healthy (5.5)", "Moderate (-1.25)", "Poor (-6.25)")
#agr manually entered
y2026 <- c(paste0(str_to_title(pybus_stockhealth), " (", pybus_healthscore, ")"), 
           c(paste0(str_to_title(gambier_stockhealth), " (", gambier_healthscore, ")")), 
           c(paste0(str_to_title(seymour_stockhealth), " (", seymour_healthscore, ")")), 
           c(paste0(str_to_title(peril_stockhealth), " (", peril_healthscore, ")")), #years with peril survey - CHAGNE EVERY YEAR
           #c(paste0(str_to_title(peril_stockhealth))), #years without peril survey
           c(paste0(str_to_title(juneau_stockhealth), " (", juneau_healthscore, ")")), 
           c(paste0(str_to_title(lynnsisters_stockhealth), " (", lynnsisters_healthscore, ")")),
           c(paste0(str_to_title(excursion_stockhealth), " (", excursion_healthscore, ")")))

tbl4 <- as.data.frame(cbind(sur.area, y2022, y2023, y2024, y2025, y2026))

names(tbl4) <- c("Survey area", "2022", "2023", "2024", "2025" , "2026")

ft <- flextable(tbl4) %>%
  fontsize(size = 7, part = "all")
set_table_properties(ft, layout = "autofit")

```

\newpage

```{r healthscores, tab.cap = "Stock health scores and their associated categories used for the previous (2006–2008) and current (since 2008) seasons. Scores are calculated in 0.25 increments.", results = "asis"}
#THE SAME EVERY YEAR (TABLE 4)

score <- c("-7.00 to -4.50", "-4.25 to -1.75", "-1.50 to 1.50", "1.75 to 4.25", "4.50 to 7.00")
pre.cat <- c("Poor", "Poor", "Moderate", "Healthy", "Healthy")
cur.cat <- c("Poor", "Below Average", "Moderate", "Above Average", "Healthy")

tbl5 <- as.data.frame(cbind(score, pre.cat, cur.cat))

names(tbl5) <- c("Score", "Previous Categories", "Current Categories")

ft <- flextable(tbl5)
set_table_properties(ft, layout = "autofit")

```


\newpage


```{r shortterm, tab.cap = "Short-term trends in survey CPUE by size/sex class and survey area. 1 = significantly positive trend; 0 = no significant trend; -1 = significantly negative trend.", results = "asis"}

files_st <- c(paste0(here::here(), "/results/rkc/Pybus/", cur_yr, "/shortterm.csv"), 
                    paste0(here::here(), "/results/rkc/Gambier/", cur_yr, "/shortterm.csv"), 
                    paste0(here::here(), "/results/rkc/Seymour/", cur_yr, "/shortterm.csv"), 
                    paste0(here::here(), "/results/rkc/Juneau/", cur_yr, "/shortterm.csv"), 
                    paste0(here::here(), "/results/rkc/LynnSisters/", cur_yr, "/shortterm.csv"),
                    paste0(here::here(), "/results/rkc/Excursion/", cur_yr, "/shortterm.csv"),
                    paste0(here::here(), "/results/rkc/Peril/", cur_yr, "/shortterm.csv")) #turn off peril in non-peril years

st_list <- files_st %>%
  map(read.csv) 
names(st_list) <- c("Pybus", "Gambier", "Seymour", "Juneau", "LynnSisters", "Excursion", "Peril") #turn of peril in non-peril years

st_all <- do.call(rbind, Map(cbind.data.frame, Location = names(st_list), st_list))
row.names(st_all) <- NULL

st_2 <- st_all %>%
  filter(recruit.status != "Missing") %>%
  select(Location, recruit.status, significant) %>%
  mutate(recruit.status = case_when(
    recruit.status == "Small.Females" ~ "Juvenile female",
    recruit.status == "Large.Females" ~ "Mature female",
    recruit.status == "Pre_Recruit" ~ "Prerecruit",
    recruit.status == "Post_Recruit" ~ "Postrecruit",
    recruit.status == "Juvenile" ~ "Juvenile male",
    recruit.status == "Recruit" ~ "Recruit"
  )) %>%
  mutate(Location = case_when(
    Location == "Pybus" ~ "Pybus Bay",
    Location == "Gambier" ~ "Gambier Bay",
    Location == "Seymour" ~ "Seymour Canal",
    Location == "Peril" ~ "Peril Strait",
    Location == "LynnSisters" ~ "Lynn Sisters",
    Location == "Excursion" ~ "Excursion Inlet",
    .default = as.character(Location)
  )) %>%
  #mutate(significant = case_when(
    #significant == -1 ~ "Below long-term average",
    #significant == 0 ~ "Not different from long-term average",
    #significant == 1 ~ "Above long-term average"
  #)) %>%
  pivot_wider(names_from = recruit.status, values_from = significant) %>%
  select(Location, `Juvenile male`, `Juvenile female`, `Mature female`, Prerecruit, Recruit, Postrecruit)

flextable(st_2) -> ft

set_table_properties(ft, layout = "autofit")

```


\newpage
```{r distribution, fig.cap = "Map of Southeast Alaska (Registration Area A) commercial fishery boundaries."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/Picture1.jpg'), dpi = 125)
```

```{r regionalbio, fig.cap = "Southeast Alaska red king crab total biomass estimates (expanded regional estimates) of mature male (gray points and grey dashed line) and legal male (black points and black solid line) from the 2026 CSA model. The gray dashed and black solid horizontal reference lines represent the long-term baselines for mature and legal biomasses, respectively."}
#refernce lines SHOULD be 1995-2007- check this please AGR
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Expanded_MRregional_biomass2_', cur_yr,'_edited.png'), dpi = 125)
#AGR 25- will need a long term median - add that to figures2tables2. TODO
#also change to odd-year tick marks on x axis please
```

```{r med1, fig.cap = "Total biomass estimates (expanded regional estimates) of legal (black points and line) red king crab in Southeast Alaska. Estimates based on Catch-Survey Analysis (CSA) methodologies adjusted using mark-recapture study results then further expanded to include non-survey areas. Squares represent years without commercial harvest. The long-term median and 50% of that median in the baseline years 1995-2007 is depicted as the horizontal orange dot-dash line and dotted line, respectively."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Expanded_biomass_with_1995_2007_median_simple', cur_yr,'_edited.png'), dpi = 125)

```



```{r distcur, fig.cap = "Southeast Alaska (Registration Area A) survey areas for red king crab."}

knitr::include_graphics(paste0(here::here(),'/figures/rkc/regional RKC survey areas.tif'), dpi=125) #was dpi = 125
```

```{r pybus2, fig.cap = "Pybus Bay CPUEs for male size/sex classes of red king crab (top panel) and biomass estimates from the current year’s CSA model with the annual harvest data (bottom panel). The horizontal reference lines represent long-term baselines for each male maturity class. The dashed gray and solid back horizontal reference lines in the bottom panel represent the long-term baseline for mature and legal biomasses, respectively."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Pybus_', cur_yr,'_2.png'), dpi = 125)
```

```{r pybus3, fig.cap = "Pybus Bay CPUEs for mature and juvenile female and juvenile male size/sex classes of red king crab (top panel), and clutch fullness and proportion of poor clutches (bottom panel). The horizontal reference lines in the top panel represent long-term baselines for each size/sex class."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Pybus_', cur_yr,'_3.png'), dpi = 125)
```

```{r pybus4, fig.cap = "The Pybus Bay current year's CSA model fitted CPUE (blue line) compared to the survey CPUE (black points) for pre-recruit, recruit, and post-recruit males."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Pybus_cpue_model_fit.png'), dpi = 125)
#AGR added
```

```{r gambier2, fig.cap = "Gambier Bay CPUEs for male size/sex classes of red king crab (top panel) and biomass estimates from the current year’s CSA model with the annual harvest data (bottom panel). The horizontal reference lines represent long-term baselines for each male maturity class. The dashed gray and solid back horizontal reference lines in the bottom panel represent the long-term baseline for mature and legal biomasses, respectively."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Gambier_', cur_yr,'_2.png'), dpi = 125)
```

```{r gambier3, fig.cap = "Gambier Bay CPUEs for mature and juvenile female and juvenile male size/sex classes of red king crab (top panel), and clutch fullness and proportion of poor clutches (bottom panel). The horizontal reference lines in the top panel represent long-term baselines for each size/sex class."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Gambier_', cur_yr,'_3.png'), dpi = 125)
```

```{r gambier4, fig.cap = "The Gambier Bay current year's CSA model fitted CPUE (blue line) compared to the survey CPUE (black points) for pre-recruit, recruit, and post-recruit males."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Gambier_cpue_model_fit.png'), dpi = 125)
#AGR added
```

```{r seymour2, fig.cap = "Seymour Canal CPUEs for male size/sex classes of red king crab (top panel) and biomass estimates from the current year’s CSA model with the annual harvest data (bottom panel). The horizontal reference lines represent long-term baselines for each male maturity class. The dashed gray and solid back horizontal reference lines in the bottom panel represent the long-term baseline for mature and legal biomasses, respectively."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Seymour_', cur_yr,'_2.png'), dpi = 125)
```

```{r seymour3, fig.cap = "Seymour Canal CPUEs for mature and juvenile female and juvenile male size/sex classes of red king crab (top panel), and clutch fullness and proportion of poor clutches (bottom panel). The horizontal reference lines in the top panel represent long-term baselines for each size/sex class."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Seymour_', cur_yr,'_3.png'), dpi = 125)
```

```{r seymour4, fig.cap = "The Seymour Canal current year's CSA model fitted CPUE (blue line) compared to the survey CPUE (black points) for pre-recruit, recruit, and post-recruit males."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Seymour_cpue_model_fit.png'), dpi = 125)
#AGR added
```

```{r peril2, fig.cap = "Peril Strait CPUEs for male size/sex classes of red king crab (top panel) and biomass estimates from the current year’s CSA model with the annual harvest data (bottom panel). The horizontal reference lines represent long-term baselines for each male maturity class. The dashed gray and solid back horizontal reference lines in the bottom panel represent the long-term baseline for mature and legal biomasses, respectively."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Peril_', cur_yr,'_2.png'), dpi = 125)
#I'll need to add a graph here - run Peril for 2025 to get the grapg - it will be mising 2025 data but that's fine.
```

```{r peril3, fig.cap = "Peril Strait CPUEs for mature and juvenile female and juvenile male size/sex classes of red king crab (top panel), and clutch fullness and proportion of poor clutches (bottom panel). The horizontal reference lines in the top panel represent long-term baselines for each size/sex class."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Peril_', cur_yr,'_3.png'), dpi = 125)
```

```{r peril4, fig.cap = "The Peril Strait current year's CSA model fitted CPUE (blue line) compared to the survey CPUE (black points) for pre-recruit, recruit, and post-recruit males."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Peril_cpue_model_fit.png'), dpi = 125)
#AGR added; turned off in 2025
```

```{r juneau2, fig.cap = "Juneau Area CPUEs for male size/sex classes of red king crab (top panel) and biomass estimates from the current year’s CSA model with the annual harvest data (bottom panel). The horizontal reference lines represent long-term baselines for each male maturity class. The dashed gray and solid back horizontal reference lines in the bottom panel represent the long-term baseline for mature and legal biomasses, respectively."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Juneau_', cur_yr,'_2.png'), dpi = 125)
```

```{r juneau3, fig.cap = "Juneau Area CPUEs for mature and juvenile female and juvenile male size/sex classes of red king crab (top panel), and clutch fullness and proportion of poor clutches (bottom panel). The horizontal reference lines in the top panel represent long-term baselines for each size/sex class."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Juneau_', cur_yr,'_3.png'), dpi = 125)
```

```{r juneau4, fig.cap = "The Juneau Area current year's CSA model fitted CPUE (blue line) compared to the survey CPUE (black points) for pre-recruit, recruit, and post-recruit males."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Juneau_cpue_model_fit.png'), dpi = 125)
#AGR added
```

```{r lynn2, fig.cap = "Lynn Sisters CPUEs for male size/sex classes of red king crab (top panel) and biomass estimates from the current year’s CSA model with the annual harvest data (bottom panel). The horizontal reference lines represent long-term baselines for each male maturity class. The dashed gray and solid back horizontal reference lines in the bottom panel represent the long-term baseline for mature and legal biomasses, respectively."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/LynnSisters_', cur_yr,'_2.png'), dpi = 125)
```

```{r lynn3, fig.cap = "Lynn Sisters CPUEs for mature and juvenile female and juvenile male size/sex classes of red king crab (top panel), and clutch fullness and proportion of poor clutches (bottom panel). The horizontal reference lines in the top panel represent long-term baselines for each size/sex class."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/LynnSisters_', cur_yr,'_3.png'), dpi = 125)
```

```{r lynn4, fig.cap = "The Lynn Sisters current year's CSA model fitted CPUE (blue line) compared to the survey CPUE (black points) for pre-recruit, recruit, and post-recruit males."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/LynnSisters_cpue_model_fit.png'), dpi = 125)
#AGR added
```

```{r excursion2, fig.cap = "Excursion Inlet CPUEs for male size/sex classes of red king crab (top panel) and biomass estimates from the current year’s CSA model with the annual harvest data (bottom panel). The horizontal reference lines represent long-term baselines for each male maturity class. The dashed gray and solid back horizontal reference lines in the bottom panel represent the long-term baseline for mature and legal biomasses, respectively."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Excursion_', cur_yr,'_2.png'), dpi = 125)
```

```{r excursion3, fig.cap = "Excursion Inlet CPUEs for mature and juvenile female and juvenile male size/sex classes of red king crab (top panel), and clutch fullness and proportion of poor clutches (bottom panel). The horizontal reference lines in the top panel represent long-term baselines for each size/sex class."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Excursion_', cur_yr,'_3.png'), dpi = 125)
```

```{r excursion4, fig.cap = "The Excursion Inlet current year's CSA model fitted CPUE (blue line) compared to the survey CPUE (black points) for pre-recruit, recruit, and post-recruit males."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/', cur_yr, '/Excursion_cpue_model_fit.png'), dpi = 125)
#AGR added
```
\newpage


```{r fredtemp, fig.cap = "Port Frederick CPUEs for male size/sex classes of red king crab. Reference lines represent long-term baselines for each parameter. Port Frederick was added back into the survey in 2025 with an alternating year schedule."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/2025/Frederick_2025Fred_male_placeholder.png'), dpi = 125)
```
\newpage

# (APPENDIX) Appendix A {-}

## Figures {-}
```{r statextra, fig.cap = "Stat areas near the Juneau Area and Lynn Sisters. In 2026, commercial catch from stat areas 115-14 (Outer St. James) and 115-13 (Postage Stamp) were discussed in their relevancy to the adjacent survey areas (Lynn Sisters and the Juneau Area, respectively)."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/stat_areas_contentious.png'), dpi = 125)

```
\newpage

```{r ridgesJNU, fig.cap = "Length density composition for the Juneau Area by year. This figure is not scaled to biomass between years."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/2026/ridges_Juneau.png'), dpi = 125)

```

\newpage

```{r ridgesBC,  fig.cap = "Length density composition for Barlow Cove by year. This figure is not scaled to biomass between years."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/2026/ridges_Barlow_Cove.png'), dpi = 125)

```

\newpage

```{r ridgesJNUBC,  fig.cap = "Length density composition for Barlow Cove by year. This figure is not scaled to biomass between years."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/2026/ridges_Juneau_Area_including_Barlow_Cove.png'), dpi = 125)

```

\newpage

```{r ridgesGB,  fig.cap = "Length density composition for Gambier Bay by year. This figure is not scaled to biomass between years."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/2026/ridges_Gambier_Bay.png'), dpi = 125)

```

\newpage

```{r ridgesSC,  fig.cap = "Length density composition for Seymour Canal by year. This figure is not scaled to biomass between years."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/2026/ridges_Seymour_Canal.png'), dpi = 125)

```

\newpage

```{r ridgesLS,  fig.cap = "Length density composition for Lynn Sisters by year. This figure is not scaled to biomass between years."}
knitr::include_graphics(paste0(here::here(),'/figures/rkc/2026/ridges_Lynn_Sisters.png'), dpi = 125)

```

\newpage


## Tables {-}

```{r maxHR, tab.cap = paste("Option 1: maximum appropriate / risk neutral – model-based equilibrium harvest rates. This is a summary of", cur_yr,  "commercial red king crab fishery guideline harvest level (GHL) calculations (lb) for the seven surveyed areas and other areas. GHL values are calculated using legal male biomass. The risk neutral option is based on 2018 calculated equilibrium exploitation rates (K.Palof, WIP RKC harvest rate determination memo Sept. 2018). The harvest rate for the non-surveyed areas is a weighted average of the surveyed areas' harvest rates (shown below) and the average mature male biomass for each area over the entire time series (1979–2018). Biomass estimates apply the mark-recapture adjustment to the CSA biomass output. Biomass of other areas was expanded using historical years (1974–1984), where 47.2% of the population is estimated to be in the non-surveyed areas. Personal use harvest for other areas is mean catch estimated from 2008–2012 statewide survey data. Blue king crab (BKC) is estimated as 1.06% of the surveyed areas based on historical catch, and its GHL contribution is an expansion of the surveyed areas GHL using the same percentage."), echo=FALSE}

df <- table2.7
df <- df %>% 
  mutate(adj.legal = round(adj.legal, 0), adj.mature = round(adj.mature, 0)) %>% 
  select(-Year, -Legal.HR) %>% 
  filter(Location != "surveyed") %>% 
  mutate(Location = case_when(
    Location == "Pybus" ~ "Pybus Bay",
    Location == "Gambier" ~ "Gambier Bay", 
    Location == "Seymour" ~ "Seymour Canal",
    Location == "Peril" ~ "Peril Strait", 
    Location == "LynnSisters" ~ "Lynn Sisters", 
    Location == "Excursion" ~ "Excursion Inlet",
    Location == "bkc" ~ "BKC",
    Location == "other.areas" ~ "Other areas",
    Location == "surveyed" ~ "Surveyed",
    Location == "total" ~ "Total",
    .default = as.character(Location)
  ))
           
names(df) <- c("Survey area", "Legal biomass (adj)", "Mature biomass (adj)", "Equilibrium HR", 
               "Total GHL", "PU harvest", paste0(cur_yr, " Commercial GHL(lb)"))

#AGR add 2026 - adds BKC numbers where they need to be
df[8,5] <- df[8,7]

#AGR add 9/6/24
##we want Juneau to be the real selected value for HR, not the equilibrium.

#knitr::kable((df), booktabs = T, caption = "Table 2")
## FIX need to edit this to reflect decision on Juneau area
ft <- flextable(df)
#ft <- italic(ft, i = 4, part = "body")
#ft <- autofit(ft)
#ft
set_table_properties(ft, layout = "autofit")
```


\newpage

```{r riskadHR, tab.cap = paste("Option 2: risk-averse – high probability of mature male biomass increasing. This is a summary of", cur_yr, "commercial red king crab fishery guideline harvest level (GHL) calculations (lb) for the seven surveyed areas and other areas. GHL values are calculated using legal male biomass. The risk-averse option is based on 2018 calculated average harvest rates when the mature male biomass was increasing (Inc; K.Palof, WIP RKC harvest rate determination memo Sept. 2018). The harvest rate for the non-surveyed areas is a weighted average of the surveyed areas' harvest rates (shown below) and the average mature male biomass for each area over the entire time series (1979–2018). Biomass estimates apply the adjustment in Table 1 to the CSA biomass output. Biomass of “other areas” was expanded using historical years (1974–1984), where 47.2% of the population is estimated to be in the non-surveyed areas. Personal use (PU) harvest for other areas is mean catch estimated from 2008–2012 statewide survey data. Blue king crab (BKC) is estimated as 1.06% of the surveyed areas based on historical catch, and its GHL contribution is an expansion of the surveyed areas GHL using the same percentage."), echo = FALSE, results = "asis"}
#FLAG 25 - I found an error that I fixed manually. 441 needs to be in total GHL for BKC, just as it is in the commercial fishery GHL for BKC. I fixed this manually in 2025 (sorry to 2026 Alex...)
df <- table3.6
df2 <- df %>% 
  mutate(adj.legal = round(adj.legal, 0), adj.mature = round(adj.mature, 0)) %>% 
  select(-Year, -Legal.HR) %>% 
  filter(Location != "surveyed") %>% 
  mutate(Location = case_when(
    Location == "Pybus" ~ "Pybus Bay",
    Location == "Gambier" ~ "Gambier Bay", 
    Location == "Seymour" ~ "Seymour Canal",
    Location == "Peril" ~ "Peril Strait", 
    Location == "LynnSisters" ~ "Lynn Sisters", 
    Location == "Excursion" ~ "Excursion Inlet",
    Location == "bkc" ~ "BKC",
    Location == "other.areas" ~ "Other areas",
    Location == "surveyed" ~ "Surveyed",
    Location == "total" ~ "Total",
    .default = as.character(Location)))
names(df2) <- c("Survey area", "Legal biomass (adj)", "Mature biomass (adj)", "Avg Inc HR", 
               "Total GHL", "PU harvest", paste0(cur_yr, " Commercial GHL(lb)"))

#AGR add 2026 - adds BKC numbers where they need to be
df2[8,5] <- df2[8,7]


#knitr::kable((df), booktabs = T, caption = "Table 2")
ft <- flextable(df2)
#ft <- italic(ft, i = 4, part = "body")
#ft <- autofit(ft)
#ft
set_table_properties(ft, layout = "autofit")
```






\newpage

```{r regbiomass, tab.cap = paste("Regional biomass estimates of surveyed areas using", cur_yr, "mark-recapture CSA adjusted biomasses in areas where they are available."), echo = FALSE}


df <- read.csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/regional_biomass_', cur_yr,'.csv'))
df %>% 
  select(Year, adj_legal, adj_mature) -> df

# this section of code only works if the two sections have equal numbers of rows - use in even years
#df %>% filter(Year <= 2000) -> df1  
#df %>% filter(Year > 2000) %>% 
  #mutate(Year.cont = Year, 
         #adj.Legal2 = adj_legal, adj.Mature2 = adj_mature) %>% 
  #select(Year.cont, adj.Legal2, adj.Mature2) -> df2
##df2[nrow(df2)+ 1, ] <- NA
#df1 %>% 
  #bind_cols(df2) %>% 
  #mutate(Year = as.character(Year), 
         #Year.cont = as.character(Year.cont)) -> df3
#names(df3) <- c("Year", "Legal", "Mature", "Year(cont)", "Legal(cont)", "Mature(cont)")
##knitr::kable((df), booktabs = T, caption = "Table 2")
#flextable(df3) %>% 
    #colformat_double(
       #digits = 0,
       #na_str = "na") -> ft
##ft <- autofit(ft)
##ft
#set_table_properties(ft, layout = "autofit")

names(df) <- c("Year", "Legal", "Mature")
df1 <- df %>% 
  mutate(Year = as.character(Year))
ft <- flextable(df1) %>% 
    colformat_double(
       digits = 0,
       na_str = "na")
  
set_table_properties(ft, layout = "autofit")

```

\newpage

```{r areabiomass, tab.cap = paste("Biomass estimates (lb) for each survey area using", cur_yr, "mark-recapture CSA adjusted biomasses in areas where they are available."), results = "asis"}
df <- read_csv(paste0(here::here(),'/results/rkc/Region1/', cur_yr, '/biomass_', cur_yr,'.csv')) %>%
  select(Year, Location, adj.legal, adj.mature) %>%
  mutate(Location = case_when(
    Location == "LynnSisters" ~ "Lynn Sisters",
    .default = as.character(Location)
  ))
  

df_b <- df %>%
  pivot_longer(cols = c(adj.legal, adj.mature), names_to = "Status", values_to = "biomass")

df_c <- df_b %>%
  pivot_wider(names_from = Location, values_from = biomass) %>%
  mutate(Status = case_when(
    Status == "adj.legal" ~ "Legal",
    Status == "adj.mature" ~ "Mature"
  )) %>%
  mutate(Year = as.character(Year))

tabA2_1 <- df_c %>% filter(Year < 1994)
tabA2_2 <- df_c %>% filter(Year >= 1994 & Year < 2009)
tabA2_3 <- df_c %>% filter(Year >= 2009)

#df %>% 
  #select(Year, Location, adj.legal, adj.mature) %>% 
  #mutate(adj.legal = round(adj.legal, 0), adj.mature = round(adj.mature, 0)) -> df
#df %>% filter(Location == "Pybus") %>%  
  #mutate(pybus.legal = adj.legal, pybus.mature = adj.mature ) %>% 
  #select(-Location, -adj.legal, -adj.mature) -> df1
#names(df1) <- c("Year", "Pybus", "Legal", "Mature")
#df %>% filter(Location == "Gambier") %>% 
  #mutate(gambier.legal = adj.legal, gambier.mature = adj.mature ) %>% 
  #select(-Location, -adj.legal, -adj.mature)-> df2
#names(df2) <- c("Year", "Gambier", "Legal", "Mature")
#df %>% filter(Location == "Seymour") %>% 
  #mutate(seymour.legal = adj.legal, seymour.mature = adj.mature ) %>% 
  #select(-Location, -adj.legal, -adj.mature)-> df3
#names(df3) <- c("Year", "Seymour", "Legal", "Mature")
#df %>% filter(Location == "Peril") %>% 
  #mutate(peril.legal = adj.legal, peril.mature = adj.mature ) %>% 
  #select(-Location, -adj.legal, -adj.mature)-> df4 
#names(df4) <- c("Year", "Peril", "Legal", "Mature")
#df %>% filter(Location == "Juneau") %>% 
  #mutate(juneau.legal = adj.legal, juneau.mature = adj.mature ) %>% 
  #select(-Location, -adj.legal, -adj.mature) -> df5
#names(df5) <- c("Year", "Juneau", "Legal", "Mature")
#df %>% filter(Location == "LynnSisters") %>% 
  #mutate(lynn.legal = adj.legal, lynn.mature = adj.mature ) %>% 
  #select(-Location, -adj.legal, -adj.mature) -> df6
#names(df6) <- c("Year", "LynnSisters", "Legal", "Mature")
#df %>% filter(Location == "Excursion") %>% 
  #mutate(excursion.legal = adj.legal, excursion.mature = adj.mature ) %>% 
  #select(-Location, -adj.legal, -adj.mature) -> df7
#names(df7) <- c("Year", "Excursion", "Legal", "Mature")

#df1 %>% 
  #left_join(df2) %>% 
  #left_join(df3) %>% 
  #left_join(df4) %>% 
  #mutate(Year = as.character(Year)) -> df_all1
#df5 %>% 
  #left_join(df6) %>% 
  #left_join(df7) %>% 
  #mutate(Year = as.character(Year)) -> df_all2 

#knitr::kable((df), booktabs = T, caption = "Table 2")
#flextable(df_all1) %>% 
    #colformat_double(
       #digits = 0,
       #na_str = "na") %>% 
  #fontsize(size = 7) %>% 
  #fontsize(size = 7, part = "header") -> ft
#ft <- autofit(ft)
#ft

ft <- flextable(tabA2_1) %>% 
  colformat_double(
       digits = 0,
       na_str = "na") %>%
  merge_v(j = "Year", target = "Year") %>%
  valign(j = 1, valign = "top", part = "all") %>%
  fontsize(size = 8)

set_table_properties(ft, layout = "autofit")


```

\newpage

```{r areabiomass2, tab.cap = paste("Biomass estimates (lb) for each survey area using", cur_yr, "mark-recapture CSA adjusted biomasses in areas where they are available, continued."), results = "asis"}
#flextable(df_all2) %>% 
    #colformat_double(
       #digits = 0,
       #na_str = "na") %>% 
  #fontsize(size = 7) %>% 
  #fontsize(size = 7, part = "header")-> ft2

#set_table_properties(ft2, layout = "autofit")

ft <- flextable(tabA2_2) %>% 
  colformat_double(
       digits = 0,
       na_str = "na") %>%
  merge_v(j = "Year", target = "Year") %>%
  valign(j = 1, valign = "top", part = "all") %>%
  fontsize(size = 8)

set_table_properties(ft, layout = "autofit")

``` 

\newpage

```{r areabiomass3, tab.cap = paste("Biomass estimates (lb) for each survey area using", cur_yr, "mark-recapture CSA adjusted biomasses in areas where they are available, continued."), results = "asis"}
#flextable(df_all2) %>% 
    #colformat_double(
       #digits = 0,
       #na_str = "na") %>% 
  #fontsize(size = 7) %>% 
  #fontsize(size = 7, part = "header")-> ft2

#set_table_properties(ft2, layout = "autofit")

ft <- flextable(tabA2_3) %>% 
  colformat_double(
       digits = 0,
       na_str = "na") %>%
  merge_v(j = "Year", target = "Year") %>%
  valign(j = 1, valign = "top", part = "all") %>%
  fontsize(size = 8)

set_table_properties(ft, layout = "autofit")

``` 

\newpage

```{r curyrregbio, tab.cap = paste(cur_yr, "regional CSA and mark-recapture adjusted biomass values."), results = "asis"}
df_tabA3_a <- tableA3
df_tabA3_b <- df_tabA3_a %>% 
  select(-Year) %>%
  mutate(Location = case_when(
    Location == "Pybus" ~ "Pybus Bay",
    Location == "Gambier" ~ "Gambier Bay",
    Location == "Seymour" ~ "Seymour Canal",
    Location == "Peril" ~ "Peril Strait",
    Location == "LynnSisters" ~ "Lynn Sisters",
    Location == "Excursion" ~ "Excursion Inlet",
    Location == "bkc" ~ "BKC",
    Location == "other.areas" ~ "Other areas",
    Location == "surveyed" ~ "Surveyed",
    Location == "total" ~ "Total",
    .default = as.character(Location)
  ))

names(df_tabA3_b) <- c("Survey area", "Legal biomass (CSA)", "Mature biomass (CSA)", 
               "MR adjustment", "Legal biomass (adj)", "Mature biomass (adj)")

flextable(df_tabA3_b) -> ft #%>% 
    #colformat_double(
    #   digits = 0,
    #   na_str = "na")
    
#ft <- autofit(ft)
#ft
set_table_properties(ft, layout = "autofit")
```


\newpage

```{r regpu, tab.cap = "Regional personal use permit reported harvests by survey area, 2018 to present, in numbers of crab. Note that a separate permit is required for 11-A (Juneau), and thus most Juneau harvests are recorded under the 11-A permit and not represented here.", echo = FALSE}

survey.area.order <- c("Pybus Bay", "Gambier Bay", "Seymour Canal", "Peril Strait", "Juneau", "Lynn Sisters", "Excursion Inlet", "Other")

regpu1 <- regpu %>%
  pivot_wider(names_from = survey.area, values_from = total_crab)

regpu_tab <- regpu %>%
  filter(crab_year < cur_yr) %>%
  mutate(`Harvest year` = as.character(crab_year), `Survey area` =  factor(survey.area, levels = survey.area.order)) %>%
  select(`Harvest year`, `Survey area`, total_crab) %>%
  pivot_wider(names_from = `Survey area`, values_from = total_crab) %>%
  mutate(
    across(everything(), ~replace_na(.x, 0))
  ) %>%
  select(`Harvest year`, `Pybus Bay`, `Gambier Bay`, `Seymour Canal`, `Peril Strait`, `Juneau`, `Lynn Sisters`, `Excursion Inlet`, `Other`)

ft <- flextable(regpu_tab) %>%
  add_header_row(top = TRUE, values = c("", "Number of crab harvested"), colwidths = c(1, 8)) %>%
  align(i = 1, j = NULL, align = "left", part = "header") %>%
  vline(j = 1)
set_table_properties(ft, layout = "autofit")
```

\newpage

# References {-}

Palof K. 2018. WIP RKC harvest rate determination memorandum Sept. 2018.

Palof, K., and J. Stratman. 2020. 2019 Southeast Alaska red king crab stock assessment and management plan for the 2019/2020 season. Alaska Department of Fish and Game, Regional Information Report No. 1J20-09, Douglas.

Palof, K., J. Stratman, and A. Olson. 2025. Southeast Alaska red king crab stock assessment and management plan for the 2022–2023 season. Alaska Department of Fish and Game, Division of Commercial Fisheries, Regional Information Report No. 1J25-28, Douglas.

Robson D. S., and H. A. Regier. 1964. Sample Size in Petersen Mark-Recapture Experiments. Transactions of the American Fisheries Society 93 (3): 215-226.

Siddon, C., J. Bednarski, G. Bishop. 2009. Southeast Alaska Tanner crab 2006 stock assessment and recommendations for the 2007 commercial fishery. Alaska Department of Fish and Game, Fishery Data Series No. 09-18, Douglas.

Stratman, J., A. Messmer, K. Wood, T. Bergmann, and K. Palof. 2019. Operational plan: Southeast Alaska red king crab pot survey, 2018-2022. Alaska Department of Fish and Game, Regional Operational Plan ROP.CF.1J.2019.02, Douglas.
