---
title: "Juneau Area (11-A) red king crab assessment CONFIDENTIAL memo "
author: "Alex Reich (alex.reich@alaska.gov)"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  bookdown::pdf_document2:
    fig_caption: true
    includes: null
    toc: no
header-includes:
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
   - \usepackage{pdflscape}
   - \newcommand{\blandscape}{\begin{landscape}}
   - \newcommand{\elandscape}{\end{landscape}}

---

\pagenumbering{arabic}

```{r global_options, include=FALSE, echo = FALSE, message = FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(tidyverse)
library(purrr)
library(readxl)
library(pander)
source(paste0(here::here(), '/code/functions.R'))
cur_yr <- 2026
pr_yr <- cur_yr-1
fut_yr <- cur_yr+1
opts_chunk$set(fig.width = 12, fig.height = 7, echo = FALSE, warning = FALSE, message = FALSE,  dpi=300)
options(scipen = 100)

yr5 <- 2026 #current year
yr4 <- yr5 - 1
yr3 <- yr5 - 2
yr2 <- yr5 - 3
yr1 <- yr5 - 4

set_flextable_defaults(
  font.family = "Arial", 
  font.size = 9,
  font.color = "black",
  table.layout = "autofit",
  text.align = "center"
  #digits = 1,
  #theme_fun = "theme_box"
  )
#\pagenumbering{gobble}
```

```{r exesum, echo = FALSE}
# run code/CSA_model/JNU_RKC_masterfile_crabCSA....... for figures of cpue fit
biomass <- read.csv(paste0(here::here(), '/data/rkc/biomass.csv'))
biomass %>% 
  filter(Location == "Juneau") -> jnu_biomass
hindcast <- read.csv(paste0(here::here(), '/data/rkc/Juneau/hind_fore_cast_JNU_current_2026.csv')) #updated/created in the juneau hindcast figure code

cpue <- read.csv(paste0(here::here(), '/results/rkc/Juneau/', cur_yr, '/JNU_CPUE_', cur_yr,'.csv'))

# change from previous year's forecasted values 
hindcast %>% 
  filter(year >= pr_yr) %>% 
  mutate(leg_change = round((legal_forecast - lag(legal_forecast))/ lag(legal_forecast)*100, 1), 
         mat_change = round((mature_forecast - lag(mature_forecast))/ lag(mature_forecast)*100, 1), 
         leg_cur_change = round((legal_curyr - lag(legal_curyr))/ lag(legal_curyr)*100, 1), 
         mat_cur_change = round((mature_curyr - lag(mature_curyr))/ lag(mature_curyr)*100, 1)) -> change_forecast

# cpue and change in cpue from last year
#cpue %>% 
#  gather(Rclass, cpue, Pre_Recruit_wt:SmallF_SE)
cpue_short <- as.data.frame(t(cpue))
cpue_short[2:13, ] -> cpue_short
colnames(cpue_short) <- c("2025", "2026") #updated years - AGR 2026
cpue_short %>% 
  mutate(change = ((`2026` - `2025`)/`2025`)*100) -> cpue_short

cpue %>% 
  filter(Year == cur_yr) -> cpue2
```


# `r cur_yr` SUMMARY POINTS {-}
- A legal harvest rate of 10% was implemented for the `r pr_yr`/`r cur_yr` personal use and commercial fisheries; estimated actual harvest rate was 9.0%. In the prior three seasons, harvest rates of 10%, 8%, and 10% were implemented and the commercial fishery was closed, resulting in an estimated actual harvest rate of 4.9% in 2024/2025, 5.3% in 2023/2024, 4.0% in 2022/2023.

- Estimated legal biomass increased (up `r change_forecast$leg_change[2]`%) and mature biomass decreased (down `r abs(change_forecast$mat_change[2])`%) compared to `r pr_yr` predicted values. The divergent trends in legal and mature biomasses are largely due to the increase in postrecruits and decrease in prerecurits observed on the Juneau Area pot survey. Legal and mature biomass both remain above the long-term average.

- Compared to `r pr_yr`, the mature male RKC CPUE trends were mixed. Prerecruits decreased by `r abs(round(cpue_short$change[1], 1))`%, recruits decreased by `r abs(round(cpue_short$change[3], 1))`%, and postrecruits increased by `r abs(round(cpue_short$change[5], 1))`%. Recruit and postrecruit RKC CPUEs are above their long-term averages and the prerecruit RKC CPUE is near its long-term average.

- Juvenile male RKC CPUE is near the long-term average and lower than the previous year. This is the fourth consecutive year of declining juvenile male CPUE, although past discussions have noted that this survey is primarily designed to quantify mature male RKC and Dungeness crab pots compete for juvenile RKC males during the time of the Juneau Area survey.

- Due to the decreases in prerecruit and recruit RKC CPUEs, a maximum harvest rate of 8% is recommended for the 2026/2027 season with the goal of supporting multiple years of commercial fishery openers.

- The Excel CSA model was used to estimate these results. The RTMB likelihood model (the new model) requires further development due to inconsistent estimates in the data-moderate areas.


# STOCK ASSESSMENT {-}
The following is a summary of the biomass estimates and stock status of red king crab (RKC) for the Juneau Area (Section 11-A) for the `r cur_yr`/`r fut_yr` season. Stock assessment methods for `r cur_yr` are identical to those used since 2012; however, in 2017 adjustments to historic (1993–2004) catch-per-unit-effort (CPUE) calculations were performed so that all CPUEs are now calculated using a stratified, weighted mean.  This corrected the long-term baseline (1995–2007) values used to determine stock health (Figure \@ref(fig:jnumodel), Table \@ref(tab:stock-status)), which in turn more accurately depicted the stock health status over time; this was specifically relevant for juvenile males and females. 

The biomass estimates for legal and mature RKC from a 3-stage catch-survey analysis (CSA) for the **Juneau Area are `r format(round(change_forecast$legal_curyr[2], 0), big.mark = ",")` lb and `r format(round(change_forecast$mature_curyr[2],0), big.mark = ",")` lb respectively for the `r cur_yr` season** (Figure \@ref(fig:jnumodel)). This is a `r change_forecast$leg_change[2]`% increase in legal male RKC biomass and `r abs(change_forecast$mat_change[2])`% decrease in mature male RKC biomass from the `r pr_yr` predicted biomass levels (Figure A1). Using the `r cur_yr` model, with estimates of historic biomass values informed by a data set that includes the current year, legal biomass increased `r change_forecast$leg_cur_change[2]`% and mature biomass increased `r change_forecast$mat_cur_change[2]`% from `r pr_yr` (Figure \@ref(fig:jnumodel)). Male RKC recruit and postrecruit CPUEs are above their respective long-term averages, while the male RKC prerecruit CPUE is non-significantly different from its long-term average (Figure \@ref(fig:panel2)). The mature female, juvenile male, and juvenile female RKC CPUEs are non-significantly different from their respective long-term averages (Figure \@ref(fig:panel3)). Juvenile male and female RKC CPUEs have notable short-term decreasing trends (Figure \@ref(fig:panel3)).

The realized harvest rate in `r pr_yr` was 9.0% of the legal biomass. The `r cur_yr ` legal and mature biomass estimates are well above their long term averages (Figure \@ref(fig:panel2)). The clutch fullness of mature females remains high and few poor clutches were evident (Figure \@ref(fig:panel3)).

The stock status for the Juneau Area is “above average” in `r cur_yr`, down from "healthy" in `r pr_yr` (Table \@ref(tab:stock-status)). This decrease in stock health is due to the relative decrease in prerecruit male and mature female RKC CPUEs compared to `r pr_yr` as well as the decreasing short-term trends in juvenile male and juvenile female RKC CPUEs.

Determining an appropriate harvest level for RKC in Southeast Alaska, specifically the Juneau Area, is a complex task. Prior to 2012, the matrix for stock health (Table \@ref(tab:stock-status)) was used to suggest an appropriate harvest rate. In 2012 this was replaced with an equilibrium harvest rate that was calculated from the relationship between observed harvest rate and observed change in mature biomass. In theory (given a stable population with consistent growth and recruitment), this calculated equilibrium harvest rate would have an equal chance of producing an increase or decrease in the mature population size, therefore being a risk-neutral choice.  

Prior to the 2018 survey, the equilibrium harvest rate was re-analyzed using data up to the 2017/18 season. The results of this analysis, for the Juneau Area, suggest an equilibrium harvest rate of 17%, which is the same as previous analyses (Figure \@ref(fig:equil), panel 1).  Despite a statistically strong relationship (p <0.01), this estimate continues to have substantial variability. To understand this variability, the analysis was repeated on subsets of the data: years with declining/low abundance, years with increasing/high abundance, and the currently used baseline years (Figure \@ref(fig:equil), panels 2-4). These subsets suggest a range of harvest rates from 6 to 25%; these rates are presented as harvest options, with the exception of 25%, because 20% is thought to be the maximum harvest that should be applied to mature king crab populations throughout Alaska (Tables \@ref(tab:harv-rate) and \@ref(tab:harv-rate-num)). 

Recent explorations of the relationship between harvest rates and observed changes in mature biomass in the Juneau Area suggest strong first-order autoregression (AR1), suggesting that the change in mature biomass under a specific harvest rate is strongly related to the mature biomass in the previous year and that we cannot set harvest rates independent of each other. Further exploration is underway to use this relationship in predicting an appropriate harvest rate. 

Under-reporting of harvest in the personal use fishery (10% and 13% of permits were not reported in previous personal use seasons 2024 and 2025 respectively) and the decrease in mature biomass associated with the 10% harvest rate in 2017 and 8% harvest rate in 2018 suggest a reduced harvest rate from the equilibrium rate of 17% or maximum 20%.

The years 2022-2025 of survey data implied a strong recruitment pulse in the Juneau Area RKC population. Survey data from this year (2026) indicated, with high levels of postrecruits and low levels of prerecruits, that RKC are still abundant in the Juneau Area but this large cohort may be phasing out and lower-catch years may be on the horizon. The absence of a decline in the biomasses in legal and mature male RKC in 2026 following the 2025 commercial fishery suggests that the commercial harvest did not negatively affect the stock, but the decrease in male prerecruit and recruit CPUEs raise the concern that stock biomass may decline in future years. The decreasing trend in juvenile male and female CPUEs may also indicate an increased risk of declining stock biomass in the near future, although the survey may not accurately assess juvenile CPUE.

The harvest rate of 10% that was applied in 2017 was enacted with the goal of allowing for population growth, since it was substantially lower than the 17% equilibrium harvest rate. Following the observed decrease in the estimated mature biomass, the harvest rate in 2018 was set at 8%, once again with the goal of allowing for overall population growth and the commercial fishery was closed. Note that the realized harvest rate is measurably less than the set harvest rate in instances where the commercial fishery is closed, as the personal use fishery is allocated only 60% of the total catch. Because the mature biomass still decreased after 2018, a further reduction in harvest pressure to 7% was enacted in 2019 with a closed commercial fishery. The harvest rate (7%; comm fishery closed) set in the  years 2020, 2021, and 2022 produced a relatively stable biomass estimate for legal and mature crab, with small (less than 8% decrease or increase) fluctuations in legal biomass estimates; the CPUEs of most mature male recruit classes showed an increase. The harvest rate in 2023 (10%; comm fishery closed) was associated with a decrease in CPUE for all male crab classes, although it is difficult to know to what extent the CPUE decreases were influenced by the harvest rate versus other factors such as environmental variation. After the 2024 harvest rate of 8% with the commercial fishery closed, all mature male crab CPUEs increased. After the 2025 harvest rate of 10% and commercial fishery opener, male postrecruit RKC CPUE is still high and has increased but prerecruit and recruit CPUEs have decreased.

Setting a harvest rate of 8%, lower than the 10% applied in the 2025-2026 season, would allow for some harvest while retaining crab for future years. This approach would be effective if the goal is to sustain a commercial fishery over multiple seasons, given that the stock is anticipated to decline in the coming years. Harvest rates exceeding 8% could result in population declines, as postrecruit RKC would be fished without sufficient recruit RKC to replace them; the probability and magnitude of the decline increase in proportion to the harvest rate. To encourage sustainability and population growth, a **8% or less harvest rate is recommended** for the `r cur_yr`/`r fut_yr` personal use season. GHL allocation tables for multiple harvest rate strategies were constructed (Tables \@ref(tab:harv-rate) and \@ref(tab:harv-rate-num)). Although harvest rates of 20%, 17%, 15%, 12%, 10%, 9%, 8%, and 7% are shown, the data suggest that implementing the higher end of this range would not serve the goal of sustaining average baseline population levels.


\newpage

\blandscape

# TABLES {-}

```{r stock-status, results = "asis", tab.cap="Determination of stock status for the Juneau Area for the 2022–2026 surveys.  Values for long-term baseline analyses represent the percentage above or below the average CPUEs from 1995–2007 baseline (historically 1993 – 2007; see memo dated 6/23/2008 for discussion of baselines). Significant relationships result in $\\alpha$ < 0.05. Values for the short-term trends (last 4 years) are either significant increase, significant decrease, or no trend. Long-term scores are +1 for significantly above, 0 for not significantly different, or -1 for significantly below the baseline, except for clutch fullness < 25%, in which the signs are reversed because a score significantly below the baseline of 10% is considered a positive indicator of stock health. Short-term scores are +0.25 for significantly increasing trends, 0 for no trend, or -0.25 for significantly decreasing trends.  The total score is the sum of long- and short-term scores for each year. Stock status is defined by the total score: < -4.25 = Poor, -4.25 to -1.75 = Below Ave, -1.5 to 1.5 = Moderate, 1.75 to 4.25 = Above Ave, and > 4.25 = Healthy."}

# create lists of required files from all year folders
# first create vector of paths
results.paths <- c(paste0(here::here(), "/results/rkc/Juneau/", yr1), paste0(here::here(), "/results/rkc/Juneau/", yr2), paste0(here::here(), "/results/rkc/Juneau/", yr3), paste0(here::here(), "/results/rkc/Juneau/", yr4), paste0(here::here(), "/results/rkc/Juneau/", yr5))

# create file lists
longterm.files <- list.files(path = results.paths, pattern = "longterm.csv", recursive = TRUE, full.names = TRUE) #should be more than one??
shortterm.files <- list.files(path =  results.paths, pattern = "shortterm.csv", recursive = TRUE, full.names = TRUE)
stockhealth.files <- list.files(path =  results.paths, pattern = "stock_health.csv", recursive = TRUE, full.names = TRUE)
ltfem.files <- list.files(path =  results.paths, pattern = "lt_female.csv", recursive = TRUE, full.names = TRUE)
stfem.files <- list.files(path =  results.paths, pattern = "short_female.csv", recursive = TRUE, full.names = TRUE)

# read in csv files
lt.files <- purrr::map(longterm.files, read_csv) %>% #AGR here- flag! something might be up
  # calculate % difference with long-term mean
  map(~mutate(., vs.lt.base = round((mean / lt.mean) * 100, 0)))
st.files <- purrr::map(shortterm.files, read_csv)
sh.files <- purrr::map(stockhealth.files, read_csv) 
lf.files <- purrr::map(ltfem.files, read_csv) %>%
  # calculate % difference with long-term mean of 10%
  map(~mutate(., vs.lt.mean = round((mean / 0.1) * 100, 0)))
sf.files <- purrr::map(stfem.files, read_csv)

# make vectors to go into table
stat.cat <- c("Large/mature female CPUE", "", "", "Small/immature female CPUE", "", "", "Juvenile males", "", "", "Prerecruit CPUE", "", "", "Recruit CPUE", "", "", "Postrecruit CPUE", "", "", "Clutch fullness < 25 percent", "", "", "Total score", "Stock status", "Maximum mature harvest rate")
stat.type <- c("vs. long-term average: percent of baseline", "vs. long-term average: score", "short-term trend: score", "vs. long-term average: percent of baseline", "vs. long-term average: score", "short-term trend: score", "vs. long-term average: percent of baseline", "vs. long-term average: score", "short-term trend: score", "vs. long-term average: percent of baseline", "vs. long-term average: score", "short-term trend: score", "vs. long-term average: percent of baseline", "vs. long-term average: score", "short-term trend: score", "vs. long-term average: percent of baseline", "vs. long-term average: score", "short-term trend: score", "vs. long-term average: percent of baseline", "vs. long-term average: score", "short-term trend: score", "", "", "")
stat.1 <- c(lt.files[[1]] %>% filter(recruit.status == "Large.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Large.Female") %>% select(significant) %>% pull(), 
            st.files[[1]] %>% filter(recruit.status == "Large.Females") %>% select(score) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Small.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Small.Female") %>% select(significant) %>% pull(), 
            st.files[[1]] %>% filter(recruit.status == "Small.Females") %>% select(score) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Juvenile") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Juvenile") %>% select(significant) %>% pull(), 
            st.files[[1]] %>% filter(recruit.status == "Juvenile") %>% select(score) %>% pull(),
            lt.files[[1]] %>% filter(recruit.status == "Pre_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Pre_Recruit") %>% select(significant) %>% pull(), 
            st.files[[1]] %>% filter(recruit.status == "Pre_Recruit") %>% select(score) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Recruit") %>% select(significant) %>% pull(), 
            st.files[[1]] %>% filter(recruit.status == "Recruit") %>% select(score) %>% pull(),
            lt.files[[1]] %>% filter(recruit.status == "Post_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Post_Recruit") %>% select(significant) %>% pull(), 
            st.files[[1]] %>% filter(recruit.status == "Post_Recruit") %>% select(score) %>% pull(),
            lf.files[[1]] %>% select(vs.lt.mean) %>% pull(),
            lf.files[[1]] %>% select(significant) %>% pull(), 
            sf.files[[1]] %>% select(score) %>% pull(), 
            sh.files[[1]]$score, 
            sh.files[[1]]$health_status, 
            sh.files[[1]]$harvest_per)#that part all seems to work
stat.2 <- c(lt.files[[2]] %>% filter(recruit.status == "Large.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Large.Female") %>% select(significant) %>% pull(), 
            st.files[[2]] %>% filter(recruit.status == "Large.Females") %>% select(score) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Small.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Small.Female") %>% select(significant) %>% pull(), 
            st.files[[2]] %>% filter(recruit.status == "Small.Females") %>% select(score) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Juvenile") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Juvenile") %>% select(significant) %>% pull(), 
            st.files[[2]] %>% filter(recruit.status == "Juvenile") %>% select(score) %>% pull(),
            lt.files[[2]] %>% filter(recruit.status == "Pre_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Pre_Recruit") %>% select(significant) %>% pull(), 
            st.files[[2]] %>% filter(recruit.status == "Pre_Recruit") %>% select(score) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Recruit") %>% select(significant) %>% pull(), 
            st.files[[2]] %>% filter(recruit.status == "Recruit") %>% select(score) %>% pull(),
            lt.files[[2]] %>% filter(recruit.status == "Post_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Post_Recruit") %>% select(significant) %>% pull(), 
            st.files[[2]] %>% filter(recruit.status == "Post_Recruit") %>% select(score) %>% pull(),
            lf.files[[2]] %>% select(vs.lt.mean) %>% pull(),
            lf.files[[2]] %>% select(significant) %>% pull(), 
            sf.files[[2]] %>% select(score) %>% pull(), 
            sh.files[[2]]$score, 
            sh.files[[2]]$health_status, 
            sh.files[[2]]$harvest_per)
stat.3 <- c(lt.files[[3]] %>% filter(recruit.status == "Large.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Large.Female") %>% select(significant) %>% pull(), 
            st.files[[3]] %>% filter(recruit.status == "Large.Females") %>% select(score) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Small.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Small.Female") %>% select(significant) %>% pull(), 
            st.files[[3]] %>% filter(recruit.status == "Small.Females") %>% select(score) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Juvenile") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Juvenile") %>% select(significant) %>% pull(), 
            st.files[[3]] %>% filter(recruit.status == "Juvenile") %>% select(score) %>% pull(),
            lt.files[[3]] %>% filter(recruit.status == "Pre_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Pre_Recruit") %>% select(significant) %>% pull(), 
            st.files[[3]] %>% filter(recruit.status == "Pre_Recruit") %>% select(score) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Recruit") %>% select(significant) %>% pull(), 
            st.files[[3]] %>% filter(recruit.status == "Recruit") %>% select(score) %>% pull(),
            lt.files[[3]] %>% filter(recruit.status == "Post_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Post_Recruit") %>% select(significant) %>% pull(), 
            st.files[[3]] %>% filter(recruit.status == "Post_Recruit") %>% select(score) %>% pull(),
            lf.files[[3]] %>% select(vs.lt.mean) %>% pull(),
            lf.files[[3]] %>% select(significant) %>% pull(), 
            sf.files[[3]] %>% select(score) %>% pull(), 
            sh.files[[3]]$score, 
            sh.files[[3]]$health_status, 
            sh.files[[3]]$harvest_per)
stat.4 <- c(lt.files[[4]] %>% filter(recruit.status == "Large.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Large.Female") %>% select(significant) %>% pull(), 
            st.files[[4]] %>% filter(recruit.status == "Large.Females") %>% select(score) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Small.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Small.Female") %>% select(significant) %>% pull(), 
            st.files[[4]] %>% filter(recruit.status == "Small.Females") %>% select(score) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Juvenile") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Juvenile") %>% select(significant) %>% pull(), 
            st.files[[4]] %>% filter(recruit.status == "Juvenile") %>% select(score) %>% pull(),
            lt.files[[4]] %>% filter(recruit.status == "Pre_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Pre_Recruit") %>% select(significant) %>% pull(), 
            st.files[[4]] %>% filter(recruit.status == "Pre_Recruit") %>% select(score) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Recruit") %>% select(significant) %>% pull(), 
            st.files[[4]] %>% filter(recruit.status == "Recruit") %>% select(score) %>% pull(),
            lt.files[[4]] %>% filter(recruit.status == "Post_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Post_Recruit") %>% select(significant) %>% pull(), 
            st.files[[4]] %>% filter(recruit.status == "Post_Recruit") %>% select(score) %>% pull(),
            lf.files[[4]] %>% select(vs.lt.mean) %>% pull(),
            lf.files[[4]] %>% select(significant) %>% pull(), 
            sf.files[[4]] %>% select(score) %>% pull(), 
            sh.files[[4]]$score, 
            sh.files[[4]]$health_status, 
            sh.files[[4]]$harvest_per)
stat.5 <- c(lt.files[[5]] %>% filter(recruit.status == "Large.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Large.Female") %>% select(significant) %>% pull(), 
            st.files[[5]] %>% filter(recruit.status == "Large.Females") %>% select(score) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Small.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Small.Female") %>% select(significant) %>% pull(), 
            st.files[[5]] %>% filter(recruit.status == "Small.Females") %>% select(score) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Juvenile") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Juvenile") %>% select(significant) %>% pull(), 
            st.files[[5]] %>% filter(recruit.status == "Juvenile") %>% select(score) %>% pull(),
            lt.files[[5]] %>% filter(recruit.status == "Pre_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Pre_Recruit") %>% select(significant) %>% pull(), 
            st.files[[5]] %>% filter(recruit.status == "Pre_Recruit") %>% select(score) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Recruit") %>% select(significant) %>% pull(), 
            st.files[[5]] %>% filter(recruit.status == "Recruit") %>% select(score) %>% pull(),
            lt.files[[5]] %>% filter(recruit.status == "Post_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Post_Recruit") %>% select(significant) %>% pull(), 
            st.files[[5]] %>% filter(recruit.status == "Post_Recruit") %>% select(score) %>% pull(),
            lf.files[[5]] %>% select(vs.lt.mean) %>% pull(),
            lf.files[[5]] %>% select(significant) %>% pull(), 
            sf.files[[5]] %>% select(score) %>% pull(), 
            sh.files[[5]]$score, 
            sh.files[[5]]$health_status, 
            sh.files[[5]]$harvest_per)

# make table data frame and set names
stockstat.tab <- data.frame(stat.cat, stat.type, stat.1, stat.2, stat.3, stat.4, stat.5)
names(stockstat.tab) <- c("", "", yr1, yr2, yr3, yr4, yr5)

kable(stockstat.tab, format = "pandoc")

#stockstat.tab1 <- xtable(stockstat.tab, digits = 0, caption = "Determination of stock status for the Juneau Area for 2018–2023 surveys.  Values for long-term baseline analyses represent the percentage above or below the average CPUEs from 1995–2007 baseline (historically 1993 – 2007; see memo dated 6/23/2008 for discussion of baselines). Significant relationships result in $\\alpha$ < 0.05. Values for the short-term trends (last 4 years) are either significant increase, significant decrease, or no trend. Long-term scores are +1 for significantly above, 0 for not significantly different, or -1 for significantly below the baseline, except for clutch fullness < 25%, in which the signs are reversed because a score significantly below the baseline of 10% is considered a positive indicator of stock health. Short-term scores are +0.25 for significantly increasing trends, 0 for no trend, or -0.25 for significantly decreasing trends.  The total score is the sum of long- and short-term scores for each year. Stock status is defined by the total score: < -4.25 = Poor, -4.25 to -1.75 = Below Ave, -1.5 to 1.5 = Moderate, 1.75 to 4.25 = Above Ave, and > 4.25 = Healthy. ", label = "tab:stock-status", format = "pandoc")

#print(stockstat.tab1, caption.placement = "top", include.rownames = FALSE, comment=FALSE, sanitize.text.function=function(x){x})
```



```{r ghl-harv, results = "asis"}

# note: each year, add one row to the import (e.g., if in 2023 range is A5:L50, then in 2024 range is A5:L51)
ghl_harv <- read_excel(paste0(here::here(), "/CSA_excel/Juneau ", cur_yr, " CPUE correction postsolver.xls"), sheet = "Table 2_currentYR", range = "A5:L53") 

colnames(ghl_harv) <- c("Year", "Legal biomass (lb)", "Mature biomass (lb)", "Rec. GHL (lb)", "Rec. PU GHL (lb)", "Rec. harvest rate", "Comm. fishery status", "Est. PU harvest (lb)", "Est. comm. harvest (lb)", "Est. total harvest (lb)", "Est. mature harvest rate", "Est. legal harvest rate")

ghl_harv1 <- ghl_harv %>% mutate(Year = as.character(Year)) %>%
  mutate(`Comm. fishery status` = case_when(
    `Comm. fishery status` == "Com. closed" ~ "Closed",
    Year == cur_yr ~ "TBD",
    TRUE ~ `Comm. fishery status`
  )) %>%
  mutate(`Est. mature harvest rate` = as.double(`Est. mature harvest rate`)) %>% #added from Caitlin code- 7/18/24
  mutate(`Est. legal harvest rate` = as.double(`Est. legal harvest rate`))%>%
  mutate(`Rec. GHL (lb)` = round(as.numeric(`Rec. GHL (lb)`), 0)) %>% #AI added 2026
mutate(`Rec. PU GHL (lb)` = round(as.numeric(`Rec. PU GHL (lb)`), 0)) %>% #AI aded 2026
  mutate(across(c(11, 12), ~ scales::label_percent(accuracy = 0.1)(.x))) %>% #updated c(11,12) for this specific table
  mutate(across(c(6), ~ scales::label_percent(accuracy = 1)(.x))) %>% #attempt to fix the rec harvest rate column
  mutate(across(where(is.double), ~ round(.x, 0))) %>%
  filter(Year > 1995) #ar added to make 1996 onward our table years

pandoc.table(ghl_harv1, keep.line.breaks = TRUE, big.mark = ',', digits = c(1,1,1,1,1,2,1,1,1,1,2,2), missing = "-", split.tables = Inf, caption = "Comparison of 2026 model output of legal biomass and mature biomass, and the recommended Guideline Harvest Level (GHL), to the harvest of RKC in the Juneau Area from 1996–2026. Estimated personal use (PU) harvest is calculated using the number of crabs reported for each permit and the average legal weight in the survey each year (since 1996). Total harvest includes both commercial and PU harvest (lb). Recommended harvest rate is % of mature biomass before 2022 and % of legal biomass from 2022 on\\label{tab:ghl-harv}.")

```

\newpage


```{r harv-rate, results = "asis"}

panderOptions('table.split.table', Inf)

harv.rate.lb <- read_excel(paste0(here::here(), "/CSA_excel/Juneau ", cur_yr, " CPUE correction postsolver_newT3.xls"), sheet = "Table 3", range = "C5:K11") %>% 
  mutate(`GHL Allocation` = case_when(
    is.na(`GHL Allocation`) == TRUE ~ "GHL allocation (lb)",
    `GHL Allocation` == "PU Summer" ~ "PU summer (50%)",
    `GHL Allocation` == "PU Winter" ~ "PU winter (10%)",
    `GHL Allocation` == "Commercial" ~ "Commercial (40%)",
    `GHL Allocation` == "Total" ~ "Total (lb)" 
  ))

header.row <- harv.rate.lb %>%
  slice(1) %>% 
  mutate(across(where(is.double), ~ scales::percent(.x)))

names(harv.rate.lb) <- as.character(header.row)
harv.rate.lb.tab <- harv.rate.lb %>% slice(-1, -5)

pandoc.table(harv.rate.lb.tab, big.mark = ',', digits = 1, missing = "-", caption = "Estimated biomass and allocation of RKC in the Juneau Area under a range of harvest rate strategies for 2026. All Guideline Harvest Levels (GHLs) are in lb and are applied to legal biomass (lb). \\label{tab:harv-rate}")

```



```{r harv-rate-num, results = "asis"}

panderOptions('table.split.table', Inf)

harv.rate.n <- read_excel(paste0(here::here(), "/CSA_excel/Juneau ", cur_yr, " CPUE correction postsolver_newT3.xls"), sheet = "Table 3", range = "C19:K25") %>% 
  mutate(`GHL Allocation` = case_when(
    is.na(`GHL Allocation`) == TRUE ~ "GHL allocation (number)",
    `GHL Allocation` == "PU Summer" ~ "PU summer (50%)",
    `GHL Allocation` == "PU Winter" ~ "PU winter (10%)",
    `GHL Allocation` == "Commercial" ~ "Commercial (40%)",
    `GHL Allocation` == "Total" ~ "Total (number)" 
  ))

header.row.n <- harv.rate.n %>%
  slice(1) %>% 
  mutate(across(where(is.double), ~ scales::percent(.x)))

names(harv.rate.n) <- header.row.n
harv.rate.n.tab <- harv.rate.n %>% slice(-1, -5)

pandoc.table(harv.rate.n.tab, big.mark = ',', digits = 1, missing = "-", caption = "Estimated numbers and allocation of RKC in the Juneau Area under a range of harvest rate strategies for 2026.  Guideline Harvest Levels (GHLs) are in approximate numbers of legal crab.  Conversion from biomass (lb) to numbers is done by dividing the biomass by the average legal weight from the Juneau Area survey (2026 average survey legal length converted to weight = 7.73 lb per crab, mature weight = 7.07 lb per crab). GHL allocation is calculated by applying the average legal weight to the above GHL of legal biomass. \\label{tab:harv-rate-num}")

panderOptions('table.split.table', 80)  # reset to default

```

\elandscape


```{r pu-tab, results = "asis"}
#AGR 25 this one works!! but need to update to 25?

pu.tab <- read.csv(paste0(here::here(), "/results/rkc/Juneau/PU_since_2018_updated", cur_yr, ".csv")) %>%
  mutate(Year = as.factor(Year)) %>%
  dplyr::rename("Summer \\\n \\\n \\\nPermits" = Summer.Permits) %>%
  dplyr::rename("Summer \\\n \\\n \\\nFished" = Summer...fished) %>%
  dplyr::rename("Summer \\\nReturned, \\\nnot fished" = Summer...returned.but.not.fished) %>%
  dplyr::rename("Summer \\\n \\\nNot \\\nreturned" = Summer...not.returned) %>%
  dplyr::rename("Summer \\\n \\\nEst. \\\nharvest" = Summer.estimated.harvest) %>%
  dplyr::rename("Winter \\\n \\\n \\\nPermits" = Winter.Permits) %>%
  dplyr::rename("Winter \\\n \\\n \\\nFished" = Winter...fished) %>%
  dplyr::rename("Winter \\\nReturned, \\\nnot fished" = Winter...returned.but.not.fished) %>%
  dplyr::rename("Winter \\\n \\\nNot \\\nreturned" = Winter...not.returned) %>%
  dplyr::rename("\\\n \\\n \\\nEst. \\\nharvest" = Winter.estimated.harvest) %>%
dplyr::rename("Total \\\nharvest" = Total.harvest) %>%
  mutate(across(c(3:5, 8:10), ~ paste0(.x, "%")))
  #mutate(across(c(3:5, 8:10), ~ scales::percent(.x)))

panderOptions('keep.line.breaks', TRUE)
pandoc.table(pu.tab, style="multiline", keep.line.breaks = TRUE, split.tables = Inf, big.mark = ',', digits = 1, missing = "-", caption = "Estimated personal use harvest by year and season for all years since 2018, in numbers of crabs. Estimated harvest is calculated using the number of crabs reported for each permit as well as the estimated harvest from those permits that were not returned. Total numbers of permits issued by season are reported, as well as the percentages of permits in each season that were fished, returned but not fished, and not returned. \\label{tab:pu-tab}")

```



\newpage

# FIGURES {-}

```{r jnumodel, fig.cap = "Juneau Area biomass estimates for legal (black symbols) and mature (gray symbols) red king crab from the current year’s 3-stage catch-survey analysis model. Black and grey (dashed) horizontal reference lines represent mean estimates during baseline years (1995–2007). Fishery status is reported in symbol type; closed status is when both commercial and personal use (PU) fisheries are closed and PU only status indicates that only a PU fishery occurred (commercial fishery was closed in that year).", out.width="90%"}
#need to update to the fig listed

knitr::include_graphics(paste0(here::here(), '/figures/rkc/', cur_yr,'/jnu_rkc_fig1_edited.png'), dpi = 125)
#AGR 25 change end yera to 2025 plz

#knitr::include_graphics(paste0(here::here(), '/figures/rkc/', cur_yr,'/jnu_rkc_fig1_edited_v2.png'), dpi = 125) #ugh why can I find the new version
```


```{r jnu-csa, fig.cap = "The current year’s CSA model fit. The blue lines represent the model fit and the black points are the standardized CPUE", out.width="90%"}

knitr::include_graphics(paste0(here::here(), '/figures/rkc/', cur_yr,'/Juneau_cpue_model_fit.png'), dpi = 125)
```

```{r panel2, fig.cap = "Survey CPUE for male size/sex classes of red king crab along with biomass and harvest estimates for the Juneau Area from 1995–2026 using the 2026 model output.  The horizontal reference lines indicate long-term averages, defined as the average CPUEs from 1995–2007. There is no mark-recapture adjustment for the Juneau Area. ", out.width="90%"}

knitr::include_graphics(paste0(here::here(), '/figures/rkc/', cur_yr,'/Juneau_', cur_yr, '_2.png'), dpi = 125)
```

```{r panel3, fig.cap = "Survey CPUE for female and juvenile size/sex classes of red king crab along with female percentage of poor clutches (% poor clutch) and overall clutch fullness (total % clutch).  The horizontal reference lines indicate long-term averages, defined as the average CPUEs from 1995–2007.", out.width="90%"}
knitr::include_graphics(paste0(here::here(), '/figures/rkc/', cur_yr,'/Juneau_', cur_yr, '_3.png'), dpi = 125)
```

```{r equil, fig.cap = "Relationships between estimated harvest rate and population change of red king crab based on CSA biomass estimates (with 95% CI) for a) all years (1979–2017), b) decreasing/depressed time (2000–2012) and increasing/ high time (1990–1999), and c) baseline years (1993–2007). Harvest rate is calculated as commercial catch/mature male biomass.  Population change is calculated as (mature male biomass at time (t+1) - mature male biomass at time (t))/mature male biomass at time (t). The horizontal reference line indicates population equilibrium; the vertical reference line indicates equilibrium harvest rate.", out.width="90%"}
knitr::include_graphics(paste0(here::here(), '/figures/rkc/Juneau_memo_equil_rate.png'), dpi = 125)

```




\clearpage

# Appendix A. Historic record of annual model forecast {-}

```{r afig1, fig.cap = "Annual forecasts of Juneau Area biomass estimates for legal (black points) and mature (gray points) red king crab as annual point estimates (forecasts) from the 3-stage catch-survey analysis model. Black and grey (dashed) reference lines represent mean estimates during baseline years (1995–2007). Fishery status is reported in symbol type; closed status is when both commercial and personal use (PU) fisheries are closed and PU only status indicates that only a PU fishery occurred (commercial fishery was closed in that year).", out.width="90%"}

knitr::include_graphics(paste0(here::here(), '/figures/rkc/', cur_yr,'/jnu_rkc_annual_fore.png'), dpi = 125)
```


\newpage


```{r ghl-harv-hist, results = "asis"}

# note: each year, add one row to the import (e.g., if in 2023 range is A5:L50, then in 2024 range is A5:L51)

ghl_harv_hist <- read_excel(paste0(here::here(), "/CSA_excel/Juneau ", cur_yr, " CPUE correction postsolver.xls"), sheet = "Table 2", range = "A4:K53") %>%
  slice(-1) %>%
  select(-Recommended) 

colnames(ghl_harv_hist) <- c("Year", "Legal biomass (lb)", "Mature biomass (lb)", "Rec. PU GHL (lb)", "Comm. fishery status", "Est. PU harvest (lb)", "Est. comm. harvest (lb)", "Est. total harvest (lb)", "Est. mature harvest rate", "Est. legal harvest rate")

ghl_harv_hist1 <- ghl_harv_hist %>% mutate(Year = as.character(Year)) %>%
  mutate(`Comm. fishery status` = case_when(
    `Comm. fishery status` == "Com. closed" ~ "Closed",
    Year == cur_yr ~ "TBD",
    TRUE ~ `Comm. fishery status`
  )) %>%
  mutate(`Est. mature harvest rate` = as.double(`Est. mature harvest rate`)) %>%
  mutate(`Est. legal harvest rate` = as.double(`Est. legal harvest rate`))%>%
  mutate(across(c(9, 10), ~ scales::label_percent(accuracy = 0.1)(.x))) %>%
  mutate(across(where(is.double), ~ round(.x, 0))) %>%
  filter(Year > 1995)
  

pandoc.table(ghl_harv_hist1, keep.line.breaks = TRUE, big.mark = ',', digits = 1, missing = "-", split.tables = Inf, caption = "Comparison of annual forecast legal biomass and mature biomass and the recommended Personal Use Guideline Harvest Level (PU GHL) to the harvest of RKC in the Juneau Area from 1996–2026. Annual forecast for the biomass estimates is the point estimate generated in the year and uses survey data only up to that year in the model, i.e. 2012 estimates here are those generated from the model output in 2012. Estimated personal use (PU) harvest is calculated using the number of crabs reported for each permit and the average legal weight in the survey each year (since 1996). Total harvest includes both commercial and PU harvest (lb). \\label{tab:ghl-harv-hist}")

```


\newpage


```{r stan-cpue, results = "asis"}

cp <- read.csv(paste0(here::here(), "/results/rkc/Juneau/", cur_yr, "/cpue_wt_since_95.csv")) %>%
  mutate(Year = as.factor(Year)) %>%
  mutate(across(where(is.double), ~ round(.x, 2))) %>%
  mutate("Pre-recruit" = paste0(Pre_Recruit_wt, " $\\pm$ ", PreR_SE)) %>%
  mutate("Recruit" = paste0(Recruit_wt, " $\\pm$ ", Rec_SE)) %>%
  mutate("Post-recruit" = paste0(Post_Recruit_wt, " $\\pm$ ", PR_SE)) %>%
  mutate("Juvenile male" = paste0(Juvenile_wt, " $\\pm$ ", Juv_SE)) %>%
  mutate("Mature female" = paste0(MatF_wt, " $\\pm$ ", MatF_SE)) %>%
  mutate("Juvenile female" = paste0(SmallF_wt, " $\\pm$ ", SmallF_SE)) %>%
  select(Year, `Pre-recruit`, Recruit, `Post-recruit`, `Juvenile male`, `Mature female`, `Juvenile female`)
  

pandoc.table(cp, split.tables = Inf, caption = "Standardized catch per unit effort (CPUE) from the Juneau Area red king crab survey. Estimates are displayed $\\pm$ standard error. \\label{tab:stan-cpue}")

```


