---
title: "Juneau area (11-A) red king crab assessment CONFIDENTIAL memo "
author: "Alex Reich (alex.reich@alaska.gov) and Caitlin Stern"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  bookdown::pdf_document2:
    fig_caption: true
    includes: null
    toc: no
header-includes:
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
   - \usepackage{pdflscape}
   - \newcommand{\blandscape}{\begin{landscape}}
   - \newcommand{\elandscape}{\end{landscape}}

---

\pagenumbering{arabic}

```{r global_options, include=FALSE, echo = FALSE, message = FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(tidyverse)
library(purrr)
library(readxl)
library(pander)
source(paste0(here::here(), '/code/functions.R'))
cur_yr <- 2024
pr_yr <- cur_yr-1
fut_yr <- cur_yr+1
opts_chunk$set(fig.width = 12, fig.height = 7, echo = FALSE, warning = FALSE, message = FALSE,  dpi=300)
options(scipen = 100)

yr5 <- 2024
yr4 <- yr5 - 1
yr3 <- yr5 - 2
yr2 <- yr5 - 3
yr1 <- yr5 - 4

set_flextable_defaults(
  font.family = "Arial", 
  font.size = 9,
  font.color = "black",
  table.layout = "autofit",
  text.align = "center"
  #digits = 1,
  #theme_fun = "theme_box"
  )
#\pagenumbering{gobble}
```

```{r exesum, echo = FALSE}
# run code/CSA_model/JNU_RKC_masterfile_crabCSA....... for figures of cpue fit
biomass <- read.csv(paste0(here::here(), '/data/rkc/biomass.csv'))
biomass %>% 
  filter(Location == "Juneau") -> jnu_biomass
hindcast <- read.csv(paste0(here::here(), '/data/rkc/Juneau/hind_fore_cast_JNU_current.csv'))

cpue <- read.csv(paste0(here::here(), '/results/rkc/Juneau/', cur_yr, '/JNU_CPUE_', cur_yr,'.csv'))

# change from previous year's forecasted values 
hindcast %>% 
  filter(year >= pr_yr) %>% 
  mutate(leg_change = round((legal_forecast - lag(legal_forecast))/ lag(legal_forecast)*100, 1), 
         mat_change = round((mature_forecast - lag(mature_forecast))/ lag(mature_forecast)*100, 1), 
         leg_cur_change = round((legal_curyr - lag(legal_curyr))/ lag(legal_curyr)*100, 1), 
         mat_cur_change = round((mature_curyr - lag(mature_curyr))/ lag(mature_curyr)*100, 1)) -> change_forecast

# cpue and change in cpue from last year
#cpue %>% 
#  gather(Rclass, cpue, Pre_Recruit_wt:SmallF_SE)
cpue_short <- as.data.frame(t(cpue))
cpue_short[2:13, ] -> cpue_short
colnames(cpue_short) <- c("2022", "2023")
cpue_short %>% 
  mutate(change = ((`2023` - `2022`)/`2022`)*100) -> cpue_short

cpue %>% 
  filter(Year == cur_yr) -> cpue2
```


# `r cur_yr` SUMMARY POINTS {-}
- A harvest rate of 10% was implemented for the `r pr_yr`/`r cur_yr` personal use and commercial fisheries; estimated actual harvest rate was 5.3% due to lack of a commercial fishery opening. In the prior three seasons, similar harvest rates were implemented and the commercial fishery was closed, resulting in an estimated actual harvest rate of 4.0% in 2022/2023, 3.8% in 2021/2022, and 4.5% in 2020/2021. 

- Estimated legal (up `r change_forecast$leg_change[2]`%) and mature (up `r change_forecast$mat_change[2]`%) biomass both increased compared to `r pr_yr` predicted values. Legal and mature biomass both remain above the long-term average (using baseline years). However, these biomass estimates rely on higher estimated abundances of recruit and post-recruit males than were observed in the 2024 survey, and so should be interpreted with caution.

- Pre-recruit CPUE decreased from `r pr_yr` (`r round(cpue_short$change[1], 1)` %), and is near its long-term average. Both recruit and post-recruit CPUE decreased from `r pr_yr` (`r round(cpue_short$change[3], 1)` % and `r round(cpue_short$change[5], 1)` % respectively) and are non-significantly above the long-term average. 

- Juvenile male CPUE is `r round(cpue2$Juvenile_wt,1)`, non-significantly above the long-term average but lower than in the previous three years. This should be monitored for further declining trends.

- Due to the decreases in pre-recruit, recruit, and post-recruit CPUE from 2023 to 2024, and the uncertainty with respect to the estimated biomass values, a harvest rate of 7% or less for the 2024/2025 season is recommended.


# STOCK ASSESSMENT {-}
The following is a summary of the biomass estimates and stock status of red king crab (RKC) for the Juneau Area (Section 11-A) for the `r cur_yr`/`r fut_yr` season. Stock assessment methods for `r cur_yr` are identical to those used since 2012; however, in 2017 adjustments to historic (1993–2004) catch-per-unit-effort (CPUE) calculations were performed so that all CPUEs are now calculated using a stratified, weighted mean.  This corrected the long-term baseline (1995–2007) values used to determine stock health (Figure \@ref(fig:jnumodel), Table \@ref(tab:stock-status)), which in turn more accurately depicted the stock health status over time; this was specifically relevant for juvenile males and females. 

The biomass estimates for legal and mature RKC from a 3-stage catch-survey analysis (CSA) for the **Juneau area are `r format(round(change_forecast$legal_curyr[2], 0), big.mark = ",")` lb and `r format(round(change_forecast$mature_curyr[2],0), big.mark = ",")` lb respectively for the `r cur_yr` season** (Figure \@ref(fig:jnumodel)). This is a `r change_forecast$leg_change[2]`% increase in legal biomass and `r change_forecast$mat_change[2]`% increase in mature biomass from the `r pr_yr` predicted biomass levels (Figure \@ref(fig:afig1)). Similarly using the `r cur_yr` model, where estimates of the historic biomass are calculated with data that includes up to the current year, there was an `r change_forecast$leg_cur_change[2]`% increase in legal biomass and a `r change_forecast$mat_cur_change[2]`% increase in mature biomass (Figure \@ref(fig:jnumodel)). However, the 2024 model biomass estimates rely on higher estimated CPUEs of recruit and post-recruit males than were observed in the 2024 survey (Figure 2), and thus the model-predicted increase in biomass is likely an overestimate. Pre-recruit CPUE decreased substantially from `r pr_yr`, suggesting the potential for a decrease in recruitment in future years. Both recruit and post-recruit CPUE decreased from `r pr_yr` but are still above the long-term average (Figure \@ref(fig:panel2)). The poor fit of the model to the observed survey CPUE values suggests that more research is needed into Southeast red king crab life history, specifically growth increments and molting probabilities, to parameterize the underlying population dynamics more completely. 

The realized harvest rate in `r pr_yr` (5.3% of the mature biomass) was associated with a decrease in male recruit and post-recruit CPUE from `r pr_yr`. The legal biomass estimate is above the long-term average, however, trends in recruitment – in the form of pre-recruit and recruit CPUE – are down from 2023. Reduced harvest pressure may be warranted given the observed decreases in pre-recruit, recruit, and post-recruit male CPUEs. 

The stock status for the Juneau area is “above average”, down from "healthy" in `r pr_yr` and 2022 (Table \@ref(tab:stock-status)). The CPUEs of pre-recruit, recruit, and post-recruit males, as well as juveniles males and juvenile females, are not significantly different from their long-term averages; the CPUE of mature females is above the long-term average (Figure \@ref(fig:panel3)). There is evidence of a significant short-term (4-year) increase in mature female, pre-recruit, and recruit CPUEs; a significant short-term decrease in juvenile male and juvenile female CPUEs; and no significant trend in post-recruit CPUE over the last four years (Figure \@ref(fig:panel2), Figure \@ref(fig:panel3), Table \@ref(tab:stock-status)). The clutch fullness of mature females remains high and few poor clutches were evident (Figure \@ref(fig:panel3)).  

While the biomass estimates remain high, the lower CPUEs compared to `r pr_yr` for juvenile males, juvenile females, pre-recruit males, recruit males, and post-recruit males are notable. The lower pre-recruit male CPUE suggests a decrease in future recruitment in the population. However, mature female CPUE remains high.

Harvest of RKC in the Juneau area has been reduced below the equilibrium harvest rate of 17% (Figure \@ref(fig:equil), panel 1) every year since 2006 (Table \@ref(tab:ghl-harv)). In the years since 2006, increases in the estimated mature biomass have only occurred following estimated harvest rates of 10.2% or lower in the previous year (Figure \@ref(fig:jnumodel), Table \@ref(tab:ghl-harv)).

Determining an appropriate harvest level for red king crab in Southeast Alaska, specifically the Juneau area, is a complex task. Prior to 2012, the matrix for stock health (Table \@ref(tab:stock-status)) was used to suggest an appropriate harvest rate. In 2012 this was replaced with an equilibrium harvest rate that was calculated from the relationship between observed harvest rate and observed change in mature biomass. In theory (given a stable population with consistent growth and recruitment), this calculated equilibrium harvest rate would have an equal chance of producing an increase or decrease in the mature population size, therefore being a risk-neutral choice.  

Prior to the 2018 survey, the equilibrium harvest rate was re-analyzed using data up to the 2017/18 season. The results of this analysis, for the Juneau area, suggest an equilibrium harvest rate of 17%, which is the same as previous analyses (Figure \@ref(fig:equil), panel 1).  Despite a statistically strong relationship (p <0.01), this estimate continues to have substantial variability. To understand this variability, the analysis was repeated on subsets of the data: years with declining/low abundance, years with increasing/high abundance, and the currently used baseline years (Figure \@ref(fig:equil), panels 2-4). These subsets suggest a range of harvest rates from 6 to 25%; these rates are presented as harvest options, with the exception of 25%, because 20% is thought to be the maximum harvest that should be applied to mature king crab populations throughout Alaska (Tables \@ref(tab:harv-rate) and \@ref(tab:harv-rate-num)). 

Recent explorations of the relationship between harvest rates and observed changes in mature biomass in the Juneau area suggest strong first-order autoregression (AR1), suggesting that the change in mature biomass under a specific harvest rate is strongly related to the mature biomass in the previous year and that we cannot set harvest rates independent of each other. Further exploration is underway to use this relationship in predicting an appropriate harvest rate. 

The previous three years' survey data (2021, 2022, 2023) suggested the potential of a strong recruitment pulse upcoming in the population; however, this year's survey data identified lower pre-recruit numbers. This may indicate lower recruitment and a possible stabilization or decline in the coming years. Molting probability and growth are both linked to the health of the crab and their environment (food availability, temperature, etc.) and can be variable throughout Southeast Alaska. 

Under-reporting of harvest in the personal use harvest reporting (29%, 9%, 19%, 14%, 7%, and 12% of permits were not reported in previous personal use seasons, 2018, 2019, 2020, 2021, 2022, and 2023 respectively) and the decrease in mature biomass associated with the 10% harvest rate in 2017 and 8% harvest rate in 2018 suggests a reduced harvest rate from the equilibrium rate of 17% or maximum 20%.

The harvest rate of 10% that was applied in 2017 was enacted with the goal of allowing for population growth, since it was substantially lower than the 17% equilibrium harvest rate. Following the observed decrease in the estimated mature biomass, the harvest rate in 2018 was set at 8%, once again with the goal of allowing for overall population growth. However, because the mature biomass decreased following both openings, a further reduction in harvest pressure to 7% was enacted in 2019. 

The harvest rate (7%) set in the previous few years (2020, 2021, 2022) produced a relatively stable biomass estimate for legal and mature crab, with small (less than 8% decrease or increase) fluctuation in both legal biomass estimates depending on which model they were compared to, but the CPUEs of most mature male recruit classes showed an increase. The harvest rate in 2023 (10%) was associated with a decrease in CPUE for all male crab classes, although it is difficult to know to what extent the CPUE decreases were influenced by the harvest rate versus other factors such as environmental variation. Setting a harvest rate of 7%, the same level as the 2020-2022 seasons, would likely allow for some stability in mature male biomass for the following season, which would be effective if the goal is to maintain the population at the current level. A harvest rate of less than 7% may allow for more growth in the coming year. Harvest rates exceeding this would likely result in further population declines, with the probability of decrease and magnitude of the decline increasing proportional to the harvest rate. This population has only shown substantial improvements from 2013 to 2017, and from 2020 to 2023, even though harvest has been severely reduced since 2008. To encourage sustainability and population growth, a **7% or less harvest rate is recommended** for the `r cur_yr`/`r fut_yr` personal use season. GHL allocation tables for multiple harvest rate strategies were constructed (Tables \@ref(tab:harv-rate) and \@ref(tab:harv-rate-num)). Although harvest rates of 20%, 17%, 15%, 12%, 10%, 8%, and 7% are shown, the data suggest that implementing the higher end of this range would not serve the goal of sustaining average baseline population levels.


\newpage

\blandscape

# TABLES {-}

```{r stock-status, results = "asis", tab.cap="Determination of stock status for the Juneau area for the 2020–2024 surveys.  Values for long-term baseline analyses represent the percentage above or below the average CPUEs from 1995–2007 baseline (historically 1993 – 2007; see memo dated 6/23/2008 for discussion of baselines). Significant relationships result in $\\alpha$ < 0.05. Values for the short-term trends (last 4 years) are either significant increase, significant decrease, or no trend. Long-term scores are +1 for significantly above, 0 for not significantly different, or -1 for significantly below the baseline, except for clutch fullness < 25%, in which the signs are reversed because a score significantly below the baseline of 10% is considered a positive indicator of stock health. Short-term scores are +0.25 for significantly increasing trends, 0 for no trend, or -0.25 for significantly decreasing trends.  The total score is the sum of long- and short-term scores for each year. Stock status is defined by the total score: < -4.25 = Poor, -4.25 to -1.75 = Below Ave, -1.5 to 1.5 = Moderate, 1.75 to 4.25 = Above Ave, and > 4.25 = Healthy."}

# create lists of required files from all year folders
# first create vector of paths
results.paths <- c(paste0(here::here(), "/results/rkc/Juneau/", yr1), paste0(here::here(), "/results/rkc/Juneau/", yr2), paste0(here::here(), "/results/rkc/Juneau/", yr3), paste0(here::here(), "/results/rkc/Juneau/", yr4), paste0(here::here(), "/results/rkc/Juneau/", yr5))

# create file lists
longterm.files <- list.files(path = results.paths, pattern = "longterm.csv", recursive = TRUE, full.names = TRUE)
shortterm.files <- list.files(path =  results.paths, pattern = "shortterm.csv", recursive = TRUE, full.names = TRUE)
stockhealth.files <- list.files(path =  results.paths, pattern = "stock_health.csv", recursive = TRUE, full.names = TRUE)
ltfem.files <- list.files(path =  results.paths, pattern = "lt_female.csv", recursive = TRUE, full.names = TRUE)
stfem.files <- list.files(path =  results.paths, pattern = "short_female.csv", recursive = TRUE, full.names = TRUE)

# read in csv files
lt.files <- purrr::map(longterm.files, read_csv) %>%
  # calculate % difference with long-term mean
  map(~mutate(., vs.lt.base = round((mean / lt.mean) * 100, 0)))
st.files <- purrr::map(shortterm.files, read_csv)
sh.files <- purrr::map(stockhealth.files, read_csv) 
lf.files <- purrr::map(ltfem.files, read_csv) %>%
  # calculate % difference with long-term mean of 10%
  map(~mutate(., vs.lt.mean = round((mean / 0.1) * 100, 0)))
sf.files <- purrr::map(stfem.files, read_csv)

# make vectors to go into table
stat.cat <- c("Large/mature female CPUE", "", "", "Small/immature female CPUE", "", "", "Juvenile males", "", "", "Prerecruit CPUE", "", "", "Recruit CPUE", "", "", "Postrecruit CPUE", "", "", "Clutch fullness < 25 percent", "", "", "Total score", "Stock status", "Mature harvest rate")
stat.type <- c("vs. long-term average: percent of baseline", "vs. long-term average: score", "short-term trend: score", "vs. long-term average: percent of baseline", "vs. long-term average: score", "short-term trend: score", "vs. long-term average: percent of baseline", "vs. long-term average: score", "short-term trend: score", "vs. long-term average: percent of baseline", "vs. long-term average: score", "short-term trend: score", "vs. long-term average: percent of baseline", "vs. long-term average: score", "short-term trend: score", "vs. long-term average: percent of baseline", "vs. long-term average: score", "short-term trend: score", "vs. long-term average: percent of baseline", "vs. long-term average: score", "short-term trend: score", "", "", "")
stat.1 <- c(lt.files[[1]] %>% filter(recruit.status == "Large.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Large.Female") %>% select(significant) %>% pull(), 
            st.files[[1]] %>% filter(recruit.status == "Large.Females") %>% select(score) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Small.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Small.Female") %>% select(significant) %>% pull(), 
            st.files[[1]] %>% filter(recruit.status == "Small.Females") %>% select(score) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Juvenile") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Juvenile") %>% select(significant) %>% pull(), 
            st.files[[1]] %>% filter(recruit.status == "Juvenile") %>% select(score) %>% pull(),
            lt.files[[1]] %>% filter(recruit.status == "Pre_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Pre_Recruit") %>% select(significant) %>% pull(), 
            st.files[[1]] %>% filter(recruit.status == "Pre_Recruit") %>% select(score) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Recruit") %>% select(significant) %>% pull(), 
            st.files[[1]] %>% filter(recruit.status == "Recruit") %>% select(score) %>% pull(),
            lt.files[[1]] %>% filter(recruit.status == "Post_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[1]] %>% filter(recruit.status == "Post_Recruit") %>% select(significant) %>% pull(), 
            st.files[[1]] %>% filter(recruit.status == "Post_Recruit") %>% select(score) %>% pull(),
            lf.files[[1]] %>% select(vs.lt.mean) %>% pull(),
            lf.files[[1]] %>% select(significant) %>% pull(), 
            sf.files[[1]] %>% select(score) %>% pull(), 
            sh.files[[1]]$score, 
            sh.files[[1]]$health_status, 
            sh.files[[1]]$harvest_per)
stat.2 <- c(lt.files[[2]] %>% filter(recruit.status == "Large.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Large.Female") %>% select(significant) %>% pull(), 
            st.files[[2]] %>% filter(recruit.status == "Large.Females") %>% select(score) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Small.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Small.Female") %>% select(significant) %>% pull(), 
            st.files[[2]] %>% filter(recruit.status == "Small.Females") %>% select(score) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Juvenile") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Juvenile") %>% select(significant) %>% pull(), 
            st.files[[2]] %>% filter(recruit.status == "Juvenile") %>% select(score) %>% pull(),
            lt.files[[2]] %>% filter(recruit.status == "Pre_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Pre_Recruit") %>% select(significant) %>% pull(), 
            st.files[[2]] %>% filter(recruit.status == "Pre_Recruit") %>% select(score) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Recruit") %>% select(significant) %>% pull(), 
            st.files[[2]] %>% filter(recruit.status == "Recruit") %>% select(score) %>% pull(),
            lt.files[[2]] %>% filter(recruit.status == "Post_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[2]] %>% filter(recruit.status == "Post_Recruit") %>% select(significant) %>% pull(), 
            st.files[[2]] %>% filter(recruit.status == "Post_Recruit") %>% select(score) %>% pull(),
            lf.files[[2]] %>% select(vs.lt.mean) %>% pull(),
            lf.files[[2]] %>% select(significant) %>% pull(), 
            sf.files[[2]] %>% select(score) %>% pull(), 
            sh.files[[2]]$score, 
            sh.files[[2]]$health_status, 
            sh.files[[2]]$harvest_per)
stat.3 <- c(lt.files[[3]] %>% filter(recruit.status == "Large.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Large.Female") %>% select(significant) %>% pull(), 
            st.files[[3]] %>% filter(recruit.status == "Large.Females") %>% select(score) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Small.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Small.Female") %>% select(significant) %>% pull(), 
            st.files[[3]] %>% filter(recruit.status == "Small.Females") %>% select(score) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Juvenile") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Juvenile") %>% select(significant) %>% pull(), 
            st.files[[3]] %>% filter(recruit.status == "Juvenile") %>% select(score) %>% pull(),
            lt.files[[3]] %>% filter(recruit.status == "Pre_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Pre_Recruit") %>% select(significant) %>% pull(), 
            st.files[[3]] %>% filter(recruit.status == "Pre_Recruit") %>% select(score) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Recruit") %>% select(significant) %>% pull(), 
            st.files[[3]] %>% filter(recruit.status == "Recruit") %>% select(score) %>% pull(),
            lt.files[[3]] %>% filter(recruit.status == "Post_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[3]] %>% filter(recruit.status == "Post_Recruit") %>% select(significant) %>% pull(), 
            st.files[[3]] %>% filter(recruit.status == "Post_Recruit") %>% select(score) %>% pull(),
            lf.files[[3]] %>% select(vs.lt.mean) %>% pull(),
            lf.files[[3]] %>% select(significant) %>% pull(), 
            sf.files[[3]] %>% select(score) %>% pull(), 
            sh.files[[3]]$score, 
            sh.files[[3]]$health_status, 
            sh.files[[3]]$harvest_per)
stat.4 <- c(lt.files[[4]] %>% filter(recruit.status == "Large.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Large.Female") %>% select(significant) %>% pull(), 
            st.files[[4]] %>% filter(recruit.status == "Large.Females") %>% select(score) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Small.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Small.Female") %>% select(significant) %>% pull(), 
            st.files[[4]] %>% filter(recruit.status == "Small.Females") %>% select(score) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Juvenile") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Juvenile") %>% select(significant) %>% pull(), 
            st.files[[4]] %>% filter(recruit.status == "Juvenile") %>% select(score) %>% pull(),
            lt.files[[4]] %>% filter(recruit.status == "Pre_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Pre_Recruit") %>% select(significant) %>% pull(), 
            st.files[[4]] %>% filter(recruit.status == "Pre_Recruit") %>% select(score) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Recruit") %>% select(significant) %>% pull(), 
            st.files[[4]] %>% filter(recruit.status == "Recruit") %>% select(score) %>% pull(),
            lt.files[[4]] %>% filter(recruit.status == "Post_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[4]] %>% filter(recruit.status == "Post_Recruit") %>% select(significant) %>% pull(), 
            st.files[[4]] %>% filter(recruit.status == "Post_Recruit") %>% select(score) %>% pull(),
            lf.files[[4]] %>% select(vs.lt.mean) %>% pull(),
            lf.files[[4]] %>% select(significant) %>% pull(), 
            sf.files[[4]] %>% select(score) %>% pull(), 
            sh.files[[4]]$score, 
            sh.files[[4]]$health_status, 
            sh.files[[4]]$harvest_per)
stat.5 <- c(lt.files[[5]] %>% filter(recruit.status == "Large.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Large.Female") %>% select(significant) %>% pull(), 
            st.files[[5]] %>% filter(recruit.status == "Large.Females") %>% select(score) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Small.Female") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Small.Female") %>% select(significant) %>% pull(), 
            st.files[[5]] %>% filter(recruit.status == "Small.Females") %>% select(score) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Juvenile") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Juvenile") %>% select(significant) %>% pull(), 
            st.files[[5]] %>% filter(recruit.status == "Juvenile") %>% select(score) %>% pull(),
            lt.files[[5]] %>% filter(recruit.status == "Pre_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Pre_Recruit") %>% select(significant) %>% pull(), 
            st.files[[5]] %>% filter(recruit.status == "Pre_Recruit") %>% select(score) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Recruit") %>% select(significant) %>% pull(), 
            st.files[[5]] %>% filter(recruit.status == "Recruit") %>% select(score) %>% pull(),
            lt.files[[5]] %>% filter(recruit.status == "Post_Recruit") %>% select(vs.lt.base) %>% pull(), 
            lt.files[[5]] %>% filter(recruit.status == "Post_Recruit") %>% select(significant) %>% pull(), 
            st.files[[5]] %>% filter(recruit.status == "Post_Recruit") %>% select(score) %>% pull(),
            lf.files[[5]] %>% select(vs.lt.mean) %>% pull(),
            lf.files[[5]] %>% select(significant) %>% pull(), 
            sf.files[[5]] %>% select(score) %>% pull(), 
            sh.files[[5]]$score, 
            sh.files[[5]]$health_status, 
            sh.files[[5]]$harvest_per)

# make table data frame and set names
stockstat.tab <- data.frame(stat.cat, stat.type, stat.1, stat.2, stat.3, stat.4, stat.5)
names(stockstat.tab) <- c("", "", yr1, yr2, yr3, yr4, yr5)

kable(stockstat.tab, format = "pandoc")

#stockstat.tab1 <- xtable(stockstat.tab, digits = 0, caption = "Determination of stock status for the Juneau area for 2018–2023 surveys.  Values for long-term baseline analyses represent the percentage above or below the average CPUEs from 1995–2007 baseline (historically 1993 – 2007; see memo dated 6/23/2008 for discussion of baselines). Significant relationships result in $\\alpha$ < 0.05. Values for the short-term trends (last 4 years) are either significant increase, significant decrease, or no trend. Long-term scores are +1 for significantly above, 0 for not significantly different, or -1 for significantly below the baseline, except for clutch fullness < 25%, in which the signs are reversed because a score significantly below the baseline of 10% is considered a positive indicator of stock health. Short-term scores are +0.25 for significantly increasing trends, 0 for no trend, or -0.25 for significantly decreasing trends.  The total score is the sum of long- and short-term scores for each year. Stock status is defined by the total score: < -4.25 = Poor, -4.25 to -1.75 = Below Ave, -1.5 to 1.5 = Moderate, 1.75 to 4.25 = Above Ave, and > 4.25 = Healthy. ", label = "tab:stock-status", format = "pandoc")

#print(stockstat.tab1, caption.placement = "top", include.rownames = FALSE, comment=FALSE, sanitize.text.function=function(x){x})
```



```{r ghl-harv, results = "asis"}

# note: each year, add one row to the import (e.g., if in 2023 range is A5:L50, then in 2024 range is A5:L51)
ghl_harv <- read_excel(paste0(here::here(), "/CSA excel/Juneau ", cur_yr, " new weighting.xls"), sheet = "Table 2_currentYR", range = "A5:L51") 

colnames(ghl_harv) <- c("Year", "Legal biomass (lb)", "Mature biomass (lb)", "Rec. GHL (lb)", "Rec. PU GHL (lb)", "Rec. harvest rate", "Comm. fishery status", "Est. PU harvest (lb)", "Est. comm. harvest (lb)", "Est. total harvest (lb)", "Est. mature harvest rate", "Est. legal harvest rate")

ghl_harv1 <- ghl_harv %>% mutate(Year = as.character(Year)) %>%
  mutate(`Comm. fishery status` = case_when(
    `Comm. fishery status` == "Com. closed" ~ "Closed",
    Year == cur_yr ~ "TBD",
    TRUE ~ `Comm. fishery status`
  )) %>%
  mutate(`Est. mature harvest rate` = as.double(`Est. mature harvest rate`)) %>% #added from Caitlin code- 7/18/24
  mutate(`Est. legal harvest rate` = as.double(`Est. legal harvest rate`))%>%
  mutate(across(c(11, 12), ~ scales::label_percent(accuracy = 0.1)(.x))) %>% #updated c(11,12) for this specific table
  mutate(across(c(6), ~ scales::label_percent(accuracy = 1)(.x))) %>% #attempt to fix the rec harvest rate column
  mutate(across(where(is.double), ~ round(.x, 0))) %>%
  filter(Year > 1995) #ar added to make 1996 onward our table years

pandoc.table(ghl_harv1, keep.line.breaks = TRUE, big.mark = ',', digits = c(1,1,1,1,1,2,1,1,1,1,2,2), missing = "-", split.tables = Inf, caption = "Comparison of 2024 model output of legal biomass and mature biomass, and the recommended Guideline Harvest Level (GHL) to the harvest of RKC in the Juneau Area from 1996–2024. Estimated personal use (PU) harvest is calculated using the number of crabs reported for each permit and the average legal weight in the survey each year (since 1996). Total harvest includes both commercial and PU harvest (lb). Recommended harvest rate is % of mature biomass before 2022 and % of legal biomass from 2022 on\\label{tab:ghl-harv}.")

```


\elandscape


```{r harv-rate, results = "asis"}

harv.rate.lb <- read_excel(paste0(here::here(), "/CSA excel/Juneau ", cur_yr, " new weighting.xls"), sheet = "Table 3", range = "C5:J11") %>% 
  mutate(`GHL Allocation` = case_when(
    is.na(`GHL Allocation`) == TRUE ~ "GHL allocation (lb)",
    `GHL Allocation` == "PU Summer" ~ "PU summer (50%)",
    `GHL Allocation` == "PU Winter" ~ "PU winter (10%)",
    `GHL Allocation` == "Commercial" ~ "Commercial (40%)",
    `GHL Allocation` == "Total" ~ "Total (lb)" 
  ))

header.row <- harv.rate.lb %>%
  slice(1) %>% 
  mutate(across(where(is.double), ~ scales::percent(.x)))

names(harv.rate.lb) <- header.row
harv.rate.lb.tab <- harv.rate.lb %>% slice(-1, -5)

pandoc.table(harv.rate.lb.tab, big.mark = ',', digits = 1, missing = "-", caption = "Estimated biomass and allocation of RKC in the Juneau area under a range of harvest rate strategies for 2024. All Guideline Harvest Levels (GHLs) are in lb and are applied to legal biomass (lb). \\label{tab:harv-rate}")

```



```{r harv-rate-num, results = "asis"}

harv.rate.n <- read_excel(paste0(here::here(), "/CSA excel/Juneau ", cur_yr, " new weighting.xls"), sheet = "Table 3", range = "C19:J25") %>% 
  mutate(`GHL Allocation` = case_when(
    is.na(`GHL Allocation`) == TRUE ~ "GHL allocation (number)",
    `GHL Allocation` == "PU Summer" ~ "PU summer (50%)",
    `GHL Allocation` == "PU Winter" ~ "PU winter (10%)",
    `GHL Allocation` == "Commercial" ~ "Commercial (40%)",
    `GHL Allocation` == "Total" ~ "Total (number)" 
  ))

header.row.n <- harv.rate.n %>%
  slice(1) %>% 
  mutate(across(where(is.double), ~ scales::percent(.x)))

names(harv.rate.n) <- header.row.n
harv.rate.n.tab <- harv.rate.n %>% slice(-1, -5)

pandoc.table(harv.rate.n.tab, big.mark = ',', digits = 1, missing = "-", caption = "Estimated numbers and allocation of RKC in the Juneau area under a range of harvest rate strategies for 2024.  Guideline Harvest Levels (GHLs) are in approximate numbers of legal crab.  Conversion from biomass (lb) to numbers is done by dividing the biomass by the average legal weight from the Juneau area survey (2024 average survey legal length converted to weight = 7.41 lb per crab, mature weight = 6.37 lb per crab). GHL allocation is calculated by applying the average legal weight to the above GHL of legal biomass. \\label{tab:harv-rate-num}")

```


```{r pu-tab, results = "asis"}

pu.tab <- read.csv(paste0(here::here(), "/results/rkc/Juneau/PU_since_2018_updated", cur_yr, ".csv")) %>%
  mutate(Year = as.factor(Year)) %>%
  dplyr::rename("Summer \\\n \\\n \\\nPermits" = Summer.Permits) %>%
  dplyr::rename("Summer \\\n \\\n \\\nFished" = Summer...fished) %>%
  dplyr::rename("Summer \\\nReturned, \\\nnot fished" = Summer...returned.but.not.fished) %>%
  dplyr::rename("Summer \\\n \\\nNot \\\nreturned" = Summer...not.returned) %>%
  dplyr::rename("Summer \\\n \\\nEst. \\\nharvest" = Summer.estimated.harvest) %>%
  dplyr::rename("Winter \\\n \\\n \\\nPermits" = Winter.Permits) %>%
  dplyr::rename("Winter \\\n \\\n \\\nFished" = Winter...fished) %>%
  dplyr::rename("Winter \\\nReturned, \\\nnot fished" = Winter...returned.but.not.fished) %>%
  dplyr::rename("Winter \\\n \\\nNot \\\nreturned" = Winter...not.returned) %>%
  dplyr::rename("\\\n \\\n \\\nEst. \\\nharvest" = Winter.estimated.harvest) %>%
dplyr::rename("Total \\\nharvest" = Total.harvest) %>%
  mutate(across(c(3:5, 8:10), ~ paste0(.x, "%")))
  #mutate(across(c(3:5, 8:10), ~ scales::percent(.x)))

panderOptions('keep.line.breaks', TRUE)
pandoc.table(pu.tab, style="multiline", keep.line.breaks = TRUE, split.tables = Inf, big.mark = ',', digits = 1, missing = "-", caption = "Estimated personal use harvest by year and season for all years since 2018, in numbers of crabs. Estimated harvest is calculated using the number of crabs reported for each permit as well as the estimated harvest from those permits that were not returned. Total numbers of permits issued by season are reported, as well as the percentages of permits in each season that were fished, returned but not fished, and not returned. \\label{tab:pu-tab}")

```



\newpage

# FIGURES {-}

```{r jnumodel, fig.cap = "Juneau Area biomass estimates for legal (black points) and mature (gray points) red king crab from the current year’s 3-stage catch-survey analysis model. Black and grey (dashed) horizontal reference lines represent mean estimates during baseline years (1995–2007). Fishery status is reported in symbol type; closed status is when both commercial and personal use (PU) fisheries are closed and PU only status indicates that only a PU fishery occurred (commercial fishery was closed in that year).", out.height="100%", out.width="100%"}

knitr::include_graphics(paste0(here::here(), '/figures/rkc/', cur_yr,'/jnu_rkc_fig1_edited_v2.png'), dpi = 125)
```


```{r jnu-csa, fig.cap = "The current year’s CSA model fit. Both top and bottom left panels show model estimated survey CPUE (red lines) compared to calculated survey CPUE (black circles). The bottom right panel shows legal (red) and mature (black) estimated stock abundance for reference.", out.height="100%", out.width="100%"}

knitr::include_graphics(paste0(here::here(), '/figures/rkc/', cur_yr,'/jnu_csa_', cur_yr,'.png'), dpi = 125)
```

```{r panel2, fig.cap = "Survey CPUE for male size/sex classes of red king crab along with biomass and harvest estimates for the Juneau Area from 1995–2024 using the 2024 model output.  The horizontal reference lines indicate long-term averages, defined as the average CPUEs from 1995–2007. There is no mark-recapture adjustment for the Juneau area. ", out.height="100%", out.width="100%"}

knitr::include_graphics(paste0(here::here(), '/figures/rkc/', cur_yr,'/Juneau_', cur_yr, '_2.png'), dpi = 125)
```

```{r panel3, fig.cap = "Survey CPUE for female and juvenile size/sex classes of red king crab along with female percentage of poor clutches (% poor clutch) and overall clutch fullness (total % clutch).  The horizontal reference lines indicate long-term averages, defined as the average CPUEs from 1995–2007.", out.height="100%", out.width="100%"}
knitr::include_graphics(paste0(here::here(), '/figures/rkc/', cur_yr,'/Juneau_', cur_yr, '_3.png'), dpi = 125)
```

```{r equil, fig.cap = "Relationships between estimated harvest rate and population change of red king crab based on CSA biomass estimates (with 95% CI) for a) all years (1979–2017), b) decreasing/depressed time (2000–2012) and increasing/ high time (1990–1999), and c) baseline years (1993–2007). Harvest rate is calculated as commercial catch/mature male biomass.  Population change is calculated as (mature male biomass at time (t+1) - mature male biomass at time (t))/mature male biomass at time (t). The horizontal reference line indicates population equilibrium; the vertical reference line indicates equilibrium harvest rate.", out.height="100%", out.width="100%"}
knitr::include_graphics(paste0(here::here(), '/figures/rkc/Juneau_memo_equil_rate.png'), dpi = 125)

```


\newpage

# Appendix A. Historic record of annual model forecast {-}

```{r afig1, fig.cap = "Annual forecasts of Juneau Area biomass estimates for legal (black points) and mature (gray points) red king crab as annual point estimates (forecasts) from the 3-stage catch-survey analysis model. Black and grey (dashed) reference lines represent mean estimates during baseline years (1995–2007). Fishery status is reported in symbol type; closed status is when both commercial and personal use (PU) fisheries are closed and PU only status indicates that only a PU fishery occurred (commercial fishery was closed in that year).", out.height="100%", out.width="100%"}

knitr::include_graphics(paste0(here::here(), '/figures/rkc/', cur_yr,'/juneau_figA1_', cur_yr, '.png'), dpi = 125)
```


\newpage


```{r ghl-harv-hist, results = "asis"}

# note: each year, add one row to the import (e.g., if in 2023 range is A5:L50, then in 2024 range is A5:L51)
ghl_harv_hist <- read_excel(paste0(here::here(), "/CSA excel/Juneau ", cur_yr, " new weighting.xls"), sheet = "Table 2", range = "A4:K51") %>%
  slice(-1) %>%
  select(-Recommended) 

colnames(ghl_harv_hist) <- c("Year", "Legal biomass (lb)", "Mature biomass (lb)", "Rec. GHL (lb)", "Comm. fishery status", "Est. PU harvest (lb)", "Est. comm. harvest (lb)", "Est. total harvest (lb)", "Est. mature harvest rate", "Est. legal harvest rate")

ghl_harv_hist1 <- ghl_harv_hist %>% mutate(Year = as.character(Year)) %>%
  mutate(`Comm. fishery status` = case_when(
    `Comm. fishery status` == "Com. closed" ~ "Closed",
    Year == cur_yr ~ "TBD",
    TRUE ~ `Comm. fishery status`
  )) %>%
  mutate(`Est. mature harvest rate` = as.double(`Est. mature harvest rate`)) %>%
  mutate(`Est. legal harvest rate` = as.double(`Est. legal harvest rate`))%>%
  mutate(across(c(9, 10), ~ scales::label_percent(accuracy = 0.1)(.x))) %>%
  mutate(across(where(is.double), ~ round(.x, 0))) %>%
  filter(Year > 1995)
  

pandoc.table(ghl_harv_hist1, keep.line.breaks = TRUE, big.mark = ',', digits = 1, missing = "-", split.tables = Inf, caption = "Comparison of annual forecast legal biomass and mature biomass, and the recommended Guideline Harvest Level (GHL) to the harvest of RKC in the Juneau Area from 1996–2023. Annual forecast for the biomass estimates is the point estimate generated in the year and uses survey data only up to that year in the model, i.e. 2012 estimates here are those generated from the model output in 2012. Estimated personal use (PU) harvest is calculated using the number of crabs reported for each permit and the average legal weight in the survey each year (since 1996). Total harvest includes both commercial and PU harvest (lb). \\label{tab:ghl-harv-hist}")

```


\newpage


```{r stan-cpue, results = "asis"}

cp <- read.csv(paste0(here::here(), "/results/rkc/Juneau/", cur_yr, "/cpue_wt_since_95.csv")) %>%
  mutate(Year = as.factor(Year)) %>%
  mutate(across(where(is.double), ~ round(.x, 2))) %>%
  mutate("Pre-recruit" = paste0(Pre_Recruit_wt, " $\\pm$ ", PreR_SE)) %>%
  mutate("Recruit" = paste0(Recruit_wt, " $\\pm$ ", Rec_SE)) %>%
  mutate("Post-recruit" = paste0(Post_Recruit_wt, " $\\pm$ ", PR_SE)) %>%
  mutate("Juvenile male" = paste0(Juvenile_wt, " $\\pm$ ", Juv_SE)) %>%
  mutate("Mature female" = paste0(MatF_wt, " $\\pm$ ", MatF_SE)) %>%
  mutate("Juvenile female" = paste0(SmallF_wt, " $\\pm$ ", SmallF_SE)) %>%
  select(Year, `Pre-recruit`, Recruit, `Post-recruit`, `Juvenile male`, `Mature female`, `Juvenile female`)
  

pandoc.table(cp, split.tables = Inf, caption = "Standardized catch per unit effort (CPUE) from the Juneau area red king crab survey. Estimates are displayed $\\pm$ standard error. \\label{tab:stan-cpue}")

```
